### 2021-10-25 Article/main.tex
Added LATEX docs

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{hyperref}
\hypersetup{
	urlbordercolor=  0.2 0.8 0.72,
    pdftitle={Linking Gamification, Ludology and Pedagogy: How to Use Serious Games for Various Knowledge Domains},}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Linking Gamification, Ludology and Pedagogy: How to Use Serious Games for Various Knowledge Domains\\

}

\author{\IEEEauthorblockN{Joshua Esterhuizen}
\IEEEauthorblockA{\textit{School of Computer Science and Information Systems} \\
\textit{North-West University,}\\
Potchefstroom, South Africa \\
\href{mailto:joshua.esterhuizen27@gmail.com}{joshua.esterhuizen27@gmail.com}}
\and

\IEEEauthorblockN{Günther Drevin}
\IEEEauthorblockA{\textit{School of Computer Science and Information Systems} \\
\textit{North-West University,}\\
Potchefstroom, South Africa \\
\href{mailto:Gunther.Drevin@nwu.ac.za}{Gunther.Drevin@nwu.ac.za}}

}

\maketitle

\begin{abstract}
This document is a model and instructions for \LaTeX.
This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes, 
or Math in Paper Title or Abstract.
\end{abstract}

\begin{IEEEkeywords}
component, formatting, style, styling, insert
\end{IEEEkeywords}

\section{Introduction}
This document is a model and instructions for \LaTeX.
Please observe the conference page limits.

\section{Ease of Use}

\subsection{Maintaining the Integrity of the Specifications}

The IEEEtran class file is used to format your paper and style the text. All margins, 
column widths, line spaces, and text fonts are prescribed; please do not 
alter them. You may note peculiarities. For example, the head margin
measures proportionately more than is customary. This measurement 
and others are deliberate, using specifications that anticipate your paper 
as one part of the entire proceedings, and not as an independent document. 
Please do not revise any of the current designations.

\section{Prepare Your Paper Before Styling}
Before you begin to format your paper, first write and save the content as a 
separate text file. Complete all content and organizational editing before 
formatting. Please note sections \ref{AA}--\ref{SCM} below for more information on 
proofreading, spelling and grammar.

Keep your text and graphic files separate until after the text has been 
formatted and styled. Do not number text heads---{\LaTeX} will do that 
for you.

\subsection{Abbreviations and Acronyms}\label{AA}
Define abbreviations and acronyms the first time they are used in the text, 
even after they have been defined in the abstract. Abbreviations such as 
IEEE, SI, MKS, CGS, ac, dc, and rms do not have to be defined. Do not use 
abbreviations in the title or heads unless they are unavoidable.

\subsection{Units}
\begin{itemize}
\item Use either SI (MKS) or CGS as primary units. (SI units are encouraged.) English units may be used as secondary units (in parentheses). An exception would be the use of English units as identifiers in trade, such as ``3.5-inch disk drive''.
\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds. This often leads to confusion because equations do not balance dimensionally. If you must use mixed units, clearly state the units for each quantity that you use in an equation.
\item Do not mix complete spellings and abbreviations of units: ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not ``webers/m\textsuperscript{2}''. Spell out units when they appear in text: ``. . . a few henries'', not ``. . . a few H''.
\item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm\textsuperscript{3}'', not ``cc''.)
\end{itemize}

\subsection{Equations}
Number equations consecutively. To make your 
equations more compact, you may use the solidus (~/~), the exp function, or 
appropriate exponents. Italicize Roman symbols for quantities and variables, 
but not Greek symbols. Use a long dash rather than a hyphen for a minus 
sign. Punctuate equations with commas or periods when they are part of a 
sentence, as in:
\begin{equation}
a+b=\gamma\label{eq}
\end{equation}

Be sure that the 
symbols in your equation have been defined before or immediately following 
the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at 
the beginning of a sentence: ``Equation \eqref{eq} is . . .''

\subsection{\LaTeX-Specific Advice}

Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
of ``hard'' references (e.g., \verb|(1)|). That will make it possible
to combine sections, add equations, or change the order of figures or
citations without having to go through the file line by line.

Please don't use the \verb|{eqnarray}| equation environment. Use
\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
environment leaves unsightly spaces around relation symbols.

Please note that the \verb|{subequations}| environment in {\LaTeX}
will increment the main equation counter even when there are no
equation numbers displayed. If you forget that, you might write an
article in which the equation numbers skip from (17) to (20), causing
the copy editors to wonder if you've discovered a new method of
counting.

{\BibTeX} does not work by magic. It doesn't get the bibliographic
data from thin air but from .bib files. If you use {\BibTeX} to produce a
bibliography you must send the .bib files.

{\LaTeX} can't read your mind. If you assign the same label to a
subsubsection and a table, you might find that Table I has been cross
referenced as Table IV-B3.

{\LaTeX} does not have precognitive abilities. If you put a
\verb|\label| command before the command that updates the counter it's
supposed to be using, the label will pick up the last counter to be
cross referenced instead. In particular, a \verb|\label| command
should not go before the caption of a figure or a table.

Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
will not stop equation numbers inside \verb|{array}| (there won't be
any anyway) and it might stop a wanted equation number in the
surrounding equation.

\subsection{Some Common Mistakes}\label{SCM}
\begin{itemize}
\item The word ``data'' is plural, not singular.
\item The subscript for the permeability of vacuum $\mu_{0}$, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
\item In American English, commas, semicolons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation. When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks. A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this). (A parenthetical sentence is punctuated within the parentheses.)
\item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
\item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
\item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
\item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
\item Do not confuse ``imply'' and ``infer''.
\item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
\item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
\item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
\end{itemize}
An excellent style manual for science writers is \cite{b7}.

\subsection{Authors and Affiliations}
\textbf{The class file is designed for, but not limited to, six authors.} A 
minimum of one author is required for all conference articles. Author names 
should be listed starting from left to right and then moving down to the 
next line. This is the author sequence that will be used in future citations 
and by indexing services. Names should not be listed in columns nor group by 
affiliation. Please keep your affiliations as succinct as possible (for 
example, do not differentiate among departments of the same organization).

\subsection{Identify the Headings}
Headings, or heads, are organizational devices that guide the reader through 
your paper. There are two types: component heads and text heads.

Component heads identify the different components of your paper and are not 
topically subordinate to each other. Examples include Acknowledgments and 
References and, for these, the correct style to use is ``Heading 5''. Use 
``figure caption'' for your Figure captions, and ``table head'' for your 
table title. Run-in heads, such as ``Abstract'', will require you to apply a 
style (in this case, italic) in addition to the style provided by the drop 
down menu to differentiate the head from the text.

Text heads organize the topics on a relational, hierarchical basis. For 
example, the paper title is the primary text head because all subsequent 
material relates and elaborates on this one topic. If there are two or more 
sub-topics, the next level head (uppercase Roman numerals) should be used 
and, conversely, if there are not at least two sub-topics, then no subheads 
should be introduced.

\subsection{Figures and Tables}
\paragraph{Positioning Figures and Tables} Place figures and tables at the top and 
bottom of columns. Avoid placing them in the middle of columns. Large 
figures and tables may span across both columns. Figure captions should be 
below the figures; table heads should appear above the tables. Insert 
figures and tables after they are cited in the text. Use the abbreviation 
``Fig.~\ref{fig}'', even at the beginning of a sentence.

\begin{table}[htbp]
\caption{Table Type Styles}
\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline
\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
\cline{2-4} 
\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
\hline
copy& More table copy$^{\mathrm{a}}$& &  \\
\hline
\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
\end{tabular}
\label{tab1}
\end{center}
\end{table}

\begin{figure}[htbp]
\centerline{\includegraphics{fig1.png}}
\caption{Example of a figure caption.}
\label{fig}
\end{figure}

Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 
rather than symbols or abbreviations when writing Figure axis labels to 
avoid confusing the reader. As an example, write the quantity 
``Magnetization'', or ``Magnetization, M'', not just ``M''. If including 
units in the label, present them within parentheses. Do not label axes only 
with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization 
\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of 
quantities and units. For example, write ``Temperature (K)'', not 
``Temperature/K''.

\section*{Acknowledgment}

The preferred spelling of the word ``acknowledgment'' in America is without 
an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
acknowledgments in the unnumbered footnote on the first page.

\section*{References}

Please number citations consecutively within brackets \cite{b1}. The 
sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference 
number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at 
the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''

Number footnotes separately in superscripts. Place the actual footnote at 
the bottom of the column in which it was cited. Do not put footnotes in the 
abstract or reference list. Use letters for table footnotes.

Unless there are six authors or more give all authors' names; do not use 
``et al.''. Papers that have not been published, even if they have been 
submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers 
that have been accepted for publication should be cited as ``in press'' \cite{b5}. 
Capitalize only the first word in a paper title, except for proper nouns and 
element symbols.

For papers published in translation journals, please give the English 
citation first, followed by the original foreign-language citation \cite{b6}.

\begin{thebibliography}{00}
\bibitem{b1} G. Eason, B. Noble, and I. N. Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil. Trans. Roy. Soc. London, vol. A247, pp. 529--551, April 1955.
\bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
\bibitem{b6} Y. Yorozu, M. Hirano, K. Oka, and Y. Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl. J. Magn. Japan, vol. 2, pp. 740--741, August 1987 [Digests 9th Annual Conf. Magnetics Japan, p. 301, 1982].
\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
\end{thebibliography}
\vspace{12pt}
\color{red}
IEEE conference templates contain guidance text for composing and formatting conference papers. Please ensure that all template text is removed from your conference paper prior to submission to the conference. Failure to remove the template text from your paper may result in your paper not being published.

\end{document}

### 2021-10-25 Article/main.tex
Added main talking points

@@
 
-\IEEEauthorblockN{Günther Drevin}
+\IEEEauthorblockN{Günther Drevin (Supervisor)}
 \IEEEauthorblockA{\textit{School of Computer Science and Information Systems} \\
@@
 \begin{abstract}
-This document is a model and instructions for \LaTeX.
-This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes, 
-or Math in Paper Title or Abstract.
+Education as a whole has seen no major improvements for a long period of time while society has matured and grown rapidly in the same time frame.
+Due to this teaching and learning methods can be seen as stale to certain students.
+One way to solve this issue is with the implementation of some from of the technology that has developed over the years.
+This study looks at the possibility of adapting various domains of knowledge into digital games referred to as Serious Games.
+The implementation of serious games within teaching may help keep certain students engaged with the content being presented and create further interest in the topic.
+However, before reaching this stage the means to transform these knowledge domains into a serious games must be studied.
+This is done by focusing on three fields in particular, those being Gamification, Ludology and Pedagogy.
 \end{abstract}
@@
 \begin{IEEEkeywords}
-component, formatting, style, styling, insert
+Education, Gamification, Knowledge Domains, Ludology, Pedagogy, Serious Games
 \end{IEEEkeywords}
@@
 
-\section{Ease of Use}
+\section{Literature Review}
+\subsection{Serious Games and Ludology}
+\subsection{A Pedagogical Approach}
+\subsection{Gamification and the Knowledge Domains}
+
+\section{Methodology}
+The following steps were taken to determine how serious games can be used for the various knowledge domains:
+
+\begin{itemize}
+\item[1.] Literature surrounding the applicable fields was researched
+\item[2.] Case studies concerning serious games was studied and similarities noted
+\item[3.] Select theories that aid this process were pinpointed
+\item[4.] From this research, recommendations for the knowledge domains were made
+\end{itemize}
+
+\subsection{Sampling of Literature}
+\subsection{Collection of Case Studies and Determine Similarities}
+\subsection{Pinpointing Connected Theories}
+\subsection{Extrapolate to other Knowledge Domains}
+
+\section{Findings}
+\subsection{Helpful Teaching Theories}
+\subsection{Case Studies and the Similarities in Design Principles}
+
+\section{Synthesis from Research}
+\subsection{Recommendations per Knowledge Domain}
+\subsection{Limitations and Future Research}
 

### 2021-10-26 Article/main.tex
Updated Article with Intro and Pedagogy Lit

@@
 % The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
-\usepackage{cite}
+
+\usepackage[backend=biber]{biblatex}
+\addbibresource{Article.bib}
 \usepackage{amsmath,amssymb,amsfonts}
@@
 \section{Introduction}
-This document is a model and instructions for \LaTeX.
-Please observe the conference page limits.
+Education, as it stands, is still built on a paradigm that is no longer needed in modern society.
+One major flaw with the current system is that it stifles the creativity and drive of some students as each level of education is largely the same and is, as such, monotonous\cite{Ackoff2008} Therefore, education requires some form of system to create an interest in learning for the students.
+\\\\
+Ackoff and Greenberg\cite{Ackoff2008} explain that the current traditional means of teaching are no longer as relevant as they once were as it is aimed to produce members of society that were likely to not question any fundamental aspects of how things operated.
+It is largely a system that focuses on teaching while disregarding learning as the last major stride in development in education was to industrialise it – having them operate efficiently like factories\cite{Ackoff2008}.
+It is a system that is designed to keep moving often employing a “No Child Left Behind” policy which results in almost no time for anything other than the standardised and constantly measured curriculum\cite{gibson2006games}.
+\\\\
+However, with the shift into the “information age”, the requirements of the workforce have also changed.
+The industrial age being a time of mass-production with the emergence of various new processing technologies and the information age being characterised by the fact that information is being transmitted and generated at an ever-increasing rate due to further technological developments\cite{gibson2006games, Reigeluth1996}.
+The most notable changes between these ages is that the industrial age focused on conformity and compliance while initiative and diversity - where greater value is placed on each individual’s strengths and contribution to a project or organisation – is the focus of the information age\cite{Reigeluth1996}.
+\\\\
+Reigeluth\cite{Reigeluth1996} continues and states that the current paradigm of instruction is not focused on learning but rather categorisation.
+Ackoff\cite{Ackoff1991} holds a similar viewpoint stating that there is more of a focus on teaching rather than learning.
+It should be noted that teaching and learning are very distinct from one another as both can take place without the other\cite{Ackoff1991}.
+Learning is defined as increasing one’s ability to perform an act effectively while trying to meet an objective through acquiring new knowledge whereas teaching is the process of providing this knowledge\cite{Ackoff1991}.
+Through this, it is clear that institutions under this paradigm aim to give learners a verbose vocabulary to speak on topics that they do not fully comprehend\cite{Ackoff1991}.
+\\\\
+Due to this aforementioned paradigm shifts between the ages and in what requirements are desired by most organisations in the information age, a shift in instructional theory is also needed – one such as going from making use of passive learning through traditional teaching means to one that is centred on active learning\cite{Reigeluth1996}.
+\\\\
+With the recent developments in technology and the fact that technology, in general, is becoming more accessible, some institutions have adopted some forms of digital learning or supplement traditional teaching with digital assistance.
+Deshpande and Huang\cite{Deshpande2011} state that the current generation of students is the first to grow up with abundant access to technology.
+They continue to state that, on average, these students spend almost double the time playing video games as they do reading\cite{Deshpande2011}.
+It can be assumed that from when Deshpande and Huang’s\cite{Deshpande2011} published this work that this figure has increased as with technology and video games as industries.
+\\\\
+Virvou, Katsionis and Manos\cite{Virvou2005} echo the point that computer games are popular among individuals who are in schools and as such could provide a means to deliver content in an interesting and engaging manner.
+\\\\
+According to Annetta\cite{Annetta2008}, the movement for the inclusion of digital games to be used in teaching and training environments first started in 2003, two years after the field of ludology, the study of games, began to gain traction in academic literature.
+This initiative is what started the concept of a serious game as one that can be used in an academic sense to relay information.
+After this point in time, various examples of serious games were made for purely academic study purposes and had found a very large use in simulation for use as explanation aides and medical training.
+\\\\
+As such, the motivation behind this study is to further investigate the possibility of using video games as a means to encourage learning in teaching environments as current means of teaching may not be optimal for some individuals.
+This will be accomplished through studying literature in the relevant fields and identifying the instances where it is viable.
 
@@
 \subsection{A Pedagogical Approach}
+Pedagogy is the filed that deals with the transferal of knowledge in an educational environment through several lenses such as social, political and cultural\cite{Li2012}.
+As such it encompasses the fields and discussions of instructional design and theory as well as any learning theories – of which several are particularly useful to this study.
+\\\\
+Learning by doing functions on the principle that skills can be improved through practice and self-perfection on a particular topic or knowledge base\cite{Fisch2009}.
+This means of instruction has become increasingly popular amongst companies where they are able to make use of “on the job” training as it allows for a person to be productive immediately as well as become more proficient at tasks gradually\cite{Fisch2009}.
+\\\\
+The learning by teaching method works under the assumption that learners are able to increase their understanding of a certain topic by teaching it to other learners\cite{Fisch2009}.
+This method of learning has garnered more usage recently as it is a viable means of learning in environments with too few teachers or instructors and increases the overall learning process\cite{Fisch2009}.
+Learning methods that place the learner in control are very flexible and as such can be incorporated when attempting to teach various and different fields or subjects\cite{Ackoff1991}.
+\\\\
+Gibson et al.\cite{gibson2006games} list and summarise several learning and instructional design theories that have the potential to be applied to a game used for learning.
+This study will, however, only look at Merrill’s First Principles of Instruction as it is the most recent of the ones depicted  and is one that is very expansive and as such can be used in a variety of manners\cite{gibson2006games}.
+\\\\
+Before discussing the principles that the name refers to in this theory, Merrill\cite{Merrill2002} provides a few definitions for the terms made use of.
+A principle in this context is a relationship that is always true regardless of the environment it is applied within – this being the driving factor for deciding to make use of this theory\cite{Merrill2002}.
+A practice is any instructional activity\cite{Merrill2002}.
+A program is a means of instruction that makes use of several practices\cite{Merrill2002}.
+Merrill\cite{Merrill2002} states that the first principles described are able to be implemented in any instructional system or environment as they are “design-oriented” and as such relate more to creating learning environments rather than describing the means of knowledge transfer.
+Each of the following principles is also accompanied by three “corollaries” each of which Merrill\cite{Merrill2002} likewise explains.
+\\\\
+The first principle of Merrill’s First Principles of Instruction is that the learning is problem centred.
+This principle describes three corollaries, the first of which being “Show Task” which states that learners should be shown the types of problems they will be solving or will be able to solve with the knowledge that they attain\cite{Merrill2002}.
+The next is the “Task Level” which explains that the problems presented should keep learners engaged due to the complexity and not just the action of solving it\cite{Merrill2002}.
+The last corollary, “Problem Progression” describes that the problems presented should have some form of increasing complexity while still being comparable to the previous iteration of the type of problem\cite{Merrill2002}.
+\\\\
+The second principle is Activation which means that learning happens whenever previous experiences are used\cite{Merrill2002}.
+The first corollary, “Previous Experience”, states that the learning process is enhanced when a learner is able to draw upon relevant past experiences and apply the associate knowledge as a foundation for new knowledge\cite{Merrill2002}.
+“New Knowledge” is the second and explains that learners should be provided with a relevant experience as an additional foundation to add to their knowledge base\cite{Merrill2002}.
+The last corollary is “Structure” and details that learners should be encouraged to organise new knowledge according to some relevant structure\cite{Merrill2002}.
+\\\\
+The third principle, Demonstration, proposes that learning takes place when the activities that are undertaken impart the knowledge instead of stating the information\cite{Merrill2002}.
+“Demonstration Consistency” explains that any examples or visualisation should be kept in line with the original learning goals\cite{Merrill2002}.
+The next is “Learner Guidance” and states that learners should be shown where the relevant information for problems can be found be it in the form of comparative examples or various representation of one source\cite{Merrill2002}.
+“Relevant Media” explains that when media is used as a means of demonstration, different types can be used provided that they do not fight for a learner’s attention\cite{Merrill2002}.
+\\\\
+The fourth principle is Application which states that learning takes place when learners actively solve problems with the new knowledge they have acquired\cite{Merrill2002}.
+“Practice Consistency” is similar to Demonstration consistency but with a focus on the application of knowledge\cite{Merrill2002}.
+“Diminishing Coaching” is where the learners are provided with relevant feedback, but it is slowly lessened over time\cite{Merrill2002}.
+It is also important that the problems provided to learners for practice have a good variety, as explained as “Varied Problems”\cite{Merrill2002}.
+\\\\
+The fifth, and final, principle is Integration which is when the knowledge a learner has acquired is used by them in their everyday life\cite{Merrill2002}.
+The first corollary, “Watch Me”, explains that learners are provided to showcase the new knowledge or skill they have acquired\cite{Merrill2002}.
+“Reflection” deals with giving learners time to be able to debate with others on the topic involved\cite{Merrill2002}.
+Lastly, “Creation” states that learners should be able to make use of their new knowledge or skill in some personal capacity\cite{Merrill2002}.
+\\
+\begin{figure}[htbp]
+\centerline{\includegraphics[scale=0.35]{merrill2.png}}
+\caption{Own Image summarising Merrill's First Principles}
+\label{fig}
+\end{figure}
+\\
+The principles and corollaries provided by Merrill\cite{Merrill2002} provide an expansive and detailed structure to be used when developing any learning opportunity making it an exceptional choice to adapt specifically to a digital game learning system.
+It does, however, lack a comprehensive discussion on how to keep learners engaged with the content and, as such, the next subsection will discuss some theories pertaining to the role of motivation in learning.
+\\\\
+Another important factor to consider is how to keep learners engaged and motivated with the instructional material.
+One model for motivating learners is the ARCS Model which was developed by John Keller which is frequently referenced in the aforementioned field of instructional design\cite{Kapp2012a}.
+It is comprised of four main elements with each focusing on designing instruction in a different way\cite{Kapp2012a}.
+\\\\
+The first of these is Attention and it is an element that is concerned with gaining and then keeping the learners’ interest.
+There are three main methods to accomplish this with the first being gaining attention through the use of relatable examples or surprise.
+The next is to create curiosity within the learners through means such as role-playing or hands-on examples.
+The last means to keep attention is the variability which means periodically changing the method of delivery\cite{Kapp2012a}.
+\\\\
+Relevance refers to having the content be relevant to the learner and Kapp\cite{Kapp2012a} mentions that this can be done through orienting the environment around achieving goals, creating a link between the motives of learners and that of the instruction means, displaying that the content is in somewhat familiar to the learners and finally developing a model of the results of learning the presented knowledge.
+\\\\
+Another element of this model, Confidence, is the expectations of success set by the learner and as such when they meet these expectations they are confident in their ability to do the work\cite{Kapp2012a}.
+This can be aided by providing learners with clear expectations and requirements upfront about the skill or knowledge.
+It is also helpful to provide smaller opportunities to succeed as with each success the learners will become more confident\cite{Kapp2012a}.
+\\\\
+The last element in the ARCS model is Satisfaction and is concerned with giving learners a sense of accomplishment and that the effort in the learning process has some value and weight to it\cite{Kapp2012a}.
+This can be accomplished by allowing learners to see how their newfound knowledge can be used, either through the use of a real-world demonstration or via some form of simulation\cite{Kapp2012a}.
+
 \subsection{Gamification and the Knowledge Domains}
@@
 
+\printbibliography
+
+%%------------------------------------------------------------
 \subsection{Maintaining the Integrity of the Specifications}
@@
 Failure to remove the template text from your paper may result in your paper not being published.
+%%-------------------------------------------------------------------
 

### 2021-10-26 Article/main.tex
Updated Article with Ludology and Gamification

@@
 \subsection{Serious Games and Ludology}
+Ludology is the formal and academic study of games and has roots in studying games through a cultural and social lens by discussing how each interacts with the so-called “spirit of play”\cite{Huizinga1949}.
+However, relatively recently, as early as 2001, the field has shifted and now encompasses the study of digital computer-based games as this is when the first academic peer reviewed journal on the topic was published as well as several international conferences taking place\cite{Frasca2013}.
+\\\\
+As such, this study will use the definition provided by Gonzalo Frasca, “Ludology can be defined as a discipline that studies games in general, and video games in particular”\cite{Frasca2013}.
+Frasca\cite{Frasca2013} further elaborates on his statement that the field of ludology has a focus on discussing and understanding the individual elements of games as well as creating models to explain the various mechanics and rules of games.
+\\\\
+“Serious games” were introduced as digital concepts in 2002 through the Serious Game Initiative which was spearheaded by David Rejeski and Ben Sawyer\cite{DeGloria2014}.
+The initial intention for serious games was for them to be used as a means of training certain tasks and skills\cite{DeGloria2014} – this was typically done through simulation type games which will be discussed in greater detail further on.
+\\\\
+Squire\cite{Squire2003} provides a definition for games as a simulation and states that these simulations attempt to model reality in a consistent manner usually through modelling physical or social systems through another system – which in this case would be a computer and the digital video game.
+There are two main types of simulations, Hi-fidelity and low fidelity.
+Hi-fidelity simulations attempt to model every possible interaction in a given system, phenomena or environment as accurately as possible\cite{Squire2003}.
+In contrast, a low fidelity simulation will make use of a fair bit of abstraction as it aims to only demonstrate a few key characteristics of the phenomena or environment\cite{Squire2003}.
+Games as simulations would comprise of both of these types depending on the content that it attempts to simulate.
+\\\\
+Virvou, Katsionis and Manos\cite{Virvou2005} mention that the endeavour to create serious games has yet to reach schools due to certain criticisms about games in general that hinders this.
+This is due to the fact that discussions around games by educators have largely focused on the social consequences of playing games instead of the educational potential games hold\cite{Squire2003}.
+Due to this the study of serious games became more theoretical and discussion-based at lower levels and more applied with actual use at higher levels.
+This can be seen by implementations implemented in several fields including medical rehabilitation, ecological studies, learning languages and business studies\cite{Burke2009, Costanza2014, Ranalli2008, Tao2009}.
+These types of games have already had an impact on the military, medical and higher business education fields early in their conception and this trend continues to this day with most serious games being used within the medical fields specifically\cite{Annetta2008, DeGloria2014}.
+However, there were attempts to use serious games, as simulations, within physics and engineering\cite{Deshpande2011}.
+\\\\
+Deshpande and Huang\cite{Deshpande2011} describe the use of games as a means of simulation for specific sections of work in physics and engineering courses as an addition to traditional teaching as it provides a relatively simple way to demonstrate certain phenomena.
+As such these authors discuss the simulation aspect of games rather than the narrative as when dealing with a simulation digital game it typical lacks most narrative elements in the traditional sense\cite{Deshpande2011}.
+
 \subsection{A Pedagogical Approach}
@@
 \subsection{Gamification and the Knowledge Domains}
+Gamification can be defined as making use of game-like mechanics, aesthetics and thinking to create motivation, solve problems and produce a more suitable learning environment\cite{Kapp2012a}.
+Kapp\cite{KappArticle2012} states that while gamification makes use of game elements, it only makes use of a few of them as in a gamified system, in a gamification context, learners are not constantly engaged in playing the game as there are sections of respite from this, such as video explanations.
+While elements such as points and achievements are found in most games, gamification strives to add more than just these to a classroom as with the absence of other elements and only points and badges, the resulting system is one that is dull\cite{KappArticle2012}.
+Kapp\cite{KappArticle2012} continues stating that gamification adds much more to create an interesting system such as narrative aspects and continuous feedback to learners to create and upkeep their motivation and engagement with the system.
+\\\\
+Gamification is often not implemented within a classroom but is rather presented to learners through some external means – such as a digital game \cite{KappArticle2012}.
+It should be noted, however, that a serious game can be the result of the gamification of some content but gamification does not always have to produce a serious game as a result \cite{KappArticle2012}.
+\\\\
+Kapp\cite{Kapp2012a} describes various types of knowledge and how to begin developing a gamified system to effectively teach each of them.
+This provides the ground work for answering the question this study poses and as such allows for a more in depth discussion on how to implement serious games.
+These knowledge domains are described as\cite{Kapp2012a}:
+
+\begin{itemize}
+\item Declarative Knowledge is usually comprised of facts and jargon within a topic.
+\item Conceptual Knowledge is the grouping of related information that have an underlying common descriptor.
+\item Rules-Based Knowledge is strict statements linking concepts.
+\item Procedural Knowledge is a progression based path to reach an outcome.
+\item Soft Skills are general strategies for dealing with various social interactions.
+\item Affective Knowledge deals with topics about subjective phenomena such as emotions.
+\item Psychomotor Domain deals with making use of cognitive knowledge through physical skills (hand-eye coordination is an example of this).
+\end{itemize}
 

### 2021-10-27 Article/main.tex
Updated Article with Methodology

@@
 
+One important aspect to note about these knowledge domains is that they are not mutually exclusive as one particular topic can be placed in several of them as the components of that topic may require multiple domains to be properly contained under them.
+
 \section{Methodology}
@@
 \subsection{Sampling of Literature}
+During this phase key fields of study were identifies for use in working towards the goal of this study.
+As discussed above, these included the fields of pedagogy (the study of instructional theory), ludology (the study of games with a focus on digital games) and gamification (the use of game-like elements to solve problems).
+Studying the literature in each of these fields yielded literature that is undoubtedly useful to this study as pedagogy gave insight into instructional theories used in education, ludology provided the necessary understanding of how to study games and the elements that each uses and gamification provided insight into the different knowledge domains and how to best approach each in a teaching environment in addition acting as a bridge for connecting pedagogy to the serious games in ludology.
+\\\\
+The bulk of this phase was spent reading articles and identifying which would be useful for this study.
+It was also during this phase that select case studies were found.
+These case studies proved useful as each made use of different design principles and as such became another set of literature to be studied.
+
 \subsection{Collection of Case Studies and Determine Similarities}
+As case studies were accumulated, only those found that discussed - either directly in great detail or indirectly during the game's description -the design principles followed were selected to be used.
+Notably, many of those chosen had a focus on some form of digital and cyber security including specific mentions to phishing, social engineering and passwords\cite{Sheng2007, Dincelli2020, snyman2021wolf}.
+\\\\
+The following step after finding these case studies was to identify their design principles and determine the major ones that most, if not all, made use of as well as how successful the game was found to be - which is determined in the individual publication either by trails of being judged by experts.
+
 \subsection{Pinpointing Connected Theories}
+Once enough literature had been acquired and studied, the connections between each of the fields' theory and case studys' design principles were noted.
+This was in attempt to identify an overall pattern in the development of serious games for use particularly for educational or training purposes.
+This included mapping the similarities between the instructional theories to the deign principles of each case study while noting which fields of knowledge the games are a part of.
+
 \subsection{Extrapolate to other Knowledge Domains}
+For the knowledge domains that the case studies do not directly relate to, recommendations for them will be generated out of what has been found.
+In addition to this, certain design principles used by the case studies can be directly applied to these domains.
 
 \section{Findings}
-\subsection{Helpful Teaching Theories}
+\subsection{Helpful Instructional Theories}
 \subsection{Case Studies and the Similarities in Design Principles}

### 2021-10-27 Article/main.tex
Updated Article

@@
 As case studies were accumulated, only those found that discussed - either directly in great detail or indirectly during the game's description -the design principles followed were selected to be used.
-Notably, many of those chosen had a focus on some form of digital and cyber security including specific mentions to phishing, social engineering and passwords\cite{Sheng2007, Dincelli2020, snyman2021wolf}.
+Notably, many of those chosen had a focus on some form of digital and cyber security including specific mentions to phishing and social engineering\cite{Sheng2007, Dincelli2020}.
 \\\\
@@
 \section{Findings}
+As described in the methodology, a large aspect of the findings comes from the literature review conducted.
+However, the literature review only provided segmented information that must still be distilled.
+This includes making note of what instructional theory is most pertinent to this study and breaking down the case studies.
+It also includes a short discussion on the initial reconsiderations from Kapp\cite{Kapp2012a} regarding the knowledge domains.
+
 \subsection{Helpful Instructional Theories}
 \subsection{Case Studies and the Similarities in Design Principles}
+
+\begin{table}[htbp]
+\caption{Design Principles Defined by Case Study}
+\begin{center}
+\begin{tabular}{|c|c|c|c|}
+\hline
+
+\textbf{SETA Artefact} & \textbf{\textit{Anti-Phishing Phil}}& \textbf{\textit{Happy Hippo}} \\
+\hline
+Story-based& Story-based & Clear and Simple Goals  \\
+Reflection& Reflection& Quality of Feedback and Rewards  \\
+-& Conceptual-Procedural & Structure of the Challenge  \\
+-& -& Motion-based Interaction  \\
+-& -& Simplicity  \\
+\hline
+
+\end{tabular}
+\label{tab1}
+\end{center}
+\end{table}
+
+\subsection{Initial Knowledge Domain Recommendations}
 

### 2021-10-27 Article/main.tex
Added and Updated Final Doc Latex

@@
 
-\begin{itemize}
-\item[1.] Literature surrounding the applicable fields was researched
-\item[2.] Case studies concerning serious games was studied and similarities noted
-\item[3.] Select theories that aid this process were pinpointed
-\item[4.] From this research, recommendations for the knowledge domains were made
-\end{itemize}
+\begin{enumerate}
+
+\item Literature surrounding the applicable fields was researched
+\item Case studies concerning serious games was studied and similarities noted
+\item Select theories that aid this process were pinpointed
+\item From this research, recommendations for the knowledge domains were made
+\end{enumerate}
 

### 2021-10-27 Final Doc/Chapters/Chapter1.tex
Added and Updated Final Doc Latex

% Chapter 1

\chapter{Introduction} % Main chapter title

\label{Chapter1} % For referencing the chapter elsewhere, use \ref{Chapter1}

%----------------------------------------------------------------------------------------

% Define some commands to keep the formatting separated from the content 
\newcommand{\keyword}[1]{\textbf{#1}}
\newcommand{\tabhead}[1]{\textbf{#1}}
\newcommand{\code}[1]{\texttt{#1}}
\newcommand{\file}[1]{\texttt{\bfseries#1}}
\newcommand{\option}[1]{\texttt{\itshape#1}}

%----------------------------------------------------------------------------------------

\section{Project Description}

\section{Project Contents}
\subsection{Problem Description and Background}
\subsection{Overview of Related Literature}
\subsection{Research Question and Expected Outcomes}

\section{Aims and Objectives of Project}

\section{Procedures and Methods of Investigation}
\subsection{Research Paradigm and Methodology Used}
\subsection{Collection of Data}
\subsection{Development of Artefact}
\subsection{Integration with Other Projects}

\section{Approach to Project Management and Project Plan}
\subsection{Provisional Project Plan}
\subsection{Scope}
\subsection{Contributions of Each Group Member}

\section{Development Platform, Resources and Environments}
\subsection{Development Platform}
\subsection{Resources}
\subsection{Environments}

\section{Ethical Implications of Project}

\section{Provisional Chapter Division}

### 2021-10-27 Final Doc/Chapters/Chapter2.tex
Added and Updated Final Doc Latex

% Chapter 2

\chapter{Literature Review} % Main chapter title

\label{Chapter2} % For referencing the chapter elsewhere, use \ref{Chapter1}

\section{Introduction}

\section{An Issue with Instructional Education}

\section{Pedagogy and Learning Theories}
\subsection{Learner's at the Core of Learning}
\subsection{Merrill's First Principles of Instruction}
\subsection{The Influence of Motivation}

\section{An Approach Through Ludology}
\subsection{What is Ludology}
\subsection{Serious Games}
\subsection{Games as Simulation}

\section{Gamification}

\section{Existing Gamified Teaching Systems and Educational Games}

\section{Potential Effects of Game-Based Learning}

\section{Conclusion and Summary}

### 2021-10-27 Final Doc/main.tex
Added and Updated Final Doc Latex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Masters/Doctoral Thesis 
% LaTeX Template
% Version 2.5 (27/8/17)
%
% This template was downloaded from:
% http://www.LaTeXTemplates.com
%
% Version 2.x major modifications by:
% Vel (vel@latextemplates.com)
%
% This template is based on a template by:
% Steve Gunn (http://users.ecs.soton.ac.uk/srg/softwaretools/document/templates/)
% Sunil Patel (http://www.sunilpatel.co.uk/thesis-template/)
%
% Template license:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[
11pt, % The default document font size, options: 10pt, 11pt, 12pt
oneside, % Two side (alternating margins) for binding by default, uncomment to switch to one side
english, % ngerman for German
singlespacing, % Single line spacing, alternatives: onehalfspacing or doublespacing
%draft, % Uncomment to enable draft mode (no pictures, no links, overfull hboxes indicated)
%nolistspacing, % If the document is onehalfspacing or doublespacing, uncomment this to set spacing in lists to single
%liststotoc, % Uncomment to add the list of figures/tables/etc to the table of contents
%toctotoc, % Uncomment to add the main table of contents to the table of contents
%parskip, % Uncomment to add space between paragraphs
%nohyperref, % Uncomment to not load the hyperref package
headsepline, % Uncomment to get a line under the header
%chapterinoneline, % Uncomment to place the chapter title next to the number on one line
%consistentlayout, % Uncomment to change the layout of the declaration, abstract and acknowledgements pages to match the default layout
]{MastersDoctoralThesis} % The class file specifying the document structure

\usepackage[utf8]{inputenc} % Required for inputting international characters
\usepackage[T1]{fontenc} % Output font encoding for international characters
\usepackage[final]{pdfpages}
\usepackage{mathpazo} % Use the Palatino font by default

\usepackage[backend=bibtex,style=authoryear,natbib=true]{biblatex} % Use the bibtex backend with the authoryear citation style (which resembles APA)

\addbibresource{example.bib} % The filename of the bibliography

\usepackage[autostyle=true]{csquotes} % Required to generate language-dependent quotes in the bibliography

%----------------------------------------------------------------------------------------
%	MARGIN SETTINGS
%----------------------------------------------------------------------------------------

\geometry{
	paper=a4paper, % Change to letterpaper for US letter
	inner=1.5cm, % Inner margin
	outer=1.5cm, % Outer margin
	bindingoffset=0.3cm, % Binding offset
	top=0.5cm, % Top margin
	bottom=0.5cm, % Bottom margin
	%showframe, % Uncomment to show how the type block is set on the page
}

%----------------------------------------------------------------------------------------
%	THESIS INFORMATION
%----------------------------------------------------------------------------------------

\thesistitle{The Qualities of Games for Use in Education} % Your thesis title, this is used in the title and abstract, print it elsewhere with \ttitle
\supervisor{Prof. Günther \textsc{Drevin}} % Your supervisor's name, this is used in the title page, print it elsewhere with \supname
\examiner{} % Your examiner's name, this is not currently used anywhere in the template, print it elsewhere with \examname
\degree{Bachelor of Science Honours in Computer Science and Information Technology} % Your degree name, this is used in the title page and abstract, print it elsewhere with \degreename
\author{Joshua \textsc{Esterhuizen}} % Your name, this is used in the title page and abstract, print it elsewhere with \authorname
\addresses{} % Your address, this is not currently used anywhere in the template, print it elsewhere with \addressname

\subject{Computer Sciences} % Your subject area, this is not currently used anywhere in the template, print it elsewhere with \subjectname
\keywords{} % Keywords for your thesis, this is not currently used anywhere in the template, print it elsewhere with \keywordnames
\university{\href{http://http://www.nwu.ac.za/}{North-West University}} % Your university's name and URL, this is used in the title page and abstract, print it elsewhere with \univname
\department{\href{http://http://natural-sciences.nwu.ac.za/computer-sciences-and-information-systems}{School of Computer Science and Information Systems}} % Your department's name and URL, this is used in the title page and abstract, print it elsewhere with \deptname
%\group{\href{}{}} % Your research group's name and URL, this is used in the title page, print it elsewhere with \groupname
\faculty{\href{http://natural-sciences.nwu.ac.za/}{Faculty of Natural and Agricultural Sciences}} % Your faculty's name and URL, this is used in the title page and abstract, print it elsewhere with \facname

\AtBeginDocument{
\hypersetup{pdftitle=\ttitle} % Set the PDF's title to your title
\hypersetup{pdfauthor=\authorname} % Set the PDF's author to your name
\hypersetup{pdfkeywords=\keywordnames} % Set the PDF's keywords to your keywords
}

\begin{document}

\frontmatter % Use roman page numbering style (i, ii, iii, iv...) for the pre-content pages

\pagestyle{plain} % Default to the plain heading style until the thesis style is called for the body content

%----------------------------------------------------------------------------------------
%	TITLE PAGE
%----------------------------------------------------------------------------------------

\begin{titlepage}
\begin{center}
\includegraphics[scale=0.3]{nwu.png}\\[0.4cm]

{\scshape\LARGE \univname\par}\vspace{0.5cm} % University name
\textsc{\Large School of Computer Science and Information Systems}\\[0.5cm] % Thesis type

\HRule \\[0.4cm] % Horizontal line
{\huge \bfseries \ttitle\par}\vspace{0.4cm} % Thesis title
\HRule \\[1.0cm] % Horizontal line

\begin{minipage}[t]{0.4\textwidth}
\begin{flushleft} \large
\emph{Author:}\\
\href{mailto:joshua.esterhuizen27@gmail.com}{\authorname} \\ % Author name - remove the \href bracket to remove the link
\textit{30285976}
\end{flushleft}
\end{minipage}
\begin{minipage}[t]{0.4\textwidth}
\begin{flushright} \large
\emph{Supervisor:} \\
\href{mailto:Gunther.Drevin@nwu.ac.za}{\supname} % Supervisor name - remove the \href bracket to remove the link  
\end{flushright}
\end{minipage}\\[3cm]

\vfill

\large \textit{A thesis submitted in fulfilment of the requirements for the degree of \\ \degreename}\\[0.3cm] % University requirement text
\large \textit{for the}\\
\large \textit{ITRI671 module}\\
\vfill

{\large \today}\\[4cm] % Date
%\includegraphics{Logo} % University/department logo - uncomment to place it

\vfill
\end{center}
\end{titlepage}

%----------------------------------------------------------------------------------------
%	ABSTRACT PAGE
%----------------------------------------------------------------------------------------

\begin{abstract}
\addchaptertocentry{\abstractname} % Add the abstract to the table of contents
The Thesis Abstract is written here (and usually kept to just this page). The page is kept centered vertically so can expand into the blank space above the title too\ldots
\end{abstract}

%--------------------------------------------------------------------------------
%	LIST OF CONTENTS/FIGURES/TABLES PAGES
%----------------------------------------------------------------------------------------

\tableofcontents % Prints the main table of contents

\listoffigures % Prints the list of figures

\listoftables % Prints the list of tables

%----------------------------------------------------------------------------------------
%	ABBREVIATIONS
%----------------------------------------------------------------------------------------
%
%\begin{abbreviations}{ll} % Include a list of abbreviations (a table of two columns)
%
%\textbf{LAH} & \textbf{L}ist \textbf{A}bbreviations \textbf{H}ere\\
%\textbf{WSF} & \textbf{W}hat (it) \textbf{S}tands \textbf{F}or\\
%
%\end{abbreviations}
%
%----------------------------------------------------------------------------------------
%	THESIS CONTENT - CHAPTERS
%----------------------------------------------------------------------------------------

\mainmatter % Begin numeric (1,2,3...) page numbering

\pagestyle{thesis} % Return the page headers back to the "thesis" style

% Include the chapters of the thesis as separate files from the Chapters folder
% Uncomment the lines as you write the chapters

\include{Chapters/Chapter1}
\include{Chapters/Chapter2}

%----------------------------------------------------------------------------------------
%	THESIS CONTENT - APPENDICES
%----------------------------------------------------------------------------------------

\appendix % Cue to tell LaTeX that the following "chapters" are Appendices

% Include the appendices of the thesis as separate files from the Appendices folder
% Uncomment the lines as you write the Appendices

\include{Appendices/AppendixA}
\include{Appendices/AppendixB}
\include{Appendices/AppendixC}

%----------------------------------------------------------------------------------------
%	BIBLIOGRAPHY
%----------------------------------------------------------------------------------------

\printbibliography[heading=bibintoc]

%----------------------------------------------------------------------------------------

\end{document}

### 2021-10-28 Article/main.tex
Updated Findings

@@
 \usepackage{graphicx}
+\usepackage{changepage}
 \usepackage{textcomp}
@@
 \begin{figure}[htbp]
-\centerline{\includegraphics[scale=0.35]{merrill2.png}}
+\centerline{\includegraphics[scale=0.37]{merrill2.png}}
 \caption{Own Image summarising Merrill's First Principles}
@@
 Another important factor to consider is how to keep learners engaged and motivated with the instructional material.
-One model for motivating learners is the ARCS Model which was developed by John Keller which is frequently referenced in the aforementioned field of instructional design\cite{Kapp2012a}.
-It is comprised of four main elements with each focusing on designing instruction in a different way\cite{Kapp2012a}.
+One model for motivating learners is the ARCS Model which was developed by John Keller\cite{keller1987development} which is frequently referenced in the aforementioned field of instructional design\cite{Kapp2012a}.
+It is comprised of four main elements with each focusing on designing instruction in a different way\cite{Kapp2012a, keller1987development}.
 \\\\
@@
 The next is to create curiosity within the learners through means such as role-playing or hands-on examples.
-The last means to keep attention is the variability which means periodically changing the method of delivery\cite{Kapp2012a}.
+The last means to keep attention is the variability which means periodically changing the method of delivery\cite{Kapp2012a, keller1987development}.
 \\\\
-Relevance refers to having the content be relevant to the learner and Kapp\cite{Kapp2012a} mentions that this can be done through orienting the environment around achieving goals, creating a link between the motives of learners and that of the instruction means, displaying that the content is in somewhat familiar to the learners and finally developing a model of the results of learning the presented knowledge.
+Relevance refers to having the content be relevant to the learner\cite{keller1987development} and Kapp\cite{Kapp2012a} mentions that this can be done through orienting the environment around achieving goals, creating a link between the motives of learners and that of the instruction means, displaying that the content is in somewhat familiar to the learners and finally developing a model of the results of learning the presented knowledge\cite{keller1987development}.
 \\\\
-Another element of this model, Confidence, is the expectations of success set by the learner and as such when they meet these expectations they are confident in their ability to do the work\cite{Kapp2012a}.
+Another element of this model, Confidence, is the expectations of success set by the learner and as such when they meet these expectations they are confident in their ability to do the work\cite{Kapp2012a, keller1987development}.
 This can be aided by providing learners with clear expectations and requirements upfront about the skill or knowledge.
-It is also helpful to provide smaller opportunities to succeed as with each success the learners will become more confident\cite{Kapp2012a}.
+It is also helpful to provide smaller opportunities to succeed as with each success the learners will become more confident\cite{Kapp2012a, keller1987development}.
 \\\\
-The last element in the ARCS model is Satisfaction and is concerned with giving learners a sense of accomplishment and that the effort in the learning process has some value and weight to it\cite{Kapp2012a}.
-This can be accomplished by allowing learners to see how their newfound knowledge can be used, either through the use of a real-world demonstration or via some form of simulation\cite{Kapp2012a}.
+The last element in the ARCS model is Satisfaction and is concerned with giving learners a sense of accomplishment and that the effort in the learning process has some value and weight to it\cite{Kapp2012a, keller1987development}.
+This can be accomplished by allowing learners to see how their new-found knowledge can be used, either through the use of a real-world demonstration or via some form of simulation\cite{Kapp2012a, keller1987development}.
 
@@
 \begin{enumerate}
-
 \item Literature surrounding the applicable fields was researched
@@
 This includes making note of what instructional theory is most pertinent to this study and breaking down the case studies.
-It also includes a short discussion on the initial reconsiderations from Kapp\cite{Kapp2012a} regarding the knowledge domains.
+It also includes a short discussion on the initial recommendations from Kapp\cite{Kapp2012a} regarding the knowledge domains.
 
 \subsection{Helpful Instructional Theories}
+This study detailed the ARCS model of motivation and Merrill's First Principles.
+While there are certainly others that would be helpful, these two provide sufficient knowledge to begin answering the question at hand.
+\\\\
+Merrill's First Principles\cite{Merrill2002} provides a basis to begin development on a framework for serious games as it is already rooted in teaching.
+As such, using this theory in conjunction with the information gained from the case studies and the work done by Kapp\cite{Kapp2012a} it allows for a particular stricture to be followed.
+\\\\
+Similarly, the ARCS model for motivation developed by John Keller\cite{keller1987development} can be used in conjunction with Merrill's First Principles and the other findings to ensure learners are kept engaged and motivated with the games.
+
+\subsection{Initial Knowledge Domain Recommendations}
+Kapp\cite{Kapp2012a}, in addition to providing definitions of the various knowledge domains, provides some ways that each domain can be taught to best relay that particular type of knowledge.
+While these reconsiderations are derived under a gamification perspective, that can just as easily be applied for a digital game.
+
+\begin{itemize}
+\item
+Games that would involve some form of sorting and matching are ideal for teaching declarative knowledge\cite{Kapp2012a}.
+\item
+Conceptual knowledge is beast taught through demonstrations and once again a sorting type game where the sorting is based on the common trait of the content or topic\cite{Kapp2012a}.
+\item
+A demonstration that displays the failure of not complying with the rules is helpful for a topic under the rules-based knowledge domain\cite{Kapp2012a}.
+\item
+Procedural knowledge is best taught through having the learners work through the procedure itself in some means\cite{Kapp2012a}.
+\item
+Soft Skills are best taught through having the learner repeatedly apply the skill in question u=in various scenarios\cite{Kapp2012a}.
+\item
+Immersing the learner within a phenomena found in the affective knowledge domain is a neffective means of teaching them about it\cite{Kapp2012a}.
+\item
+Kapp\cite{Kapp2012a} states that observation is an ideal method of teaching the learner about a topic in this domain.
+\end{itemize}
+
 \subsection{Case Studies and the Similarities in Design Principles}
-
+Several case studies were examined in which some form of gamified system or serious game was developed in addition to the author(s) detailing what design principles were followed during the development process.
+There are three main case studies that will be focused on in this study\cite{Dincelli2020,Sheng2007,allers2021children}.
+\\\\
+The first of these is titled, \textit{"Choose your own training adventure: designing a gamified SETA artefact for improving information security and privacy through interactive storytelling"} and focused on developing a gamified system to teach employees about security issues - focussing on social media and social engineering\cite{Dincelli2020}.
+\\\\
+The next case study is titles \textit{"Anti-phishing phil: the design and evaluation of a game that teaches people not to fall for phish"} and focused on teaching people about phishing that is done through the use of fake websites and the ways links are used for this\cite{Sheng2007}.
+\\\\
+The final case study used is titled \textit{"Children’s Awareness of Digital Wellness: A Serious Games Approach"} and was targeted towards teching children, particularly preschoolers, about digital well-being and foster cyber security awareness by means of a mobile-based serious game\cite{allers2021children}
 \begin{table}[htbp]
-\caption{Design Principles Defined by Case Study}
-\begin{center}
+\caption{Design Principles Defined by Case Study \cite{Dincelli2020,Sheng2007,allers2021children}}
+\begin{adjustwidth}{-0.6cm}{}
 \begin{tabular}{|c|c|c|c|}
@@
 \hline
-Story-based& Story-based & Clear and Simple Goals  \\
-Reflection& Reflection& Quality of Feedback and Rewards  \\
--& Conceptual-Procedural & Structure of the Challenge  \\
--& -& Motion-based Interaction  \\
--& -& Simplicity  \\
+Story-based	& Story-based 			& Clear and Simple Goals  \\
+Reflection	& Reflection			& Quality of Feedback and Rewards  \\
+	-		& Conceptual-Procedural & Structure of the Challenge  \\
+	-		& 		-				& Motion-based Interaction  \\
+	-		& 		-				& Simplicity  \\
 \hline
@@
 \label{tab1}
-\end{center}
+\end{adjustwidth}
 \end{table}
-
-\subsection{Initial Knowledge Domain Recommendations}
 
@@
 \subsection{Recommendations per Knowledge Domain}
-\subsection{Limitations and Future Research}
+
+\section{Limitations and Future Research}
 
@@
 
-%%------------------------------------------------------------
-\subsection{Maintaining the Integrity of the Specifications}
-
-The IEEEtran class file is used to format your paper and style the text. All margins, 
-column widths, line spaces, and text fonts are prescribed; please do not 
-alter them. You may note peculiarities. For example, the head margin
-measures proportionately more than is customary. This measurement 
-and others are deliberate, using specifications that anticipate your paper 
-as one part of the entire proceedings, and not as an independent document. 
-Please do not revise any of the current designations.
-
-\section{Prepare Your Paper Before Styling}
-Before you begin to format your paper, first write and save the content as a 
-separate text file. Complete all content and organizational editing before 
-formatting. Please note sections \ref{AA}--\ref{SCM} below for more information on 
-proofreading, spelling and grammar.
-
-Keep your text and graphic files separate until after the text has been 
-formatted and styled. Do not number text heads---{\LaTeX} will do that 
-for you.
-
-\subsection{Abbreviations and Acronyms}\label{AA}
-Define abbreviations and acronyms the first time they are used in the text, 
-even after they have been defined in the abstract. Abbreviations such as 
-IEEE, SI, MKS, CGS, ac, dc, and rms do not have to be defined. Do not use 
-abbreviations in the title or heads unless they are unavoidable.
-
-\subsection{Units}
-\begin{itemize}
-\item Use either SI (MKS) or CGS as primary units.
-(SI units are encouraged.) English units may be used as secondary units (in parentheses).
-An exception would be the use of English units as identifiers in trade, such as ``3.5-inch disk drive''.
-\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds.
-This often leads to confusion because equations do not balance dimensionally.
-If you must use mixed units, clearly state the units for each quantity that you use in an equation.
-\item Do not mix complete spellings and abbreviations of units: ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not ``webers/m\textsuperscript{2}''.
-Spell out units when they appear in text: ``.
-.
-.
-a few henries'', not ``.
-.
-.
-a few H''.
-\item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm\textsuperscript{3}'', not ``cc''.)
-\end{itemize}
-
-\subsection{Equations}
-Number equations consecutively. To make your 
-equations more compact, you may use the solidus (~/~), the exp function, or 
-appropriate exponents. Italicize Roman symbols for quantities and variables, 
-but not Greek symbols. Use a long dash rather than a hyphen for a minus 
-sign. Punctuate equations with commas or periods when they are part of a 
-sentence, as in:
-\begin{equation}
-a+b=\gamma\label{eq}
-\end{equation}
-
-Be sure that the 
-symbols in your equation have been defined before or immediately following 
-the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at 
-the beginning of a sentence: ``Equation \eqref{eq} is . . .''
-
-\subsection{\LaTeX-Specific Advice}
-
-Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
-of ``hard'' references (e.g., \verb|(1)|). That will make it possible
-to combine sections, add equations, or change the order of figures or
-citations without having to go through the file line by line.
-
-Please don't use the \verb|{eqnarray}| equation environment. Use
-\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
-environment leaves unsightly spaces around relation symbols.
-
-Please note that the \verb|{subequations}| environment in {\LaTeX}
-will increment the main equation counter even when there are no
-equation numbers displayed. If you forget that, you might write an
-article in which the equation numbers skip from (17) to (20), causing
-the copy editors to wonder if you've discovered a new method of
-counting.
-
-{\BibTeX} does not work by magic. It doesn't get the bibliographic
-data from thin air but from .bib files. If you use {\BibTeX} to produce a
-bibliography you must send the .bib files.
-
-{\LaTeX} can't read your mind. If you assign the same label to a
-subsubsection and a table, you might find that Table I has been cross
-referenced as Table IV-B3.
-
-{\LaTeX} does not have precognitive abilities. If you put a
-\verb|\label| command before the command that updates the counter it's
-supposed to be using, the label will pick up the last counter to be
-cross referenced instead. In particular, a \verb|\label| command
-should not go before the caption of a figure or a table.
-
-Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
-will not stop equation numbers inside \verb|{array}| (there won't be
-any anyway) and it might stop a wanted equation number in the
-surrounding equation.
-
-\subsection{Some Common Mistakes}\label{SCM}
-\begin{itemize}
-\item The word ``data'' is plural, not singular.
-\item The subscript for the permeability of vacuum $\mu_{0}$, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
-\item In American English, commas, semicolons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation.
-When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks.
-A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this).
-(A parenthetical sentence is punctuated within the parentheses.)
-\item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
-\item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
-\item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
-\item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
-\item Do not confuse ``imply'' and ``infer''.
-\item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
-\item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
-\item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
-\end{itemize}
-An excellent style manual for science writers is \cite{b7}.
-
-\subsection{Authors and Affiliations}
-\textbf{The class file is designed for, but not limited to, six authors.} A 
-minimum of one author is required for all conference articles. Author names 
-should be listed starting from left to right and then moving down to the 
-next line. This is the author sequence that will be used in future citations 
-and by indexing services. Names should not be listed in columns nor group by 
-affiliation. Please keep your affiliations as succinct as possible (for 
-example, do not differentiate among departments of the same organization).
-
-\subsection{Identify the Headings}
-Headings, or heads, are organizational devices that guide the reader through 
-your paper. There are two types: component heads and text heads.
-
-Component heads identify the different components of your paper and are not 
-topically subordinate to each other. Examples include Acknowledgments and 
-References and, for these, the correct style to use is ``Heading 5''. Use 
-``figure caption'' for your Figure captions, and ``table head'' for your 
-table title. Run-in heads, such as ``Abstract'', will require you to apply a 
-style (in this case, italic) in addition to the style provided by the drop 
-down menu to differentiate the head from the text.
-
-Text heads organize the topics on a relational, hierarchical basis. For 
-example, the paper title is the primary text head because all subsequent 
-material relates and elaborates on this one topic. If there are two or more 
-sub-topics, the next level head (uppercase Roman numerals) should be used 
-and, conversely, if there are not at least two sub-topics, then no subheads 
-should be introduced.
-
-\subsection{Figures and Tables}
-\paragraph{Positioning Figures and Tables} Place figures and tables at the top and 
-bottom of columns. Avoid placing them in the middle of columns. Large 
-figures and tables may span across both columns. Figure captions should be 
-below the figures; table heads should appear above the tables. Insert 
-figures and tables after they are cited in the text. Use the abbreviation 
-``Fig.~\ref{fig}'', even at the beginning of a sentence.
-
-\begin{table}[htbp]
-\caption{Table Type Styles}
-\begin{center}
-\begin{tabular}{|c|c|c|c|}
-\hline
-\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
-\cline{2-4} 
-\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
-\hline
-copy& More table copy$^{\mathrm{a}}$& &  \\
-\hline
-\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
-\end{tabular}
-\label{tab1}
-\end{center}
-\end{table}
-
-\begin{figure}[htbp]
-\centerline{\includegraphics{fig1.png}}
-\caption{Example of a figure caption.}
-\label{fig}
-\end{figure}
-
-Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 
-rather than symbols or abbreviations when writing Figure axis labels to 
-avoid confusing the reader. As an example, write the quantity 
-``Magnetization'', or ``Magnetization, M'', not just ``M''. If including 
-units in the label, present them within parentheses. Do not label axes only 
-with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization 
-\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of 
-quantities and units. For example, write ``Temperature (K)'', not 
-``Temperature/K''.
-
-\section*{Acknowledgment}
-
-The preferred spelling of the word ``acknowledgment'' in America is without 
-an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
-G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
-acknowledgments in the unnumbered footnote on the first page.
-
-\section*{References}
-
-Please number citations consecutively within brackets \cite{b1}. The 
-sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference 
-number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at 
-the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''
-
-Number footnotes separately in superscripts. Place the actual footnote at 
-the bottom of the column in which it was cited. Do not put footnotes in the 
-abstract or reference list. Use letters for table footnotes.
-
-Unless there are six authors or more give all authors' names; do not use 
-``et al.''. Papers that have not been published, even if they have been 
-submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers 
-that have been accepted for publication should be cited as ``in press'' \cite{b5}. 
-Capitalize only the first word in a paper title, except for proper nouns and 
-element symbols.
-
-For papers published in translation journals, please give the English 
-citation first, followed by the original foreign-language citation \cite{b6}.
-
-\begin{thebibliography}{00}
-\bibitem{b1} G.
-Eason, B.
-Noble, and I.
-N.
-Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil.
-Trans.
-Roy.
-Soc.
-London, vol.
-A247, pp.
-529--551, April 1955.
-\bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
-\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
-\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
-\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
-\bibitem{b6} Y.
-Yorozu, M.
-Hirano, K.
-Oka, and Y.
-Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl.
-J.
-Magn.
-Japan, vol.
-2, pp.
-740--741, August 1987 [Digests 9th Annual Conf.
-Magnetics Japan, p.
-301, 1982].
-\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
-\end{thebibliography}
-\vspace{12pt}
-\color{red}
-IEEE conference templates contain guidance text for composing and formatting conference papers.
-Please ensure that all template text is removed from your conference paper prior to submission to the conference.
-Failure to remove the template text from your paper may result in your paper not being published.
-%%-------------------------------------------------------------------
-
 \end{document}

### 2021-10-28 Article/main.tex
Update Article

@@
 \subsection{Collection of Case Studies and Determine Similarities}
-As case studies were accumulated, only those found that discussed - either directly in great detail or indirectly during the game's description -the design principles followed were selected to be used.
+As case studies were accumulated, only those found that discussed - either directly in great detail or indirectly during the game's description - the design principles followed were selected to be used.
 Notably, many of those chosen had a focus on some form of digital and cyber security including specific mentions to phishing and social engineering\cite{Sheng2007, Dincelli2020}.
@@
 \\\\
+%---------------No. 1
 The first of these is titled, \textit{"Choose your own training adventure: designing a gamified SETA artefact for improving information security and privacy through interactive storytelling"} and focused on developing a gamified system to teach employees about security issues - focussing on social media and social engineering\cite{Dincelli2020}.
 \\\\
+For the development of the artefact Dincelli and Chengalur-Smith\cite{Dincelli2020} made use of literature from instructional theory and gamification and as a result made use of a few key design principles.
+The first design principle followed is that the gamified system should make use of a \textit{story-based agent}\cite{Dincelli2020}.
+This means that a game should include some figure or character to guide users through the content as well as making use of story-telling in some capacity which is found to create curiosity within users\cite{Dincelli2020, Kapp2012a}.
+Furthermore, the use of a "choose your own adventure" style creates an interactive narrative by which the user is in control of certain decisions that change how the story plays out also improves learning\cite{Dincelli2020}.
+The second design principle used was that of \textit{reflection} which states that users should be given a moment of respite to dwell on what has previously been presented to them\cite{Dincelli2020,Sheng2007}.Feedback on various metrics of a users performance is also a design principle followed which allows for users to perform self evaluation\cite{Dincelli2020}.
+\\\\
+The findings of this case study was that making use of a gamified system that used either visual stimuli or text were better at relaying information that traditional means and visual stimuli were better than text in terms of recognition, redintegration and ease of learning and they performed similarly in terms of recall, satisfaction and usability\cite{Dincelli2020}.
+\\\\
+%---------------No. 2
 The next case study is titles \textit{"Anti-phishing phil: the design and evaluation of a game that teaches people not to fall for phish"} and focused on teaching people about phishing that is done through the use of fake websites and the ways links are used for this\cite{Sheng2007}.
 \\\\
+%---------------No. 3
 The final case study used is titled \textit{"Children’s Awareness of Digital Wellness: A Serious Games Approach"} and was targeted towards teching children, particularly preschoolers, about digital well-being and foster cyber security awareness by means of a mobile-based serious game\cite{allers2021children}
+
 \begin{table}[htbp]
 \caption{Design Principles Defined by Case Study \cite{Dincelli2020,Sheng2007,allers2021children}}
-\begin{adjustwidth}{-0.6cm}{}
+\begin{adjustwidth}{-0.0cm}{}
 \begin{tabular}{|c|c|c|c|}
@@
 Reflection	& Reflection			& Quality of Feedback and Rewards  \\
-	-		& Conceptual-Procedural & Structure of the Challenge  \\
+Feedback	& Conceptual-Procedural & Structure of the Challenge  \\
 	-		& 		-				& Motion-based Interaction  \\

### 2021-10-29 Article/main.tex
Phil Added + Hippo Highlights

@@
 %---------------No. 2
-The next case study is titles \textit{"Anti-phishing phil: the design and evaluation of a game that teaches people not to fall for phish"} and focused on teaching people about phishing that is done through the use of fake websites and the ways links are used for this\cite{Sheng2007}.
+The next case study is titles \textit{"Anti-phishing phil: the design and evaluation of a game that teaches people not to fall for phish"} and focused on teaching people about phishing and how to avoid becoming a victim to these attacks\cite{Sheng2007}.
+\\\\
+Sheng \textit{et al.}\cite{Sheng2007} made use of learning science theories in the games development and to refine the various iterations throughout the development process.
+The first two design principles discussed are \textit{reflection} and \textit{story-based agent encironment}\cite{Sheng2007}.
+These have already been mentioned  in the previous case study.
+Additionally, \textit{feedback} is also discussed in this study but specifically to how it was implemented.
+Anti-phishing Phil makes use of feedback both during, though displaying a short message for each choice during gameplay, and after a round of the game, through a score sheet and brief explanation of the links used\cite{Sheng2007}.
+\\\\
+The next design principle followed is the \textit{procedural-conceptual principle}\cite{Sheng2007}.
+It should be noted that Sheng \textit{et al.}\cite{Sheng2007} mention that procedural knowledge is also referred to as declarative knowledge.
+A similar definition to the one Kapp\cite{Kapp2012a} provides for procedural knowledge is given and as such the definition for declarative knowledge used in this study will be the one provided by Kapp\cite{Kapp2012a}.
+This principle states that these two knowledge domains, conceptual and procedural, hold a mutually supportive influence over the other\cite{Sheng2007}.
+In practice, and thus the development of a serious game, this means that learners should be given context to the processes they are being taught as without the context they may incorrectly apply processes\cite{Sheng2007}.
+\\\\
+The findings of Anti-phishing phil showed that the serious game approach made users more knowledgeable on the topic and how to go about dealing with phishing\cite{Sheng2007}.
+While the game was a success for the most part, Sheng \textit{et al.}\cite{Sheng2007} mention that the game falls behind in one aspect - some users may become more susceptible to phishing as the game provided a fixed number of indicators to be aware of.
 \\\\
 %---------------No. 3
-The final case study used is titled \textit{"Children’s Awareness of Digital Wellness: A Serious Games Approach"} and was targeted towards teching children, particularly preschoolers, about digital well-being and foster cyber security awareness by means of a mobile-based serious game\cite{allers2021children}
+The final case study used is titled \textit{"Children’s Awareness of Digital Wellness: A Serious Games Approach"} and was targeted towards teaching children, particularly preschoolers, about digital well-being and foster cyber security awareness by means of a mobile-based serious game\cite{allers2021children}.
+One thing to be noted before discussing this case study is that it focused on the design and research needed for such a serious game and stated that future work could include the development and deployment of the game\cite{allers2021children}.
+Nonetheless, due to the level of planning done for the game as well as the positive outcome from an expert review process, this case study is still a viable option to consider.
+\\\\
 
@@
 \hline
-Story-based	& Story-based 			& Clear and Simple Goals  \\
-Reflection	& Reflection			& Quality of Feedback and Rewards  \\
-Feedback	& Conceptual-Procedural & Structure of the Challenge  \\
+Story-based	& Story-based 			& Simplicity  \\
+Reflection	& Reflection			& Clear and Simple Goals  \\
+Feedback	& Feedback 				& Quality of Feedback and Rewards  \\
+	-		& Conceptual-Procedural	& Structure of the Challenge  \\
 	-		& 		-				& Motion-based Interaction  \\
-	-		& 		-				& Simplicity  \\
 \hline

### 2021-10-29 Article/main.tex
Updated refs

@@
 This will be accomplished through studying literature in the relevant fields and identifying the instances where it is viable.
+The primary question aimed to be answered by this study is \textit{what qualities are required for a serious game to be effectively used in an educational environment on various topics}.
 
@@
 Lastly, “Creation” states that learners should be able to make use of their new knowledge or skill in some personal capacity\cite{Merrill2002}.
-\\
+
 \begin{figure}[htbp]
@@
 \end{figure}
-\\
+
 The principles and corollaries provided by Merrill\cite{Merrill2002} provide an expansive and detailed structure to be used when developing any learning opportunity making it an exceptional choice to adapt specifically to a digital game learning system.
@@
 \begin{itemize}
-\item Declarative Knowledge is usually comprised of facts and jargon within a topic.
-\item Conceptual Knowledge is the grouping of related information that have an underlying common descriptor.
-\item Rules-Based Knowledge is strict statements linking concepts.
-\item Procedural Knowledge is a progression based path to reach an outcome.
-\item Soft Skills are general strategies for dealing with various social interactions.
-\item Affective Knowledge deals with topics about subjective phenomena such as emotions.
+\item Declarative Knowledge is usually comprised of facts and jargon within a topic.\\
+\item Conceptual Knowledge is the grouping of related information that have an underlying common descriptor.\\
+\item Rules-Based Knowledge is strict statements linking concepts.\\
+\item Procedural Knowledge is a progression based path to reach an outcome.\\
+\item Soft Skills are general strategies for dealing with various social interactions.\\
+\item Affective Knowledge deals with topics about subjective phenomena such as emotions.\\
 \item Psychomotor Domain deals with making use of cognitive knowledge through physical skills (hand-eye coordination is an example of this).
@@
 \\\\
+While this case study made use of instructional theory targeted towards preschool children\cite{allers2021children, callaghan2018}
 

### 2021-10-29 Article/main.tex
Finished Findings + Limitations

@@
 \\\\
-While this case study made use of instructional theory targeted towards preschool children\cite{allers2021children, callaghan2018}
+While this case study\cite{allers2021children} made use of instructional theory targeted towards preschool children\cite{matthews2007,callaghan2018} some the frameworks and learning theory used can also be applied to all serious games.
+The first design principle followed was \textit{simplicity} as it allows a user to follow the content adequately and as such learn effectively\cite{allers2021children}.
+This principle is specified to the success of a awareness campaign however can also be applied to a serious game as, depending on the specific level of education, simplicity is vitally important.
+\\\\
+The study goes on to cite Matthews \textit{et al.}\cite{matthews2007} on the ways children tend to learn. This includes:
+\begin{itemize}
+\item Observation
+\item Listening
+\item Exploring
+\item Experimentation
+\item Asking questions
+\end{itemize}
+\vspace*{\baselineskip}
+
+Learning through play, such as a serious game, is an effective way to implement all of these methods\cite{allers2021children} and as such provides an additional framework targeted specifically at younger children as opposed to the previous studies\cite{Dincelli2020,Sheng2007} which were focused on adults.
+While this list does not provide direct principles to follow during the design process, including ways for these methods of learning to be present in a serious game should also be taken into consideration.
+\\\\
+In addition to the above, the study also made use of several elements identified by Callaghan \textit{et al.}\cite{callaghan2018} which are based off how young children, namely preschoolers, learn.
+The first of these is \textit{clear and simple goals} which is concerned with presenting a user with concise outcomes to work towards\cite{callaghan2018}.
+Similarly with Anti-phishing phil\cite{Sheng2007}, is the element of \textit{quality of feedback and rewards} which deals with how feedback is presented to a user - for example preschoolers may not yet be able to read and as such the feedback must be structured accordingly such as making use of simple visuals\cite{allers2021children}.
+The next element is \textit{Structure of the challenge} consists of setting the difficulty of tasks and changing the difficulty depending on how the user is performing\cite{callaghan2018}.
+This element can also be described using some of the corollaries from Merril's First Principles\cite{Merrill2002} - which will be discussed in the following section.
+The last element Callaghan \textit{et al.}\cite{callaghan2018} is that of \textit{Motion based learning} which describes the physical interaction a user will have with applications which in this case would be designing larger touch controls to account for a preschool child's current level of motor functions.
+This particular aspect is almost certainly vital when dealing with any knowledge from the psycho motor domain.
+\\\\
+As previously mentioned, this case study has not yet developed the serious game and as such cannot be tested by users.
+However, a expert review was conducted on the design of this serious game of which the outcomes were largely positive as the reviewers "found the implementations of each element satisfactory"\cite{allers2021children}.
+\\\\
 
 \begin{table}[htbp]
-\caption{Design Principles Defined by Case Study \cite{Dincelli2020,Sheng2007,allers2021children}}
+\caption{Design Principles Defined by Case Study (Summarised) \cite{Dincelli2020,Sheng2007,allers2021children}}
 \begin{adjustwidth}{-0.0cm}{}
@@
 \section{Limitations and Future Research}
+This study made use of various fields of study as well as case studies of serious games and their design in order to answer the question posed.
+The current limitations of answering the question largely center around the amount of literature sourced.
+In terms of the fields looked at (pedagogy, ludology and gamification) these seem to be sufficient in terms of what literature can be used and as such it is the specific literature used that imposes limitations.
+There are many more instructional theories that could be considered and as such future research could delve into more theories and expand the knowledge base used to answer the question.
+Another limitation comes from the case studies used.
+All of the main case studies discussed in this article had a focus on computer security to varying degrees.
+Due to this, future research could include case studies on the design, implementation or development of serious games in other fields.
+\\\\
+Furthermore, a more practical approach to future research could include the development of a serious game on a topic based in one of the knowledge domains mentioned.
+This could include the development an artefact for user testing, similarly to Anti-phishing phil\cite{Sheng2007}, based of the synthesis provided or the designing of such an artefact more in line with the "Happy Hippo" game\cite{allers2021children}.
+
+\section{Conclusion}
 

### 2021-10-30 Article/main.tex
Formatting Fixes
Conclusion Started

@@
 The next case study is titles \textit{"Anti-phishing phil: the design and evaluation of a game that teaches people not to fall for phish"} and focused on teaching people about phishing and how to avoid becoming a victim to these attacks\cite{Sheng2007}.
-\\\\
+\\
 Sheng \textit{et al.}\cite{Sheng2007} made use of learning science theories in the games development and to refine the various iterations throughout the development process.
@@
 \end{itemize}
-\vspace*{\baselineskip}
 
@@
 However, a expert review was conducted on the design of this serious game of which the outcomes were largely positive as the reviewers "found the implementations of each element satisfactory"\cite{allers2021children}.
-\\\\
 
-\begin{table}[htbp]
-\caption{Design Principles Defined by Case Study (Summarised) \cite{Dincelli2020,Sheng2007,allers2021children}}
-\begin{adjustwidth}{-0.0cm}{}
+\begin{table}[h]
+\caption{Design Principles Defined by Case Study \cite{Dincelli2020,Sheng2007,allers2021children}}
+\begin{adjustwidth}{-0.5cm}{}
 \begin{tabular}{|c|c|c|c|}
@@
 Furthermore, a more practical approach to future research could include the development of a serious game on a topic based in one of the knowledge domains mentioned.
-This could include the development an artefact for user testing, similarly to Anti-phishing phil\cite{Sheng2007}, based of the synthesis provided or the designing of such an artefact more in line with the "Happy Hippo" game\cite{allers2021children}.
+This could include the development an artefact for user testing, similarly to Anti-phishing phil\cite{Sheng2007}, based off of the findings of this study or the designing of such an artefact more in line with the "Happy Hippo" game\cite{allers2021children}.
 
 \section{Conclusion}
+This study discussed the current state of the paradigms that instructional institutions are based off of and how society has progressed and developed different needs than the systems in place currently provide.
+As such, research into how serious games can be used in an educational environment was conducted with specific focus on the fields of pedagogy, ludology and gamification in order to answer the question, \textit{what qualities are required for a serious game to be effectively used in an educational environment on various topics}.
+Through a literature review in these fields, various instructional theories were found that could be helpful to answer the question as they are able to be translated into the context of games relatively easy.
+Furthermore, several research papers were used as case studies to discover what design principles are typically followed in the development of serious games.
+This information was then used to....
 

### 2021-11-01 Article/main.tex
Updates
Updated Article -> Synthesis

@@
 Kapp\cite{Kapp2012a}, in addition to providing definitions of the various knowledge domains, provides some ways that each domain can be taught to best relay that particular type of knowledge.
-While these reconsiderations are derived under a gamification perspective, that can just as easily be applied for a digital game.
+While these recommendations are derived under a gamification perspective\cite{Kapp2012a}, that can just as easily be applied for a digital game:
 
@@
 \item
-Games that would involve some form of sorting and matching are ideal for teaching declarative knowledge\cite{Kapp2012a}.
+Games that would involve some form of sorting and matching are ideal for teaching declarative knowledge.
 \item
-Conceptual knowledge is beast taught through demonstrations and once again a sorting type game where the sorting is based on the common trait of the content or topic\cite{Kapp2012a}.
+Conceptual knowledge is beast taught through demonstrations and once again a sorting type game where the sorting is based on the common trait of the content or topic.
 \item
-A demonstration that displays the failure of not complying with the rules is helpful for a topic under the rules-based knowledge domain\cite{Kapp2012a}.
+A demonstration that displays the failure of not complying with the rules is helpful for a topic under the rules-based knowledge domain.
 \item
-Procedural knowledge is best taught through having the learners work through the procedure itself in some means\cite{Kapp2012a}.
+Procedural knowledge is best taught through having the learners work through the procedure itself in some means.
 \item
-Soft Skills are best taught through having the learner repeatedly apply the skill in question u=in various scenarios\cite{Kapp2012a}.
+Soft Skills are best taught through having the learner repeatedly apply the skill in question u=in various scenarios.
 \item
-Immersing the learner within a phenomena found in the affective knowledge domain is a neffective means of teaching them about it\cite{Kapp2012a}.
+Immersing the learner within a phenomena found in the affective knowledge domain is an effective means of teaching them about it.
 \item
-Kapp\cite{Kapp2012a} states that observation is an ideal method of teaching the learner about a topic in this domain.
+Kapp\cite{Kapp2012a} states that observation is an ideal method of teaching the learner about a topic in the psychomotor domain.
 \end{itemize}
@@
 This principle is specified to the success of a awareness campaign however can also be applied to a serious game as, depending on the specific level of education, simplicity is vitally important.
-\\\\
+\\\\\\
 The study goes on to cite Matthews \textit{et al.}\cite{matthews2007} on the ways children tend to learn. This includes:
@@
 The last element Callaghan \textit{et al.}\cite{callaghan2018} is that of \textit{Motion based learning} which describes the physical interaction a user will have with applications which in this case would be designing larger touch controls to account for a preschool child's current level of motor functions.
-This particular aspect is almost certainly vital when dealing with any knowledge from the psycho motor domain.
+This particular aspect is almost certainly vital when dealing with any knowledge from the psychomotor domain.
 \\\\
@@
 \section{Synthesis from Research}
+From the literature and case studies examined, there are several key qualities that they share among each other either under the same descriptor or with similar descriptions with different names.
+It is these qualities that will form the basis to answer the question posed in the beginning of this study.
+\\\\
+The first quality is shared amongst Merrill's First Principles\cite{Merrill2002} and two of the case studies\cite{Dincelli2020,Sheng2007}.
+\textit{Reflection} is then a vital quality to a serious game if intended to be used in an educational environment and is described as giving a user some time after being presented with new knowledge or a task to dwell on what they have experienced.
+\\\\
+The second quality a serious game should make use of is that of \textit{Feedback}.
+All of the case studies\cite{Dincelli2020,Sheng2007,allers2021children} mention as such and Merrill\cite{Merrill2002} refers to it under the diminishing coaching corollary.
+A user should be presented with feedback on how they are progressing on a given set of tasks within the game at some point and as they progress the amount of feedback should be slowly diminished.
+The feedback amount should also be tied to the performance of the user - increasing if they begin to struggle and decrease if not.
+Since feedback can take on many different forms, the type of feedback as well as the method of delivery is dependant on the topic being taught.
+\\\\
+Another quality that should be implemented is that the serious game should showcase and teach topics through the use of \textit{Story-telling}.
+The case studies\cite{Dincelli2020,Sheng2007,allers2021children} all mention the use of this and John Keller's ARCS model\cite{keller1987development}, specifically under the attention element, also states that this is a proponent of keeping users engaged.
+A game should then allow for a story to take place during the teaching of a topic which can also be done in several ways - such as contextually with Anti-phishing phil or as the main focus of the topic as with the SETA artefact\cite{Dincelli2020} and Happy Hippo\cite{allers2021children}.
+Another means to accomplish this is to make use of an agent that guides the user through the game.
+\\\\
+
 \subsection{Recommendations per Knowledge Domain}
@@
 Furthermore, several research papers were used as case studies to discover what design principles are typically followed in the development of serious games.
-This information was then used to....
+This information was then used to identify what are the major qualities which a serious game should have in order to be effective in a educational environment as well as providing specific recommendations for various knowledge domains.
+The qualities identified were allowing for Reflection, providing Feedback, making use of Story elements and Structuring.
 

### 2021-11-01 Article/main.tex
Article Finished

@@
 \documentclass[conference]{IEEEtran}
-\IEEEoverridecommandlockouts
+%\IEEEoverridecommandlockouts
 % The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
@@
 \item
-Soft Skills are best taught through having the learner repeatedly apply the skill in question u=in various scenarios.
+Soft Skills are best taught through having the learner repeatedly apply the skill in question within various scenarios.
 \item
@@
 \caption{Design Principles Defined by Case Study \cite{Dincelli2020,Sheng2007,allers2021children}}
-\begin{adjustwidth}{-0.5cm}{}
+\begin{adjustwidth}{-0.6cm}{}
 \begin{tabular}{|c|c|c|c|}
@@
 Since feedback can take on many different forms, the type of feedback as well as the method of delivery is dependant on the topic being taught.
+As part of this quality, a serious game should also be designed to create an environment in which users are able to complete smaller tasks and are rewarded for these smaller successes - as per the ARCS model\cite{keller1987development}.
 \\\\
@@
 A game should then allow for a story to take place during the teaching of a topic which can also be done in several ways - such as contextually with Anti-phishing phil or as the main focus of the topic as with the SETA artefact\cite{Dincelli2020} and Happy Hippo\cite{allers2021children}.
-Another means to accomplish this is to make use of an agent that guides the user through the game.
+Another means to accomplish this is to make use of an agent that guides the user through the game which can be used in accordance with the Learner Guidance corollary from Merrill's First Principles\cite{Merrill2002}.
 \\\\
+The last major quality a serious game should possess is that of \textit{Structuring}.
+This quality refers more to the content the game will deal with in terms of the instructions given as well as how the difficulty of problems could progress.
+It is derived from both Merrill's First Principles\cite{Merrill2002}, the ARCS model\cite{keller1987development} as well as the framework by Callaghan\cite{callaghan2018}.
+From the ARCS model\cite{keller1987development}, specifically Confidence, and Callaghan's\cite{callaghan2018} framework it is clear that a serious game should be structured with simple goals and clear expectations from the user and by structuring a game's instructions in this manner the user will be motivated to continue playing and therefore learning.
+Structuring the problems and tasks within the game should follow a similar method to how Feedback is provided - increasing the difficulty as a user gets them correct and lessening the difficulty when they are struggling to once again keep engagement with the game high.
+Merrill's First Principles\cite{Merrill2002} discusses this quality in several Principles and their subsequent corollaries - some of which refer to the difficulty scaling mentioned above.
+As such, a serious game's structure should be centred around the problems themselves - or the knowledge being taught when dealing with Affective knowledge and soft skills.
+The tasks given to a user should be both varied to keep the users' attention as well as be consistent in the ways the user interacts with them.
+This approach should keep users motivated to use the game according to the ARCS model\cite{keller1987development} as it makes use of both the Attention and Relevance elements.
+\\\\
+While the remaining aspects of the pedagogical theories and design principles from the case studies are also useful in the implementation of a serious game, they are specific to the content being taught and as such should be considered in greater detail if a similar game to those were to be developed.
 
-\subsection{Recommendations per Knowledge Domain}
+\subsection{Recommendations for Specific Knowledge Domains}
+Kapp's\cite{Kapp2012a} recommendations are a helpful starting point to how to effectively teach content relating to the knowledge domains. 
+\\\\
+Referring back to Squire's\cite{Squire2003} descriptions of games as simulations - both Hi-fidelity and low fidelity.
+These types of serious games are certainly the most useful for teaching content found in the Affective, Soft Skills and Psychomotor domains since the best means to teach these is through immersing the user in the phenomena, repeated application of skills and observation respectively\cite{Kapp2012a}.
+Simulation-type serious games can also be used in the other domains such as with the game used to aid in teaching physics described by Deshpande and Huang\cite{Deshpande2011}.
+These types of games are also the most effective means for the psychomotor domain as shown by various studies\cite{Burke2009, Costanza2014, Ranalli2008, Tao2009}.
+\\\\
+The remaining knowledge domains tend to have some heavy overlap depending of the topic being covered.
+Sheng \textit{et al.}\cite{Sheng2007} discussed the Conceptual-Procedural principle in their game's development.
+To reiterate, it simply states that a topic cannot be fully understood from only the procedures or context - both are needed for a deeper understanding.
 
@@
 There are many more instructional theories that could be considered and as such future research could delve into more theories and expand the knowledge base used to answer the question.
+Future research could also include looking at various types of games and how they could teach content in the different knowledge domains to build upon Kapp's\cite{Kapp2012a} recommendations.
 Another limitation comes from the case studies used.
@@
 This information was then used to identify what are the major qualities which a serious game should have in order to be effective in a educational environment as well as providing specific recommendations for various knowledge domains.
-The qualities identified were allowing for Reflection, providing Feedback, making use of Story elements and Structuring.
+The qualities identified were allowing for Reflection, providing Feedback, making use of Story elements and a well thought out Structuring of the game.
+Recommendations for the different knowledge domains were also given.
+\\
+\section*{Acknowledgements}
+This article was part of a research project for an Honours degree and as such I would like to thank my supervisor, Günther Drevin, for their aid throughout the year as well as for the lessons on the field of ludology as well as the School of Computer Science and Information Systems at the North West University for providing this opportunity.
 

### 2021-11-02 Final Doc/Chapters/Chapter1.tex
Added gantt chart to final doc
Added Ch1 to Final Doc

@@
 \section{Project Description}
+A student’s learning experience is typically affected by their enjoyment of interacting with the material and their general interest in the topic material presented.
+As such, a student will have their own individual preferences and style of learning.
+Due to the rapid and prevalent development of technology, using video games as a means of teaching has been a topic of discussion.
+\\\\
+This project aims to create an artefact in the form of a digital game and incorporate specific qualities into one level to demonstrate how a game may be used in a learning environment through the example of an “advanced game tutorial” that aims to not only act as the usual tutorial phase of the game but also to infer certain information about the game’s assorted enemy types.
 
@@
 \subsection{Problem Description and Background}
+Education as it stands is still built on a system that is no longer needed in modern society.
+Ackoff and Greenberg (2008) explain that the current traditional methods of teaching are no longer as relevant as they once were as it is aimed to produce members of society that were likely to not question any fundamental aspects of how things operated.
+It is largely a system that focuses on teaching while disregarding learning as the last major stride in development in education was to industrialise it – having them operate efficiently like factories.
+Ackoff (1991) discusses that while learning is the advancement of one’s understanding and knowledge on a given topic or subject, this can happen in the complete absence of teaching, which is the explanation of a subject from one person to another.
+The opposite of this is also true, teaching may occur with no learning.
+\\\\
+One major flaw with this system currently is that it stifles the creativity and drive of some students as each level of education is largely the same and as such monotonous.
+As such, education needs some form of system to create an interest in learning for the students or risk providing only a means of teaching without individual students learning (\cite{Ackoff2008}).
+It is therefore vital to provide learners in all levels of education with engaging content or methods of delivery that they will enjoy will cause them to be more motivated to learn and look further into that specific topic (\cite{Ackoff2008}).
+\\\\
+With the recent developments in technology and the fact that technology, in general, becoming more accessible, some institutions have adopted some forms of digital learning or assist traditional teaching with digital assistance.
+Deshpande and Huang (2011) state that the current generation of students is the first to grow up with abundant access to technology.
+They continue to state that, on average, these students spend almost double the time playing video games as they do reading (\cite{Deshpande2011}).
+\\\\
+Virvou, Katsionis and Manos (2005) echo the point that computer games are popular among individuals who are in schools and as such could provide a means to deliver content in an interesting and engaging manner.
+As such, the motivation behind this study is to further investigate the possibility of using video games as a means to encourage learning in teaching environments as current means of teaching may not be optimal for some individuals.
+
+\begin{figure}[H]
+\centering
+\includegraphics[scale=0.5]{atlantis}
+\caption{Example (Quest Atlantis) of an Educational Game}
+\end{figure}
+
+According to Annetta (2008), the movement for the inclusion of digital games to be used in teaching and training environments first started in 2003, two years after the field of ludology, the study of games, began to gain traction in academic literature.
+This initiative is what started the concept of a serious game as one that can be used in an academic sense to relay information.
+After this point in time, various examples of serious games were made for purely academic study purposes and had found a very large use in simulation for use as explanation aides and medical training.
+\\\\
+The use of games as simulations may stretch the colloquial definition of a video game but in academic terms, this is one facet of video games.
+Frasca (2002) cites that simulations, such as the ones discussed above, can fall into one of two categories, namely; Paidea (play) and Ludus (game).
+“Play” refers to the simulations that lack any defined set of rules and conditions to meet a fixed goal while “Game” refers to a simulation that has these conditions and a user can directly, according to the predetermined rules, move towards a fixed goal (\cite{Frasca2002}).
+\\\\
+From the abovementioned definitions and examples, there is a loose description of what a serious game typically looks like and where it can be applied.
+However, the qualities needed by these games to effectively relay information has not been directly explained in any one piece of literature.
+There is also a lack of explanation on how these qualities can be applied to a game to result in what may be described as a serious game.
+
 \subsection{Overview of Related Literature}
+Annetta (2008) discusses multiple examples of these games, such as Discover Babylon and Quest Atlantis, that had been developed to immerse children and young adolescents in an academic environment.
+Further examples of the use of serious games have already had an impact on the military, medical and higher business education fields early in their conception and this trend continues to this day with most serious games being used within the medical fields specifically (\cite{Annetta2008}).
+\\\\
+Deshpande and Huang (2011) describe the use of games as a means of simulation for specific sections of work in physics and engineering courses as an addition to traditional teaching as it provides a relatively simple way to demonstrate certain phenomena.
+As such these authors discuss the simulation aspect of games rather than the narrative.
+\\\\
+The endeavour to create serious games has yet to reach schools due to certain criticisms about games in general which hinder the adoption of games as a means of teaching and learning (\cite{Virvou2005}).
+\\\\
+The study of serious games became more theoretical and discussion-based at lower levels and more applied with actual use at higher levels, with a great impact on medical fields and training.
+As such, there is a fair amount of theoretical research on specific aspects that relate to serious games as simulations and within ludology as a whole, but only a few mention the qualities a game needs to better present information to a user.
+
+\begin{figure}[H]
+\centering
+\includegraphics[scale=0.4]{soil}
+\caption{Example of Using a Game to Simulate Soil Erosion}
+\end{figure}
+
 \subsection{Research Question and Expected Outcomes}
+The main research question this project is set out to answers is; “What qualities does a video game require in order for it to be useful in relaying certain information to a user whilst still maintaining proper engagement with the user?”.
+The findings resulting from answering this question will be used in the development of a specific video game level that will attempt to teach users about the games various mechanics and enemy types presented.
+\\\\
+The expected outcomes of this project is the aforementioned game as the artefact as well as a description of the qualities a game must exhibit to effectively relay information in an educational sense.
 
 \section{Aims and Objectives of Project}
+The primary aim of this study is to identify what qualities and principles can be applied to a video game to allow it to be used in a learning environment as a means to provide better engagement among certain students by providing an enjoyable delivery of information.
+\\\\
+To effectively reach the aforementioned aim, all the following objectives will have to be met as certain objectives will benefit from the completion of others:
+\begin{enumerate}
+\item A literature study will need to be performed to gather information with a focus on:
+\begin{enumerate}
+\item Ludology, narratology and simulation to better understand the academia centred around this project;
+\item Other implementations of serious games and the qualities they possess;
+\item The impact and effects of games in early development as this is the main “target audience” if this project were to be implemented as well as in a more general sense;
+\item Previous attempts to integrate game use in learning.
+\end{enumerate}
+\item Collect examples of games that employ some form of teaching:
+\item Where objective 1-ii focuses on examples already discussed in an academic sense, this objective will make use of more informal analysis
+\end{enumerate}
+
+The next aim of this project is to develop an artefact which will require the following objectives:
+\begin{enumerate}
+\item Learn and understand how to use the chosen development platform and associated environments;
+\item Develop a base to build other levels/scenes off of;
+\begin{enumerate}
+\item Development of basic scripts needed.
+\end{enumerate}
+\item Create a specific scene/level within the aforementioned artefact that specialises in delivering information through various audio-visual stimuli that incorporates the principles and qualities found.
+\end{enumerate}
 
@@
 \subsection{Research Paradigm and Methodology Used}
+The research aspect of this project will be conducted in accordance with the interpretivist paradigm.
+The main undertaking of this paradigm is to understand the world and its’ various aspects according to the subjective experiences of people (\cite{kivunja2017understanding}).
+It is due to this reason that this project uses this paradigm as what each student requires to efficiently learn is subjective to each individual.
+Kivunja and Kuyini  (2017) further mention that the interpretivist paradigm makes use of subjective epistemology which allows the researcher to analyse the data, which in this project is the principles and qualities that allow for a game to be effective in a learning environment, through their individual cognitive processes.
+\\\\
+Kivunja and Kuyini (2017) continue to list certain characteristics of research conducted under this paradigm typically possess.
+These include the understanding that the social world cannot be fully comprehended from one standpoint which is why this project makes use of various other studies in the compilation of the aforementioned principles and qualities.
+Another is that knowledge and its’ understanding is developed through the findings of the study itself.
+\\\\
+Design science is a methodology composed of using analytical techniques and can be used according to many paradigms to perform research in the information systems field (\cite{vaishnavi2004design}).
+This means of research centres on the development of artefacts to better understand certain aspects through the creation of new knowledge and that assessment of an artefacts performance (\cite{vaishnavi2004design}).
+This methodology was chosen as it provides certain outlines that will allow for the development and analyses of the principles and qualities for a game to be used academically through the creation of such artefact incorporation these qualities into its’ design and development.
+\\\\
+Design Science also provides a general structure as to how this project will be completed as shown in Figure 3 below taken from Vaishnavi and Kuechler’s (2004) work.
+This process allows for the development of an artefact alongside the collection of information and knowledge that can be incorporated into the design and development of the artefact as well as the evaluation of the implementation of the qualities onto the artefact.
+
+\begin{figure}[H]
+\centering
+\includegraphics[scale=0.6]{ds}
+\caption{The Design Science Research Process (\cite{vaishnavi2004design})}
+\end{figure}
+
 \subsection{Collection of Data}
+This project will collect data in the form of literary studies and real-world examples of serious and educational games.
+The main channel of processing this data will be in the form of a literature review and consequential implementation of the findings in an article.
+
 \subsection{Development of Artefact}
+The artefact that will be developed as a part of this project will be a computer video game that will be developed as a group effort.
+This game will be a standalone artefact with no major links to each group members research – it may, however, be influenced by them.
+Due to the expansive nature of game design, the Agile software development life cycle will be used.
+Following this cycle of development allows for the artefact to be developed in smaller increments through the use of iterative cycles and regular meetings about the design and features of the artefact (\cite{highsmith2001agile}).
+According to Highsmith and Cockburn (2001), Agile also allows for “dynamic prioritisation” which allows for the shifting of development to other aspects if they urgently require more attention over others on short notice.
+Agile also makes use of constant testing which ensures that defects and issues are found and dealt with quickly (\cite{highsmith2001agile}).
+Most importantly, the development of the artefact will be continuous from the start date and will make use of weekly scrums, or discussion-based meetings on what should be developed, to ensure a regular flow of development on the game.
+
 \subsection{Integration with Other Projects}
+The development of an artefact as part of this project is being conducted alongside two other students, one focusing on the different effects on cognition from various genres and the other dealing with the controls of games.
+These other projects are conducted by:
+\begin{itemize}
+\item GC Wehmeyer (29977339)
+\item Rickus Trollip (30083575)
+\end{itemize}
+These other projects only integrate with this one when concerning the artefact that will be developed as each will conduct a fully indecent research study and, if applicable, develop any other questionnaires or models independently.
+The development of the artefact will be done as a group effort and as such the computer game that will be developed for this project may be impacted by the findings of these other projects.
 
@@
 \subsection{Provisional Project Plan}
+The provisional project plan is discussed below and specific dates of completion may shift due to unforeseen circumstances.
+This project began on the 15th of February 2021 and will be fully completed by the 8th of November 2021.
+During this period the project has certain deadlines for particular deliverables that will need to be adhered to.
+
+\begin{enumerate}
+\item The first of these is the project planning and research proposal which must be completed and submitted by the 18th of April 2021.
+The research proposal will cover a substantiation of the project and its feasibility.
+The project planning includes a project description with the research question, the main aims and objectives of the project, a detailed explanation of the developmental process of the project, and a description of what will be used in the development of the project.
+
+\item Following this, a literature study regarding Ludology as a whole, implementations of serious games, the qualities they possess, the impact and effects of games and previous attempts to integrate game use in learning.
+This literature review is set to be completed for submission by the 13th of June 2021.
+
+\item The next deliverable for this project is the demonstration of the artefact and the development of a video presentation on the 1st of November 2021.
+This deliverable will be met by continuously developing the artefact according to provisional dates shown in Figure 4 below.
+
+\item The final deliverable is the final documentation of the entire project that consists of all previous deliverables as one document with certain additions.
+This deliverable must be completed and submitted by the 8th of November 2021.
+\end{enumerate}
+
+A more detailed breakdown of the project plan is presented in Figure 4 below with provisional dates for the deliverables and the anticipated objectives required to meet them.
+
+\begin{figure}[H]
+\centering
+\includegraphics[scale=0.75]{gantt}
+\caption{Provisional Project Plan}
+\end{figure}
+
 \subsection{Scope}
+This project is split into two distinct parts.
+First is the research aspect that will be conducted individually which involves the review and analysis of literature and examples of serious games.
+This aspect aims to find and describe the qualities and principles that could allow a game to be used in a learning environment.
+\\\\
+The second aspect of this project is the development of a computer game as the artefact.
+This artefact will be developed as a group effort with each member focusing on specific areas of development and all members having some contribution to other areas.
+
+\subsection{Limitations}
+The most notable limitation towards this project is that it must be completed according to a fixed time frame which is provisionally set out as follows:
+\begin{itemize}
+\item Submission of the project plan and research proposal on 18th April 2021
+\item Submission of the literature study on 13th June 2021
+\item Demonstration of the artefact and a poster on 1st November 2021
+\item Submission of the complete documentation of the project on 8th November 2021
+\end{itemize}
+Other time constraints will be applied according to certain aspects of development, such as meetings or self-imposed deadlines, which can only be set at a later date.
+\\\\
+As will be discussed in 1.6, the artefact will make use of third party resources and as such is limited to what is publicly available at no cost as not to apply any financial constraints on the projects involved with the artefact.
+\\\\
+Since the artefact developed is a digital computer game, the demonstration and development of it will require a system that meets the requirements for the associated development platform and environments.
+As such the artefact is limited to systems with the following minimum requirements - as described by Unity:
+\begin{itemize}
+\item Windows 7;
+\item Processor with x64 architecture;
+\item A capable graphics processing system with DX10, DX11 and DX12 functionality.
+\end{itemize}
+
+\subsection{Risks and SWOT Analysis}
+The project will have risks associated with the artefact, which will be discussed below.
+\\\\
+Firstly, is the risk of scope creep.
+As the planning only depicts and describes the basic structure and aims of the project, once development on the artefact begins the specifications and features may continue to increase in number which may cause the project to fail expectations set.
+As such, the intended features of the artefact should be discussed and solidified early on in its’ development to mitigate this specific risk.
+\\\\
+The artefact’s development and the research aspect of this project is also at risk of unforeseen events.
+In an attempt to mitigate the harm that may be caused by these events, the artefact is being developed in such a manner to facilitate both contact sessions as well as fully digitally.
+
 \subsection{Contributions of Each Group Member}
+This project has an element of group work as the artefact that will be developed will be done as a group.
+Each member of the group will be responsible for different aspects of the development of the artefact such as, but not limited to;
+\begin{itemize}
+\item focusing on the animation of models, 
+\item development of character controls, 
+\item developing a simple artificial intelligence for the enemy characters;
+\item narrative design and 
+\item level layout and design. 
+\end{itemize}
+Members may be fully responsible for the contribution of the aforementioned areas while other aspects may be worked on by all members concurrently.
+The specific areas that a group member will contribute towards will be discussed when the artefact begins proper and continuous development.
+\\\\
+However, it should be noted that each member is still solely responsible for their individual research study project that may directly or indirectly link to the artefact.
 
@@
 \subsection{Development Platform}
+The main platform for the development of the artefact will be the Unity game editor developed by Unity Technologies.
+The 2019.4.22f version of the program will be used as it is marked as one of the publicly availably versions that is depicted to get long term support and as such should provide a fair balance of features and stability required for the development of this artefact.
+Unity is also equipped with various tools for the development of games, such as Probuilder which allows for the construction and editing of basic three-dimensional objects and will also be included in the development of the artefact.
+Other tools provided by Unity may also be employed in the development of the artefact as they become needed.
+Unity was chosen for the development of the artefact as it is a fairly popular game development platform and as such has a fair amount of introductory courses and tutorials on its’ use.
+\\\\
+GitHub will be used in the development of the artefact to allow for a simplified way to quickly share any changes made to the artefact and track the contributions towards the artefact's development by all members involved.
+Hence, a repository for the artefact's files will be initialised and then used throughout its’ development life cycle.
+A programmer can quickly download (pull) and upload (push/commit) their changes to a project with this platform.
+The desktop client GitHub is used to facilitate all the operations discussed above.
+GitHub’s repository features will be used for the ease it provides in communicating changes between the various developers of the artefact.
+\\\\
+Other development platforms may be used in the development of the artefact if they are required.
+One such example of this is Blender, a 3D modelling program that allows for the creation of three-dimensional objects and models and may be used if need be in the editing of models used.
+As such other programs currently not specified may be used for the artefact's development; specifically, in areas that Unity does not directly cater for.
+
 \subsection{Resources}
+The Unity Asset Store will be used to acquire 3D models to be used within the artefact to complete the artefact within the given time frame since this is one aspect of game development that is very time-consuming.
+In a similar vein, Mixamo.com will be used to acquire animations for the artefact as this is another time-consuming process.
+\\\\
+A list of all resources used will be compiled and the relevant creators and/or distributors will be referenced in the artefacts final documentation.
+
 \subsection{Environments}
+Microsoft's Visual Studio IDE will be used for the creation and development of most of the scripts and classes that will be implemented into the Unity game editor.
+This specific IDE was chosen as it has some basic integration with the Unity editor and can be installed directly from and during the Unity editor's initial installation.
 
 \section{Ethical Implications of Project}
+This project will not make use of external participants in a formal manner that would require any ethical implications as the only participants towards the development of this projects is the developers working on the artefact itself.
+The prescribed ethics form has been completed and attached.
 
 \section{Provisional Chapter Division}
+This document will contain a bulk of the final project documentation and the associated literature study.
+It will be divided into separate chapters which are listed below with a brief description of the respective content.
+\\\\
+\textbf{Chapter 1: Introduction} \\	
+The problem that is being researched, the qualities of games needed for use in education, is discussed in Chapter 1.
+Information on the background of this problem, similar research and the research contribution will be discussed.
+Furthermore, the aim of the study in addition to the planned method of conduct will be discussed.
+\\\\
+\textbf{Chapter 2: Literature Study} \\
+Chapter 2 will discuss the impact of games both in early development and in general in more detail, the accessibility of games as well as a focus on games being used in learning.
+It will attempt to find what qualities and principles work best to make a game a suitable means of learning.
+\\\\
+\textbf{Chapter 3: Development of Accompanying Artefact} \\
+The accompanying artefact that will be developed as a part of the study will be discussed along with the development process of the artefact.
+\\\\
+\textbf{Chapter 4: Review of Collected Data} \\
+The means of data collection, processing and analysis will be discussed in this chapter along with the results of this data.
+As this project pertains to the application of knowledge towards an artefact, this section will mostly discuss the underlying principles and qualities that make for a game to be used in a learning capacity.
+\\\\
+\textbf{Chapter 5: Discussion on Results} \\
+A discussion on the results obtained will be presented in this chapter.
+This chapter will focus more on the application of the acquired knowledge and principles towards the development of the artefact.
+\\\\
+\textbf{Chapter 6: Conclusion} \\
+The contents and results of the study will be briefly discussed and reiterated in an overview.
+\\\\
+\textbf{Reference List}
+Contains all literary works referenced in the project.

### 2021-11-02 Final Doc/main.tex
Update Article
Added gantt chart to final doc
Added Ch1 to Final Doc

@@
 ]{MastersDoctoralThesis} % The class file specifying the document structure
-
+\usepackage{graphicx}
+\usepackage{float}
 \usepackage[utf8]{inputenc} % Required for inputting international characters
@@
 
-\usepackage[backend=bibtex,style=authoryear,natbib=true]{biblatex} % Use the bibtex backend with the authoryear citation style (which resembles APA)
+\usepackage[backend=biber,style=apa,natbib=true]{biblatex} % Use the bibtex backend with the authoryear citation style (which resembles APA)
 
-\addbibresource{example.bib} % The filename of the bibliography
+\addbibresource{honsDoc.bib} % The filename of the bibliography
 
@@
 %----------------------------------------------------------------------------------------
+%	BIBLIOGRAPHY
+%----------------------------------------------------------------------------------------
+
+\printbibliography[heading=bibintoc]
+
+%----------------------------------------------------------------------------------------
 %	THESIS CONTENT - APPENDICES
@@
 %----------------------------------------------------------------------------------------
-%	BIBLIOGRAPHY
-%----------------------------------------------------------------------------------------
-
-\printbibliography[heading=bibintoc]
-
-%----------------------------------------------------------------------------------------
 

### 2021-11-02 Final Doc/Chapters/Chapter1.tex
Added Chapter 2 to Final Docs

@@
 \newcommand{\code}[1]{\texttt{#1}}
-\newcommand{\file}[1]{\texttt{\bfseries#1}}
+\newcommand{\file}[1]{\1texttt{\bfseries#1}}
 \newcommand{\option}[1]{\texttt{\itshape#1}}
@@
 \section{Project Description}
-A student’s learning experience is typically affected by their enjoyment of interacting with the material and their general interest in the topic material presented.
+A student's learning experience is typically affected by their enjoyment of interacting with the material and their general interest in the topic material presented.
 As such, a student will have their own individual preferences and style of learning.
@@
 They continue to state that, on average, these students spend almost double the time playing video games as they do reading (\cite{Deshpande2011}).
-\\\\
+\newpage
 Virvou, Katsionis and Manos (2005) echo the point that computer games are popular among individuals who are in schools and as such could provide a means to deliver content in an interesting and engaging manner.
@@
 \centering
-\includegraphics[scale=0.5]{atlantis}
+\includegraphics[scale=0.5]{Figures/atlantis}
 \caption{Example (Quest Atlantis) of an Educational Game}
@@
 As such these authors discuss the simulation aspect of games rather than the narrative.
-\\\\
+\\\\\\
 The endeavour to create serious games has yet to reach schools due to certain criticisms about games in general which hinder the adoption of games as a means of teaching and learning (\cite{Virvou2005}).
@@
 \centering
-\includegraphics[scale=0.4]{soil}
+\includegraphics[scale=0.4]{Figures/soil}
 \caption{Example of Using a Game to Simulate Soil Erosion}
@@
 \end{enumerate}
-\item Collect examples of games that employ some form of teaching:
-\item Where objective 1-ii focuses on examples already discussed in an academic sense, this objective will make use of more informal analysis
+\item Collect examples of games that employ some form of teaching 
+(\textit{Where objective 1-b focuses on examples already discussed in an academic sense, this objective will make use of more informal analysis})
 \end{enumerate}
@@
 \centering
-\includegraphics[scale=0.6]{ds}
+\includegraphics[scale=0.6]{Figures/ds}
 \caption{The Design Science Research Process (\cite{vaishnavi2004design})}
@@
 \centering
-\includegraphics[scale=0.75]{gantt}
+\includegraphics[scale=0.75]{Figures/gantt}
 \caption{Provisional Project Plan}
@@
 This artefact will be developed as a group effort with each member focusing on specific areas of development and all members having some contribution to other areas.
-
+\newpage
 \subsection{Limitations}
@@
 \\\\
-The artefact’s development and the research aspect of this project is also at risk of unforeseen events.
+The artefact's development and the research aspect of this project is also at risk of unforeseen events.
 In an attempt to mitigate the harm that may be caused by these events, the artefact is being developed in such a manner to facilitate both contact sessions as well as fully digitally.
+
+\begin{figure}[H]
+\centering
+\includegraphics[scale=1.75]{Figures/swot}
+\caption{Swot Analysis of the Project}
+\end{figure}
 
@@
 
+\newpage
 \section{Provisional Chapter Division}

### 2021-11-02 Final Doc/Chapters/Chapter2.tex
Added Chapter 2 to Final Docs

@@
 \section{Introduction}
+This research study aims to develop a framework of qualities or principles needed for a digital game to be used effectively within an educational environment as well as whenever a game attempts to impart information in general.
+As such, this research study applies to any educational game and “serious games”.
+This chapter will focus on available literature on several fields in an attempt to both explain the necessary background information and also perform a pseudo-meta-analysis on the available literature by presenting and then discussing what has already been done and what could still be done in each respective field, if applicable.
+These fields will include pedagogy, ludology and gamification as these are closely linked to the research question of this study.
+Pedagogy to discuss approaches to teaching, ludology to discuss the development and implementations of games and gamification to attempt to link the two.
 
 \section{An Issue with Instructional Education}
+Education, as it stands, is still built on a paradigm that is no longer needed in modern society.
+One major flaw with the current system is that it stifles the creativity and drive of some students as each level of education is largely the same and is, as such, monotonous (\cite{Ackoff2008}).
+Therefore, education requires some form of system to create an interest in learning for the students.
+\\\\
+Ackoff and Greenberg (2008) explain that the current traditional means of teaching are no longer as relevant as they once were as it is aimed to produce members of society that were likely to not question any fundamental aspects of how things operated.
+It is largely a system that focuses on teaching while disregarding learning as the last major stride in development in education was to industrialise it – having them operate efficiently like factories (\cite{Ackoff2008}).
+It is a system that is designed to keep moving often employing a “No Child Left Behind” policy which results in almost no time for anything other than the standardised and constantly measured curriculum (\cite{gibson2006games}).
+
+\begin{table}[H]
+\centering
+\caption{Organisational Needs Between the Industrial and Information Ages - Adapted from \cite{Reigeluth1996}}
+\begin{tabular}{@{}l|l@{}}
+\toprule
+\textbf{Industrial Age} & \textbf{Information Age} \\ \midrule
+Standardisation         & Customisation            \\
+Adversarial relations   & Cooperative relations    \\
+Compliance              & Initiative               \\
+Conformity              & Diversity                \\
+CEO as “king”           & Customer as “King”       \\ \bottomrule
+\end{tabular}
+\label{tab1}
+\end{table}
+
+This current paradigm of education is operated on the basis of standardisation to accommodate the change in societal needs and requirements that the industrial age brought with it (\cite{Reigeluth1996}).
+Reigeluth (1996) states that this system was developed on the fundamental need of sorting students into different categories and to allow for comparisons so that the training of the workforce could also be separated into different groups, those being labourers, having “hands-on” skills, and managers, who mainly had a managerial skill set.
+\\\\
+However, with the shift into the “information age”, the requirements of the workforce have also changed.
+The industrial age being a time of mass-production with the emergence of various new processing technologies and the information age being characterised by the fact that information is being transmitted and generated at an ever-increasing rate due to further technological developments (\cite{gibson2006games, Reigeluth1996}).
+The most notable changes from the aforementioned paradigm shifts are that from conformity and compliance to initiative and diversity where greater value is placed on each individual’s strength and contribution to a project or organisation rather than each individual having the same skill set (\cite{Reigeluth1996}).
+A few other differences between the needs of organisations during the industrial age and the new requirements brought with the information age are depicted in the above table.
+\\\\
+Reigeluth (1996) continues and states that the current paradigm is not focused on learning but rather categorisation.
+Ackoff (1991) hold a similar viewpoint stating that there is more of a focus on teaching rather than learning.
+It should be noted that teaching and learning are very distinct from one another as both can take place without the other (\cite{Ackoff1991}).
+Learning is defined as increasing one’s ability to perform an act effectively while trying to meet an objective through acquiring new knowledge whereas teaching is the process of providing this knowledge (\cite{Ackoff1991}).
+Through this, it is clear that institutions under this paradigm aim to give learners a verbose vocabulary to speak on topics that they do not fully comprehend (\cite{Ackoff1991}).
+\\\\
+Due to this aforementioned paradigm shift and in what requirements are desired by most organisations in the information age, a shift in instructional theory is also needed – one such as going from making use of passive learning through traditional teaching means to one that is centred on active learning (\cite{Reigeluth1996}).
+These changes are discussed in more detail in the following section on pedagogy and learning theories and the means to accomplish them in the further sections on ludology and gamification.
 
 \section{Pedagogy and Learning Theories}
+As one of the outcomes of this research study is a framework that details qualities and principles for a digital game to effectively present knowledge and information to a user, one of the first areas to look towards and discuss is pedagogy which entails a general discussion about several learning and instructional theories as well as how motivation plays a role in learning.
+Pedagogy is the study of the transferal of knowledge in an educational environment through several lenses such as social, political and cultural (\cite{Li2012}).
+As such it encompasses the fields and discussions of instructional design and theory as well as any learning theories.
+
 \subsection{Learner's at the Core of Learning}
+Some instructional theories focus on students learning with minimal interaction with a teacher or instructor.
+Reigeluth (1996) refers to the learning methods that follow his ideology as ones where an instructor acts as an indirect guide to a class of learners instead of the typical “sage on the stage” structure of a lecture or presentation.
+\\\\
+Two of these aforementioned theories are learning by doing and learning by teaching methods.
+Learning by doing functions on the principle that skills can be improved through practice and self-perfection on a particular topic or knowledge base (\cite{Fisch2009}).
+This means of instruction has become increasingly popular amongst companies where they are able to make use of “on the job” training as it allows for a person to be productive immediately as well as become more proficient at tasks gradually (\cite{Fisch2009}).
+The learning by teaching method works under the assumption that learners are able to increase their understanding of a certain topic by teaching it to other learners (\cite{Fisch2009}).
+This method of learning has garnered more usage recently as it is a viable means of learning in environments with too few teachers or instructors and increases the overall learning process (\cite{Fisch2009}).
+As shown in the following table, learning methods that place the learner in control are very flexible and as such can be incorporated when attempting to teach various and different fields or subjects (\cite{Ackoff1991}).
+
+\begin{table}[H]
+\caption{List of Several Learning Methods and Their Strengths - Adapted from (Moleda, 1995, as cited in \cite{Reigeluth1996})}
+\begin{tabular}{@{}l|l@{}}
+\toprule
+Learning Method                          & Strengths                                                            \\ \midrule
+Lectures or Presentations                & Efficient, Standardised and   Structured                             \\
+Learners in Control                      & Very Flexible                                                        \\
+Games and Simulations with a Rule System & \multirow{2}{*}{Increased Learner motivation and Knowledge Transfer} \\
+Discovery as Individuals and Groups      &                                                                      \\ \bottomrule
+\end{tabular}
+\end{table}
+
+As shown in the above table, using games and simulations as a means of learning is nothing new and it has been found that they have been used as instructional tools as far back as 3000 B.C in China (\cite{Dempsey1996}).
+Games are also a viable means of learning in a new paradigm of instructional design as it has been found to increase motivation amongst learners when used (\cite{Reigeluth1996}).
+The distinction between a game and a simulation is discussed in one of the following sections.
+However, the increased motivation this means of instruction brings is important and should be noted as providing learners, in all levels of education, with content through methods of delivery that they enjoy will, as previously stated, cause them to be more motivated to learn and thus look further into that specific topic themselves which circles back to the increased transfer of knowledge through discovery as an individual (\cite{Ackoff2008, Reigeluth1996}).
+
 \subsection{Merrill's First Principles of Instruction}
+Gibson et al.
+(2006) list and summarise several learning and instructional design theories that have the potential to be applied to a game used for learning.
+This study will, however, only look at 	Merrill’s First Principles of Instruction as it is the most recent of the ones depicted (\cite{gibson2006games}).
+\\\\
+Before discussing the principles that the name refers to in this theory, Merrill (2002) provides a few definitions for terms made use of.
+A principle in this context is a relationship that is always true regardless of the environment it is applied within (\cite{Merrill2002}).
+A practice is any instructional activity (\cite{Merrill2002}).
+A program is a means of instruction that makes use of several practices (\cite{Merrill2002}).
+Merrill (2002) states that the first principles described are able to be implemented in any instructional system or environment as they are “design-oriented” and as such relate more to creating learning environments rather than describing the means of knowledge transfer.
+Each of the following principles is also accompanied by three “corollaries” each of which Merrill (2002) likewise explains.
+\\\\
+The first principle of Merrill’s (2002) First Principles of Instruction is that the learning is problem centred.
+This principle describes three corollaries, the first of which being “Show Task” which states that learners should be shown the types of problems they will be solving or will be able to solve with the knowledge that they attain (\cite{Merrill2002}).
+The next is the “Task Level” which explains that the problems presented should keep learners engaged due to the complexity and not just the action of solving it (\cite{Merrill2002}).
+The last corollary, “problem progression” describes that the problems presented should have some form of increasing complexity while still being comparable to the previous iteration of the type of problem (\cite{Merrill2002}).
+\\\\
+The second principle is Activation which means that learning happens whenever previous experiences are used (\cite{Merrill2002}).
+The first corollary, “Previous Experience”, states that the learning process is enhanced when a learner is able to draw upon relevant past experiences and apply the associate knowledge as a foundation for new knowledge (\cite{Merrill2002}).
+“New Knowledge” is the second and explains that learners should be provided with a relevant experience as an additional foundation to add to their knowledge base (\cite{Merrill2002}).
+The last corollary is “Structure” and details that learners should be encouraged to organise new knowledge according to some relevant structure (\cite{Merrill2002}).
+\newpage
+The third principle, Demonstration, proposes that learning takes place when the activities that are undertaken impart the knowledge instead of stating the information (\cite{Merrill2002}).
+“Demonstration consistency” explains that any examples or visualisation should be kept in line with the original learning goals (\cite{Merrill2002}).
+The next is “Learner Guidance” and states that learners should be shown where the relevant information for problems can be found be it in the form of comparative examples or various representation of one source (\cite{Merrill2002}).
+“Relevant Media” explains that when media is used as a means of demonstration, different types can be used provided that they do not fight for a learner’s attention (\cite{Merrill2002}).
+\\\\
+The fourth principle is Application which states that learning takes place when learners actively solve problems with the new knowledge they have acquired (\cite{Merrill2002}).
+“Practice Consistency” is similar to Demonstration consistency but with a focus on the application of knowledge (\cite{Merrill2002}).
+“Diminishing Coaching” is where the learners are provided with relevant feedback, but it is slowly lessened over time (\cite{Merrill2002}).
+It is also important that the problems provided to learners for practice have a good variety, as explained as “Varied Problems” (\cite{Merrill2002}).
+\\\\
+The fifth, and final, principle is Integration which is when the knowledge a learner has acquired is used by them in their everyday life (\cite{Merrill2002}).
+The first corollary, “Watch Me”, explains that learners are provided to showcase the new knowledge or skill they have acquired (\cite{Merrill2002}).
+“Reflection” deals with giving learners time to be able to debate with others on the topic involved (\cite{Merrill2002}).
+Lastly, “Creation” states that learners should be able to make use of their new knowledge or skill in some personal capacity (\cite{Merrill2002}).
+
+\begin{figure}[H]
+\centering
+\centerline{\includegraphics[scale=0.5]{Figures/merrill2.png}}
+\caption{Own Image summarising Merrill's First Principles}
+\end{figure}
+
+The principles and corollaries provided by Merrill (2002) provide an expansive and detailed structure to be used when developing any learning opportunity making it an exceptional choice to adapt specifically to a digital game learning system.
+It does, however, lack a comprehensive discussion on how to keep learners engaged with the content and, as such, the next subsection will discuss some theories pertaining to the role of motivation in learning.
+\newpage
 \subsection{The Influence of Motivation}
+A learner's motivation is what will drive them to engage with and enjoy the content being studied.
+This motivation can come in one of two forms according to Kapp (2012a) and to better understand the theories focussed on learner motivation, this distinction will be discussed first.
+\\\\
+The first is intrinsic motivation which is any motivation aimed to accomplish something and has originated from a desire to do something for oneself (\cite{Kapp2012a}).
+Thus, the motivation comes from the learner.
+On the other hand, with extrinsic motivation, the drive and desire to accomplish a task of some kind stems from wanting some form of reward or avoiding punishment of some kind (\cite{Kapp2012a}).
+Thus, motivation is created in return for something, either tangible or otherwise.
+\\\\
+One model for motivating learners is the ARCS Model which was developed by John Keller (1987) which is frequently referenced in the aforementioned field of instructional design (\cite{Kapp2012a}).
+It is comprised of four main elements with each focusing on designing instruction in a different way ((\cite{Kapp2012a, keller1987development})).
+\\\\
+The first of these is Attention and it is an element that is concerned with gaining and then keeping the learners’ interest.
+There are three main methods to accomplish this with the first being gaining attention through the use of relatable examples or surprise.
+The next is to create curiosity within the learners through means such as role-playing or hands-on examples.
+The last means to keep attention is the variability which means periodically changing the method of delivery (\cite{Kapp2012a, keller1987development}).
+\\\\
+Relevance refers to having the content be relevant to the learner and Kapp (Kapp2012a) mentions that this can be done through orienting the environment around achieving goals, creating a link between the motives of learners and that of the instruction means, displaying that the content is in somewhat familiar to the learners and finally developing a model of the results of learning the presented knowledge (\cite{keller1987development}).
+\\\\
+Another element of this model, Confidence, is the expectations of success set by the learner and as such when they meet these expectations they are confident in their ability to do the work (\cite{Kapp2012a, keller1987development}).
+This can be aided by providing learners with clear expectations and requirements upfront about the skill or knowledge.
+It is also helpful to provide smaller opportunities to succeed as with each success the learners will become more confident (\cite{Kapp2012a, keller1987development}).
+\\\\
+The last element in the ARCS model is Satisfaction and is concerned with giving learners a sense of accomplishment and that the effort in the learning process has some value and weight to it (\cite{Kapp2012a, keller1987development}).
+This can be accomplished by allowing learners to see how their new-found knowledge can be used, either through the use of a real-world demonstration or via some form of simulation (\cite{Kapp2012a, keller1987development}).
+\\\\
+This section has detailed three aspects found within pedagogy, instructional design and learning theories each providing some insight into effectively transferring and imparting knowledge to a learner.
+Placing the learner at the centre of both teaching and learning allows for great flexibility in how to present that given material while Merrill (2002) provides an expansive framework to structure this presentation of knowledge whereas Kapp (2012a), through citing John Keller, explains ways to keep learners motivated throughout the learning process.
 
+\newpage
 \section{An Approach Through Ludology}
+Another approach that could be taken is one that is rooted in games as these are popular among those in schools and as such should provide a means to deliver content in an interesting and engaging manner (\cite{Virvou2005}).
+\\\\
+To be able to implement a digital game as a means of learning, an understanding of games, in general, is needed.
+This section details ludology in general and the various applications and topics it encompasses ha relate in some manner to the research problem discussed.
+These topics will include a discussion on games as a means of simulation and what is referred to as a “serious game” within the field.
+
 \subsection{What is Ludology}
+Ludology is the formal and academic study of games and has roots in studying games through a cultural and social lens by discussing how each interacts with the so-called “spirit of play” (\cite{Huizinga1949}).
+However, relatively recently, as early as 2001, the field has shifted and now encompasses the study of digital computer-based games as this is when the first academic peer reived journal on the topic was published as well as several international conferences taking place (\cite{Frasca2013}).
+\\\\
+As such, this study will use the definition provided by Gonzalo Frasca, “Ludology can be defined as a discipline that studies games in general, and video games in particular” (\cite{Frasca2013}).
+Frasca (2013) further elaborates on his statement that the field of ludology has a focus on discussing and understanding the individual elements of games as well as creating models to explain the various mechanics and rules of games.
+\\\\
+In its infancy, the field of ludology was heavily compared to narratology, the study of narratives as they were seen as nothing more than a new medium to demonstrate and display story-telling (Murray, 1997, as cited in \cite{Frasca2002}).
+Due to this digital and video games were studied under the same framework that would regularly be applied to drama, films and narratives as they unarguably had narrative elements in them to varying degrees (\cite{Manovich2002}).
+Frasca (2002) cites Espen Aarseth stating that studying digital games under a narratology framework was a misguided attempt at understanding them and digital games would require their framework to be studied under.
+Eskelinen (2001) echoes this mentioning that when games were studied, the discussions were centred within literary and film studies as games were depicted as interactive narratives.
+This definition of games has little substance to it and comes from a limited knowledge of, often outdated, literary theory (\cite{Eskelinen2001}).
+
 \subsection{Serious Games}
+Annetta (2008) states that the movement to include video games in teaching and training began in 2003, two years after the field of ludology began to gain traction itself concerning digital and computer-based games.
+The types of games used in this context are often referred to as “serious games”.
+\\\\
+“Serious games” were introduced as digital concepts in 2002 through the Serious Game Initiative which was spearheaded by David Rejeski and Ben Sawyer (\cite{DeGloria2014}).
+The initial intention for serious games was for them to be used as a means of training certain tasks and skills (\cite{DeGloria2014}) – this was typically done through simulation type games which will be discussed in the following subsection in greater detail.
+\\\\
+Virvou, Katsionis and Manos (2005) mention that the endeavour to create serious games has yet to reach schools due to certain criticisms about games in general that hinders this.
+This is due to the fact that discussions around games by educators have largely focused on the social consequences of playing games instead of the educational potential games hold (\cite{Squire2003}).
+Due to this the study of serious games became more theoretical and discussion-based at lower levels and more applied with actual use at higher levels.
+This can be seen by implementations implemented in several fields including medical rehabilitation, ecological studies, learning languages and business studies (\cite{Burke2009, Costanza2014, Ranalli2008, Tao2009}).
+\newpage
+These types of games have already had an impact on the military, medical and higher business education fields early in their conception and this trend continues to this day with most serious games being used within the medical fields specifically (\cite{Annetta2008, DeGloria2014}).
+However, there were attempts to use serious games, as simulations, within physics and engineering (\cite{Deshpande2011}).
+
 \subsection{Games as Simulation}
+Games have also found use as a means to simulate models, environments and a myriad of other systems.
+As mentioned in the previous subsection, there are a few games used for medical training (\cite{Burke2009}) and to be effective at teaching and demonstrating these topics, digital games need to be used as a simulation.
+\\\\
+Squire (2003) provides a definition for games as a simulation and states that these simulations attempt to model reality in a consistent manner usually through modelling physical or social systems through another system – which in this case would be a computer and the digital video game.
+There are two main types of simulations, Hi-fidelity and low fidelity.
+Hi-fidelity simulations attempt to model every possible interaction in a given system, phenomena or environment as accurately as possible (\cite{Squire2003}).
+In contrast, a low fidelity simulation will make use of a fair bit of abstraction as it aims to only demonstrate a few key characteristics of the phenomena or environment (\cite{Squire2003}).
+Games as simulations would comprise of both of these types depending on the content that it attempts to simulate,
+\\\\
+Deshpande and Huang (2011) describe the use of games as a means of simulation for specific sections of work in physics and engineering courses as an addition to traditional teaching as it provides a relatively simple way to demonstrate certain phenomena.
+As such these authors discuss the simulation aspect of games rather than the narrative as when dealing with a simulation digital game it typical lacks most narrative elements in the traditional sense (\cite{Deshpande2011}).
+\\\\
+This section detailed the field of ludology and its roots in the “spirit of play” amongst cultures and society as well as the shift into being an academic means to study digital computer games.
+Through this, it was able to describe and develop the idea of a “serious game” and consequently games as simulations which are the most effective means to convey a learning environment through video games as a whole.
+Following this section, this study discusses how to link the learning theories of the previous section and the study of games together through a specific discussion on gamification.
 
 \section{Gamification}
+This section will discuss the process of gamification and the theoretical knowledge behind it.
+This field is crucial to what this research study wishes to accomplish as it is the link to transform traditional teaching and learning into a game-based structure.
+Furthermore, this section will focus on the aspects of gamification that can be applied and translated into a digital game.
+\\\\
+Gamification can be defined as making use of game-like mechanics, aesthetics and thinking to create motivation, solve problems and produce a more suitable learning environment (\cite{Kapp2012a}).
+Kapp (2012b) states that while gamification makes use of game elements, it only makes use of a few of them as in a gamified system, in a gamification context, learners are not constantly engaged in playing the game as there are sections of respite from this, such as video explanations.
+While elements such as points and achievements are found in most games, gamification strives to add more than just these to a classroom as with the absence of other elements and only points and badges, the resulting system is one that is dull (\cite{KappArticle2012}).
+Kapp (2012b) continues stating that gamification adds much more to create an interesting system such as narrative aspects and continuous feedback to learners to create and upkeep their motivation and engagement with the system.
+\newpage
+Gamification is often not implemented within a classroom but is rather presented to learners through some external means – such as a digital game (\cite{KappArticle2012}).
+It should be noted, however, that a serious game can be the result of the gamification of some content but gamification does not always have to produce a serious game as a result (\cite{KappArticle2012}).
+Kapp (2012a) describes various types of knowledge and how to begin developing a gamified system to effectively teach each of them:
 
+\begin{itemize}
+\item Declarative Knowledge is usually comprised of facts and jargon within a topic and is best taught by making use of sorting and matching type games.
+\item Conceptual Knowledge is the grouping of related information that have an underlying common descriptor and is best taught by using demonstrations and sorting based on the common trait.
+\item Rules-Based Knowledge is strict statements linking concepts and is best taught by demonstrating what failing to comply with the rules are.
+\item Procedural Knowledge is a progression based path to reach an outcome and is best taught through the use of having learners work through the procedure in a demonstration and other means as well.
+\item Soft Skills are general strategies for dealing with various social interactions and are best taught through the use of repeated application of the skill in different scenarios.
+\item Affective Knowledge deals with topics about subjective phenomena such as emotions and is most effectively taught through immersing the learner within these phenomena.
+
+\item Psychomotor Domain deals with making use of cognitive knowledge through physical skills (hand-eye coordination is an example of this) and is most effectively taught through observation.
+\end{itemize}
+Gamification makes use of several procedures and processes that are rooted in various academic theories, most notably ones found within pedagogy and as such was discussed in the pedagogy section of this literature review (\cite{KappArticle2012}).
+\\\\
+This section on gamification has thus discussed what gamification entails and how it usually implemented.
+A focus on the types of knowledge it is able to gamify is also presented as well as one way to effectively teach that type of knowledge.
+The following section will discuss existing attempts at producing a gamified system and serious games.
+\newpage
 \section{Existing Gamified Teaching Systems and Educational Games}
+This section will detail various examples of previously implemented gamified teaching systems and educational games in an attempt to identify what approaches have already been detailed.
+Furthermore, this approach will also allow for the identification of which aspects are commonly used in educational systems and games among these implementations.
+\\\\
+Dincelli and Chengalur-Smith (2020) developed a game with the intention to train employees on certain security issues such as social engineering through social media.
+This study developed two different gamified artefacts, one that made use of graphics and one that was entirely comprised of text, with both of them following a “choose your own adventure” approach where the narrative of the game shifts depending on the users’ choices or actions (\cite{Dincelli2020}).
+
+\begin{figure}[H]
+\centering
+\centerline{\includegraphics[scale=0.5]{seta.png}}
+\caption{Example Frame from the SETA gamified training system – Reused from (\cite{Dincelli2020})}
+\end{figure}
+
+Dincelli and Chengalur-Smith (2020) discuss their approach to developing this artefact and make a few key decisions.
+The first is to apply some form of narrative, or story-based elements to the game, which allows for an agent to guide a user through the learning process presented (\cite{Dincelli2020, Sheng2007}).
+Another principle they made use of is reflection, which, when implemented, should provide time to users to think about the information and reflect on it (\cite{Dincelli2020, Sheng2007}).
+This study also goes on to mention further articles used in the construction of the artefact hen identifying what qualities they should make use of (\cite{Dincelli2020, Liu2017}).
+The conclusion this study came to was that a gamified system of any kind is more effective than traditional means and a game with graphics is easier for users to comprehend (\cite{Dincelli2020}).
+\\\\
+Annetta (2008) discusses multiple examples of educational games aimed towards younger audiences, such as Discover Babylon.
+This game was developed by the University of California in conjunction with several other institutes.
+It was a multiplayer game that made use of hi-fidelity simulation, as defined above, to accurately simulate mysteries around Babylon that are solved by garnering an understanding of the Mesopotamian society of the city (\cite{Annetta2008}).
+It was designed for children just entering their teen years and made use of 3D photorealistic renderings of the city, shown in the figure below, as well as a question and answer management system (\cite{Annetta2008}).
+
+\begin{figure}[H]
+\centering
+\begin{subfigure}{.5\textwidth}
+  \centering
+  \includegraphics[width=0.84\linewidth]{Figures/baby.png}
+  \caption{A Screenshot from Discover Babylon}
+\end{subfigure}%
+\begin{subfigure}{.5\textwidth}
+  \centering
+  \includegraphics[width=0.84\linewidth]{Figures/wolf.png}
+  \caption{A Wolf Den Minigame - Reused from (\cite{Annetta2008})}
+\end{subfigure}
+\caption{Examples of Serious Games used for Educational Purposes}
+\end{figure}
+
+The Wolf Den is a virtual learning environment developed at North Carolina State University as a means to facilitate online and distance learning (\cite{Annetta2008}).
+The system facilitated real-time communication between participants and allowed for students and teachers to engage in the development of role-playing games as well as a means to teach online courses (\cite{Annetta2008}).
+This system also allowed for various “minigames”, one such example being a digital laboratory designed to test water samples and interact with chemicals usually found within a chemistry lab – thus making use of hi-fidelity simulation as well (\cite{Annetta2008}).
+The water testing lab example is pictured above;
+\\\\
+A brief look at three serious game examples has shown that for an educational institution learning game, hi-fidelity simulation is more often used as the topics discussed require a full array of interactions while serious games meant for employee training that does not directly teach skills pertinent to their job, low fidelity simulation with some form of narrative is a solid approach.
 
 \section{Potential Effects of Game-Based Learning}
+Lastly, this section will document various and effects of using game-based learning in an attempt to ensure the framework of qualities and principles developed can avoid introducing them into the system that will be developed.
+Specifically, this section will focus on several studies that discuss the effect of games or elements of games.
+\\\\
+With the implementation of games as a means of learning, positive effects are wanted over others.
+A study had developed a digital game to illustrate the executive function of being able to switch attention from one task to another effectively and quickly and found that participants that had several hours of playtime performed better on cognitive tests that tested the aforementioned skill (\cite{Mayer2019}).
+This study also found that the increase in cognitive skills had not happened in some games but had in others, although they do not mention which games these are (\cite{Mayer2019}).
+\\\\
+A study by Kristiadi et al.
+(2019) found that games that have an element of adventure to them tend to cause and develop positive behaviour in those who played them.
+This is, however, dependent on several other requirements as well such as representation based on knowledge morality, ethics and cooperation (\cite{Kristiadi2019}).
+\\\\
+Mertala and Meriläinen (2019) conducted a study into what type of games children were most interested in and talked about in a meaningful way.
+The study found a few key influential games that most children mentioned, the most notable being Minecraft and Super Mario (\cite{Mertala2019}).
+The study goes on to discuss the “ideal game” that each child designed through a drawing and it is clear that, as with the aforementioned influential games, they are all vibrantly colourful (\cite{Mertala2019}).
+\\\\
+Wouters et al.
+(2013) conducted a meta-analysis into the motivational effects of serious games and as such discuss various motivation based theories.
+It was found that serious games are a more effective means of instruction than other contemporary methods (\cite{Wouters2013}).
+Wouters et al.
+(2013) also found that the motivation of the participants making use of the game was not statistically more significant than those using traditional methods.
+One reason for this may be found in an explanation of the self-determination theory of motivation, which links to intrinsic motivation defined above in this literature review (\cite{Wouters2013}).
+\\\\
+Gomez et al.
+(2019) conducted a study into what effects prolonged exposure to playing a popular game franchise, Pokémon, as a child would have later in life as an adult.
+The study made use of several images and took images of the brain’s activity in participants while showing them these different images, examples of these pictures are shown below in the figure (\cite{Gomez2019}).
+The study found that people who did play Pokémon extensively as children, had different activity in their visual cortex when looking at the image of a Pokémon as compared to the other images in addition to the other participants, those who had no interaction with Pokémon growing up, had almost no activity when looking at images of Pokémon (\cite{Gomez2019}).
+Gomez et al.
+(2019) suggest that during the period of early development that participants were exposed to Pokémon is also when the brain is most responsive to visual stimuli.
+
+\begin{figure}[H]
+\centering
+\centerline{\includegraphics[scale=0.5]{Figures/poke.png}}
+\caption{Example Images Used in The Study – Reused form (\cite{Gomez2019})}
+\end{figure}
 
 \section{Conclusion and Summary}
+This chapter has discussed various fields of knowledge required to develop a framework of qualities needed by a serious or educational game to effectively teach a learner the content it deals with.
+The fields of pedagogy, ludology and gamification were discussed in addition to several case studies to further understand what is required.
+\\\\
+When focusing on each of these fields with a lens focusing on developing this study’s framework, it is apparent that there is overlap between all three fields even without making use of gamification as a link between ludology and pedagogy.
+Gamification makes heavy reference to theories stated within the field of pedagogy as well as, as per its’ definition, borrows elements from ludology (\cite{KappArticle2012}).
+The most notable overlap between all three fields is that all make reference to narratology in some shape or form – pedagogy referring to including relatable examples, ludology being compared to narratology as a whole and gamification mentioning that involving stories is needed to teach certain knowledge types (\cite{Dincelli2020, Frasca2013, Kapp2012a, Sheng2007}).
+This was also shown in one of the case studies where story elements were used in a gamified training system (\cite{Dincelli2020, Sheng2007}).
+\\\\
+Both gamification and pedagogy have means within their respective fields to gauge the effectiveness of teaching and learning through the use of some framework or principles (\cite{Kapp2012a, Merrill2002, Reigeluth1996}) while ludology only provides a framework to develop the games through the lens of game rules and mechanics (\cite{DeGloria2014}) and as such gamification provides a good base for developing a framework, much like Merrill’s in pedagogy, based within the field of ludology.

### 2021-11-03 Final Doc/Chapters/Chapter1.tex
Formatting

@@
 As such, a student will have their own individual preferences and style of learning.
-Due to the rapid and prevalent development of technology, using video games as a means of teaching has been a topic of discussion.
+Due to the rapid and prevalent development and accessibility of technology, using digital computer games as a means of teaching has been a topic of discussion.
+In light of this, an academic study will be undertaken as an individual research project to determine how computer games can be used in education.
+This includes determining what qualities are needed for a digital computer game to be effective as a means of teaching and learning.
 \\\\
-This project aims to create an artefact in the form of a digital game and incorporate specific qualities into one level to demonstrate how a game may be used in a learning environment through the example of an “advanced game tutorial” that aims to not only act as the usual tutorial phase of the game but also to infer certain information about the game’s assorted enemy types.
-
+Additionally, this project aims to create an artefact in the form of a digital computer game as a group practical effort.
+This artefact will be developed alongside the individual research projects of the group members.
+It should be noted that this artefact is developed as a standalone project with no links to the research projects of the group members but may be influenced by each members individual research projects as the research may help develop certain aspects of the artefact.
+\pagebreak
 \section{Project Contents}
@@
 They continue to state that, on average, these students spend almost double the time playing video games as they do reading (\cite{Deshpande2011}).
-\newpage
 Virvou, Katsionis and Manos (2005) echo the point that computer games are popular among individuals who are in schools and as such could provide a means to deliver content in an interesting and engaging manner.
@@
 
-According to Annetta (2008), the movement for the inclusion of digital games to be used in teaching and training environments first started in 2003, two years after the field of ludology, the study of games, began to gain traction in academic literature.
+\noindent According to Annetta (2008), the movement for the inclusion of digital games to be used in teaching and training environments first started in 2003, two years after the field of ludology, the study of games, began to gain traction in academic literature.
 This initiative is what started the concept of a serious game as one that can be used in an academic sense to relay information.
@@
 As such these authors discuss the simulation aspect of games rather than the narrative.
-\\\\\\
+\\\\
 The endeavour to create serious games has yet to reach schools due to certain criticisms about games in general which hinder the adoption of games as a means of teaching and learning (\cite{Virvou2005}).
@@
 
-The next aim of this project is to develop an artefact which will require the following objectives:
+\noindent The next aim of this project is to develop an artefact which will require the following objectives:
 \begin{enumerate}
@@
 Another is that knowledge and its’ understanding is developed through the findings of the study itself.
-\\\\
+\pagebreak
 Design science is a methodology composed of using analytical techniques and can be used according to many paradigms to perform research in the information systems field (\cite{vaishnavi2004design}).
@@
 The development of the artefact will be done as a group effort and as such the computer game that will be developed for this project may be impacted by the findings of these other projects.
-
+\pagebreak
 \section{Approach to Project Management and Project Plan}
@@
 This artefact will be developed as a group effort with each member focusing on specific areas of development and all members having some contribution to other areas.
-\newpage
+
 \subsection{Limitations}
@@
 \end{itemize}
-
+\pagebreak
 \subsection{Risks and SWOT Analysis}
@@
 \centering
-\includegraphics[scale=1.75]{Figures/swot}
+\includegraphics[scale=1.5]{Figures/swot}
 \caption{Swot Analysis of the Project}
@@
 
-\newpage
 \section{Provisional Chapter Division}
@@
 As this project pertains to the application of knowledge towards an artefact, this section will mostly discuss the underlying principles and qualities that make for a game to be used in a learning capacity.
-\\\\
+\pagebreak
 \textbf{Chapter 5: Discussion on Results} \\
@@
 \\\\
-\textbf{Reference List}
+\textbf{Reference List} \\
 Contains all literary works referenced in the project.

### 2021-11-03 Final Doc/Chapters/Chapter2.tex
Formatting

@@
 It is largely a system that focuses on teaching while disregarding learning as the last major stride in development in education was to industrialise it – having them operate efficiently like factories (\cite{Ackoff2008}).
-It is a system that is designed to keep moving often employing a “No Child Left Behind” policy which results in almost no time for anything other than the standardised and constantly measured curriculum (\cite{gibson2006games}).
+It is a system that is designed to keep moving often employing a “No Child Left Behind” policy which results in almost no time for anything other than the standardised and constantly measured curriculum \citep{gibson2006games}.
 
@@
 A few other differences between the needs of organisations during the industrial age and the new requirements brought with the information age are depicted in the above table.
-\\\\
-Reigeluth (1996) continues and states that the current paradigm is not focused on learning but rather categorisation.
+\newpage
+\noindent Reigeluth (1996) continues and states that the current paradigm is not focused on learning but rather categorisation.
 Ackoff (1991) hold a similar viewpoint stating that there is more of a focus on teaching rather than learning.
@@
 Reigeluth (1996) refers to the learning methods that follow his ideology as ones where an instructor acts as an indirect guide to a class of learners instead of the typical “sage on the stage” structure of a lecture or presentation.
-\\\\
+\\\\\\
 Two of these aforementioned theories are learning by doing and learning by teaching methods.
@@
 \caption{List of Several Learning Methods and Their Strengths - Adapted from (Moleda, 1995, as cited in \cite{Reigeluth1996})}
+\begin{adjustwidth}{-1cm}{}
 \begin{tabular}{@{}l|l@{}}
@@
 \end{tabular}
+\end{adjustwidth}
 \end{table}
 
-As shown in the above table, using games and simulations as a means of learning is nothing new and it has been found that they have been used as instructional tools as far back as 3000 B.C in China (\cite{Dempsey1996}).
+\noindent As shown in the above table, using games and simulations as a means of learning is nothing new and it has been found that they have been used as instructional tools as far back as 3000 B.C in China (\cite{Dempsey1996}).
 Games are also a viable means of learning in a new paradigm of instructional design as it has been found to increase motivation amongst learners when used (\cite{Reigeluth1996}).
@@
 The last corollary is “Structure” and details that learners should be encouraged to organise new knowledge according to some relevant structure (\cite{Merrill2002}).
-\newpage
-The third principle, Demonstration, proposes that learning takes place when the activities that are undertaken impart the knowledge instead of stating the information (\cite{Merrill2002}).
+
+\noindent The third principle, Demonstration, proposes that learning takes place when the activities that are undertaken impart the knowledge instead of stating the information (\cite{Merrill2002}).
 “Demonstration consistency” explains that any examples or visualisation should be kept in line with the original learning goals (\cite{Merrill2002}).
@@
 Lastly, “Creation” states that learners should be able to make use of their new knowledge or skill in some personal capacity (\cite{Merrill2002}).
+\\\\
+The principles and corollaries provided by Merrill (2002) provide an expansive and detailed structure to be used when developing any learning opportunity making it an exceptional choice to adapt specifically to a digital game learning system.
+It does, however, lack a comprehensive discussion on how to keep learners engaged with the content and, as such, the next subsection will discuss some theories pertaining to the role of motivation in learning.
 
@@
 \centering
-\centerline{\includegraphics[scale=0.5]{Figures/merrill2.png}}
+\centerline{\includegraphics[scale=0.6]{Figures/merrill2.png}}
 \caption{Own Image summarising Merrill's First Principles}
@@
 
-The principles and corollaries provided by Merrill (2002) provide an expansive and detailed structure to be used when developing any learning opportunity making it an exceptional choice to adapt specifically to a digital game learning system.
-It does, however, lack a comprehensive discussion on how to keep learners engaged with the content and, as such, the next subsection will discuss some theories pertaining to the role of motivation in learning.
-\newpage
 \subsection{The Influence of Motivation}
@@
 One model for motivating learners is the ARCS Model which was developed by John Keller (1987) which is frequently referenced in the aforementioned field of instructional design (\cite{Kapp2012a}).
-It is comprised of four main elements with each focusing on designing instruction in a different way ((\cite{Kapp2012a, keller1987development})).
-\\\\
+It is comprised of four main elements with each focusing on designing instruction in a different way (\cite{Kapp2012a, keller1987development}).
+\\
 The first of these is Attention and it is an element that is concerned with gaining and then keeping the learners’ interest.
@@
 
-\newpage
 \section{An Approach Through Ludology}
@@
 Frasca (2002) cites Espen Aarseth stating that studying digital games under a narratology framework was a misguided attempt at understanding them and digital games would require their framework to be studied under.
+\\\\
 Eskelinen (2001) echoes this mentioning that when games were studied, the discussions were centred within literary and film studies as games were depicted as interactive narratives.
@@
 This can be seen by implementations implemented in several fields including medical rehabilitation, ecological studies, learning languages and business studies (\cite{Burke2009, Costanza2014, Ranalli2008, Tao2009}).
-\newpage
+\\\\
 These types of games have already had an impact on the military, medical and higher business education fields early in their conception and this trend continues to this day with most serious games being used within the medical fields specifically (\cite{Annetta2008, DeGloria2014}).
@@
 Kapp (2012b) continues stating that gamification adds much more to create an interesting system such as narrative aspects and continuous feedback to learners to create and upkeep their motivation and engagement with the system.
-\newpage
+
 Gamification is often not implemented within a classroom but is rather presented to learners through some external means – such as a digital game (\cite{KappArticle2012}).
@@
 The following section will discuss existing attempts at producing a gamified system and serious games.
-\newpage
+
 \section{Existing Gamified Teaching Systems and Educational Games}
@@
 Furthermore, this approach will also allow for the identification of which aspects are commonly used in educational systems and games among these implementations.
-\\\\
-Dincelli and Chengalur-Smith (2020) developed a game with the intention to train employees on certain security issues such as social engineering through social media.
+\newpage
+\noindent Dincelli and Chengalur-Smith (2020) developed a game with the intention to train employees on certain security issues such as social engineering through social media.
 This study developed two different gamified artefacts, one that made use of graphics and one that was entirely comprised of text, with both of them following a “choose your own adventure” approach where the narrative of the game shifts depending on the users’ choices or actions (\cite{Dincelli2020}).
@@
 \centering
-\centerline{\includegraphics[scale=0.5]{seta.png}}
+\centerline{\includegraphics[scale=0.45]{seta.png}}
 \caption{Example Frame from the SETA gamified training system – Reused from (\cite{Dincelli2020})}
@@
 
-Dincelli and Chengalur-Smith (2020) discuss their approach to developing this artefact and make a few key decisions.
+\noindent Dincelli and Chengalur-Smith (2020) discuss their approach to developing this artefact and make a few key decisions.
 The first is to apply some form of narrative, or story-based elements to the game, which allows for an agent to guide a user through the learning process presented (\cite{Dincelli2020, Sheng2007}).
@@
 The fields of pedagogy, ludology and gamification were discussed in addition to several case studies to further understand what is required.
-\\\\
+\\\\\\
 When focusing on each of these fields with a lens focusing on developing this study’s framework, it is apparent that there is overlap between all three fields even without making use of gamification as a link between ludology and pedagogy.

### 2021-11-03 Final Doc/main.tex
Added Chapter 2 to Final Docs
Formatting

@@
 \documentclass[
-11pt, % The default document font size, options: 10pt, 11pt, 12pt
+12pt, % The default document font size, options: 10pt, 11pt, 12pt
 oneside, % Two side (alternating margins) for binding by default, uncomment to switch to one side
 english, % ngerman for German
-singlespacing, % Single line spacing, alternatives: onehalfspacing or doublespacing
+onehalfspacing, % Single line spacing, alternatives: onehalfspacing or doublespacing
 %draft, % Uncomment to enable draft mode (no pictures, no links, overfull hboxes indicated)
@@
 ]{MastersDoctoralThesis} % The class file specifying the document structure
+
 \usepackage{graphicx}
@@
 \usepackage[T1]{fontenc} % Output font encoding for international characters
+\usepackage{booktabs}
+\usepackage{multirow}
 \usepackage[final]{pdfpages}
 \usepackage{mathpazo} % Use the Palatino font by default
-
+\usepackage{changepage}
+\usepackage{caption}
+\usepackage[list=false]{subcaption}
 \usepackage[backend=biber,style=apa,natbib=true]{biblatex} % Use the bibtex backend with the authoryear citation style (which resembles APA)
@@
 	paper=a4paper, % Change to letterpaper for US letter
-	inner=1.5cm, % Inner margin
-	outer=1.5cm, % Outer margin
-	bindingoffset=0.3cm, % Binding offset
-	top=0.5cm, % Top margin
-	bottom=0.5cm, % Bottom margin
+	inner=2.5cm, % Inner margin
+	outer=2cm, % Outer margin
+	%bindingoffset=0.3cm, % Binding offset
+	top=2cm, % Top margin
+	bottom=2.5cm, % Bottom margin
 	%showframe, % Uncomment to show how the type block is set on the page
@@
 \begin{center}
-\includegraphics[scale=0.3]{nwu.png}\\[0.4cm]
+\includegraphics[scale=0.4]{Figures/nwu.png}\\[.4cm]
 
@@
 \include{Chapters/Chapter2}
+\include{Chapters/Chapter3}
 

### 2021-11-03 Final Doc/Chapters/Chapter1.tex
Final Docs Updated

@@
 \centering
-\includegraphics[scale=1.5]{Figures/swot}
+\includegraphics[scale=2]{Figures/swot}
 \caption{Swot Analysis of the Project}
@@
 \\\\
-\textbf{Chapter 1: Introduction} \\	
+\indent \textbf{Chapter 1: Introduction} \\	
 The problem that is being researched, the qualities of games needed for use in education, is discussed in Chapter 1.
@@
 Furthermore, the aim of the study in addition to the planned method of conduct will be discussed.
-\\\\
-\textbf{Chapter 2: Literature Study} \\
+\\
+\indent \textbf{Chapter 2: Literature Study} \\
 Chapter 2 will discuss the impact of games both in early development and in general in more detail, the accessibility of games as well as a focus on games being used in learning.
 It will attempt to find what qualities and principles work best to make a game a suitable means of learning.
-\\\\
-\textbf{Chapter 3: Development of Accompanying Artefact} \\
+\\
+\indent \textbf{Chapter 3: Development of Artefact and Article} \\
 The accompanying artefact that will be developed as a part of the study will be discussed along with the development process of the artefact.
-\\\\
-\textbf{Chapter 4: Review of Collected Data} \\
-The means of data collection, processing and analysis will be discussed in this chapter along with the results of this data.
-As this project pertains to the application of knowledge towards an artefact, this section will mostly discuss the underlying principles and qualities that make for a game to be used in a learning capacity.
-\pagebreak
-\textbf{Chapter 5: Discussion on Results} \\
+\\
+\indent \textbf{Chapter 4: Results} \\
 A discussion on the results obtained will be presented in this chapter.
 This chapter will focus more on the application of the acquired knowledge and principles towards the development of the artefact.
-\\\\
-\textbf{Chapter 6: Conclusion} \\
-The contents and results of the study will be briefly discussed and reiterated in an overview.
-\\\\
-\textbf{Reference List} \\
+\\
+\indent \textbf{Chapter 5: Reflection} \\
+The contents and results of the study will be briefly discussed and reiterated in an overview in addition to a brief discussion on how the project could possibly progress.
+\\
+\indent \textbf{Reference List} \\
 Contains all literary works referenced in the project.

### 2021-11-03 Final Doc/Chapters/Chapter3.tex
Added and Updated Final Doc Latex
Final Docs Updated

--- 2021-10-27 Final Doc/Chapters/Chapter1.tex
@@
-% Chapter 1
+% Chapter 3
 
-\chapter{Introduction} % Main chapter title
+\chapter{Development of Artefact and Article} % Main chapter title
 
-\label{Chapter1} % For referencing the chapter elsewhere, use \ref{Chapter1}
+\label{Chapter3} % For referencing the chapter elsewhere, use \ref{Chapter1}
 
-%----------------------------------------------------------------------------------------
+This chapter describes the artefact that was developed in a group effort as well as the process followed for the writing of the academic article.
 
-% Define some commands to keep the formatting separated from the content 
-\newcommand{\keyword}[1]{\textbf{#1}}
-\newcommand{\tabhead}[1]{\textbf{#1}}
-\newcommand{\code}[1]{\texttt{#1}}
-\newcommand{\file}[1]{\texttt{\bfseries#1}}
-\newcommand{\option}[1]{\texttt{\itshape#1}}
+\section{Description of Artefact}
+This research project was split into two main aspects: 
+\begin{enumerate}
+\item An individual research study into a chosen topic \textit{(this being the qualities needed for a computer game to be used in education)}
+\item A group effort to develop a digital computer game.
+\end{enumerate}
 
-%----------------------------------------------------------------------------------------
+\noindent For the first aspect of this project, the resulting outcome was an academic article titled, \textit{"Linking Gamification, Ludology and Pedagogy: How to Use Serious Games for Various Knowledge Domains"}.
+As stipulated in the title, the fields of gamification, ludology and pedagogy were the focus of this research aspect of the project.
+In this article, the question posed by this project is again reiterated and sequentially answered.
+The article is attached to this document under Appendix  \ref{AppendixC}.
+\\\\
+The artefact accompanying this research project is a digital computer came which was developed as part of a group effort as mentioned previously.
+While this artefact is separate from the individual research studies conducted by its' group members, it may have been influenced by the topics being researched.
+The artefact is titled \textit{"Puzzle Ball: Spherical Shadows"} and is further categorised as a 3D puzzle platformer with aspects of action gameplay played in first person.
+A playable version of the artefact is available on the website itch.io website\footnote{\url{https://josh-scg.itch.io/puzzle-ball-spherical-shadows}} and the source code of the artefact is available on GitHub\footnote{\url{https://github.com/GCWehmeyer/Spherical_Shadows}}$^{,}$\footnote{\url{https://github.com/Josh-SCG/Spherical_Shadows}}
 
-\section{Project Description}
+\section{Artefact Life Cycle Followed and its Different Phases}
+% Briefly provide general background on the life cycle that was followed and why it is appropriate to this artefact.
 
-\section{Project Contents}
-\subsection{Problem Description and Background}
-\subsection{Overview of Related Literature}
-\subsection{Research Question and Expected Outcomes}
-
-\section{Aims and Objectives of Project}
-
-\section{Procedures and Methods of Investigation}
-\subsection{Research Paradigm and Methodology Used}
-\subsection{Collection of Data}
-\subsection{Development of Artefact}
-\subsection{Integration with Other Projects}
-
-\section{Approach to Project Management and Project Plan}
-\subsection{Provisional Project Plan}
-\subsection{Scope}
-\subsection{Contributions of Each Group Member}
-
-\section{Development Platform, Resources and Environments}
-\subsection{Development Platform}
-\subsection{Resources}
-\subsection{Environments}
-
-\section{Ethical Implications of Project}
-
-\section{Provisional Chapter Division}
+\section{Description of the Development of the Artefact}
+%Comprehensive report on the way in which each phase of the life cycle was applied in the development of this artefact.

### 2021-11-03 Final Doc/Chapters/Chapter4.tex
Final Docs Updated

% Chapter 4

\chapter{Results} % Main chapter title

\label{Chapter4}

### 2021-11-03 Final Doc/Chapters/Chapter5.tex
Final Docs Updated

% Chapter 5

\chapter{Reflection} % Main chapter title

\label{Chapter5} % For referencing the chapter elsewhere, use \ref{Chapter1}

%What did you learn while completing this project?  Refer to the decisions that you took, and evaluate them.  Analyse the strong and weak points of the product and the process that you followed.  What would you do differently?

%Did you achieve the objectives that you set for the project?  Discuss.

%How successful were you in managing the project and meeting target dates?  Discuss.

%Comments on group work.  Responsibilities and contribution of each group member.  Problems with cooperation and contributions, and dealing with these problems.

%The reflection must be structured logically.

%Conclude the reflection with a summary that is a critical evaluation of the process followed with the honours project

### 2021-11-03 Final Doc/Chapters/Chapter3.tex
Final Doc Updated

@@
 
-\section{Description of Artefact}
+\section{Description of Artefact and Article}
 This research project was split into two main aspects: 
@@
 A playable version of the artefact is available on the website itch.io website\footnote{\url{https://josh-scg.itch.io/puzzle-ball-spherical-shadows}} and the source code of the artefact is available on GitHub\footnote{\url{https://github.com/GCWehmeyer/Spherical_Shadows}}$^{,}$\footnote{\url{https://github.com/Josh-SCG/Spherical_Shadows}}
+\\\\
+Before moving on the the development of the artefact, a brief look at the cycle of play will be shown. 
+\\\\
+Once the application is launched, the user is taken to the \textit{Main Menu} screen (depicted below) where clicking the text \textit{Play} triggers a function to start the first level - that being the the Tutorial.
+Each group member was responsible for the design of an individual level where the Tutorial/First level being the level undertaken in this project.
+The reason for this is that the research aspect of this project aligns with the goals of a tutorial level.
+
+\begin{figure}[H]
+\centering
+\begin{subfigure}{0.5\textwidth}
+  \centering
+  \includegraphics[width=1\linewidth]{Figures/menu.png}
+  \caption{The Main Menu of the Artefact}
+\end{subfigure}%
+\begin{subfigure}{0.5\textwidth}
+  \centering
+  \includegraphics[width=1\linewidth]{Figures/start.png}
+  \caption{The Starting Point of the Level}
+\end{subfigure}
+\caption{Starting the Game}
+\end{figure}
+
+\noindent One the tutorial level has started, the user is shown the basic character movement controls on the right side of the screen and can continue forward.
+Text based signs such as this were used throughout the level to explain various mechanics or tasks to be completed.
+
+\begin{figure}[H]
+\centering
+\centerline{\includegraphics[scale=0.33]{tutSignEg.png}}
+\caption{A Further Example of the Tutorial Signs}
+\end{figure}
+
+\noindent The user must then make there way to a central area, referred to as the Hub Room, where they are given the choice in what order they would like to complete the five main tutorials.
+These will be discussed and shown below.
+As the user completes the several tutorials, a blockade that restricted movement to the next level is slowly removed as shown below.
+
+\begin{figure}[H]
+\centering
+\begin{subfigure}{0.3\textwidth}
+  \centering
+  \includegraphics[width=1\linewidth]{Figures/barrier5.png}
+  \caption{No Tutorials Completed}
+\end{subfigure}%
+\begin{subfigure}{0.3\textwidth}
+  \centering
+  \includegraphics[width=1\linewidth]{Figures/barrier3.png}
+  \caption{Two Tutorials Completed}
+\end{subfigure}
+\begin{subfigure}{0.3\textwidth}
+  \centering
+  \includegraphics[width=1\linewidth]{Figures/barrier0.png}
+  \caption{All Tutorials Completed}
+\end{subfigure}
+\caption{Progress Blocker in Tutorial}
+\end{figure}
+
+\noindent Once all the tutorials in this level are completed and the blockade removed, the user is allowed to move towards the final room where they must throw the ball object into the centre of the desk-like object with a particle effect on it.
+
+\begin{figure}[H]
+\centering
+\centerline{\includegraphics[scale=0.33]{endgoal.png}}
+\caption{The End Goal Object}
+\end{figure}
+
+\noindent Once the ball object collides with the end goal object, the user is taken to the next level where the main aim to to traverse the level and throw the ball object into the next end goal.
+This process is followed for two additional levels for three in total.
 
@@
 %Comprehensive report on the way in which each phase of the life cycle was applied in the development of this artefact.
+
+%Full Level
+\begin{figure}[H]
+\centering
+\begin{subfigure}{0.5\textwidth}
+  \centering
+  \includegraphics[width=1\linewidth]{Figures/fullplan.png}
+  \caption{Provisional Plan}
+\end{subfigure}%
+\begin{subfigure}{0.5\textwidth}
+  \centering
+  \includegraphics[width=1\linewidth]{Figures/full.png}
+  \caption{Screenshot in Unity Editor}
+\end{subfigure}
+\caption{Layout of Full Level (Tutorial)}
+\end{figure}
+
+%Hub
+\begin{figure}[H]
+\centering
+\begin{subfigure}{0.5\textwidth}
+  \centering
+  \includegraphics[width=1\linewidth]{Figures/hubplan.png}
+  \caption{Provisional Plan}
+\end{subfigure}%
+\begin{subfigure}{0.5\textwidth}
+  \centering
+  \includegraphics[width=1\linewidth]{Figures/hub.png}
+  \caption{Screenshot in Artefact}
+\end{subfigure}
+\caption{Layout of Hub Room}
+\end{figure}
+
+%Platform
+\begin{figure}[H]
+\centering
+\begin{subfigure}{0.5\textwidth}
+  \centering
+  \includegraphics[width=1\linewidth]{Figures/platformplan.png}
+  \caption{Provisional Plan}
+\end{subfigure}%
+\begin{subfigure}{0.5\textwidth}
+  \centering
+  \includegraphics[width=1\linewidth]{Figures/platform.png}
+  \caption{Screenshot in Artefact}
+\end{subfigure}
+\caption{Layout of Platforming Tutorial}
+\end{figure}
+
+%WallRun
+\begin{figure}[H]
+\centering
+\begin{subfigure}{0.5\textwidth}
+  \centering
+  \includegraphics[width=1\linewidth]{Figures/wallplan.png}
+  \caption{Provisional Plan}
+\end{subfigure}%
+\begin{subfigure}{0.5\textwidth}
+  \centering
+  \includegraphics[width=1\linewidth]{Figures/wall.png}
+  \caption{Screenshot in Artefact}
+\end{subfigure}
+\caption{Layout of Wall Running Tutorial}
+\end{figure}
+
+%Throw
+\begin{figure}[H]
+\centering
+\begin{subfigure}{0.5\textwidth}
+  \centering
+  \includegraphics[width=1\linewidth]{Figures/throwplan.png}
+  \caption{Provisional Plan}
+\end{subfigure}%
+\begin{subfigure}{0.5\textwidth}
+  \centering
+  \includegraphics[width=1\linewidth]{Figures/throw.png}
+  \caption{Screenshot in Unity Editor}
+\end{subfigure}
+\caption{Layout of Throw Tutorial}
+\end{figure}
+
+%Mcap
+\begin{figure}[H]
+\centering
+\begin{subfigure}{0.5\textwidth}
+  \centering
+  \includegraphics[width=1\linewidth]{Figures/mcapplan.png}
+  \caption{Provisional Plan}
+\end{subfigure}%
+\begin{subfigure}{0.5\textwidth}
+  \centering
+  \includegraphics[width=1\linewidth]{Figures/mcap.png}
+  \caption{Screenshot in Artefact}
+\end{subfigure}
+\caption{Layout of Movement Tutorial}
+\end{figure}
+
+%Enemy
+\begin{figure}[H]
+\centering
+\begin{subfigure}{0.5\textwidth}
+  \centering
+  \includegraphics[width=1\linewidth]{Figures/enemyplan.png}
+  \caption{Provisional Plan}
+\end{subfigure}%
+\begin{subfigure}{0.5\textwidth}
+  \centering
+  \includegraphics[width=1\linewidth]{Figures/enemy.png}
+  \caption{Screenshot in Unity Editor}
+\end{subfigure}
+\caption{Layout of Enemy Tutorial}
+\end{figure}

### 2021-11-03 Final Doc/Chapters/Chapter5.tex
Final Doc Updated

@@
 \label{Chapter5} % For referencing the chapter elsewhere, use \ref{Chapter1} 
-
-%What did you learn while completing this project?
+This chapter will focus on the personal reflections held about this project at its' completion. This process is conducted by answering several questions about the project.
+\\\\
+\indent \textit{What did you learn while completing this project?
 Refer to the decisions that you took, and evaluate them.
 Analyse the strong and weak points of the product and the process that you followed.
-What would you do differently?
+What would you do differently?}
+\\
+learn stuff
+\\\\
+\indent \textit{Did you achieve the objectives that you set for the project? Discuss.}
+\\
+list original goals and discuss
+\\\\
+\indent \textit{How successful were you in managing the project and meeting target dates? Discuss.}
+\\
+While all milestone submissions were delivered on time, the time management of the individual aspects of the project were lacking.
+The group aspect of this project was completed roughly three weeks before final submissions while the individual research project elements, the article and documentation were only completed a few days prior to the deadlines with final checks typically happing on the day of submission.
+\\\\
+\indent \textit{Comments on group work. Responsibilities and contribution of each group member. Problems with cooperation and contributions, and dealing with these problems.}
+\\
+As mentioned in the sections and chapters above each group member was responsible for certain aspects of the artefact development. These were: %itemise and itemise again
+\begin{itemize}
+\item Joshua Esterhuizen was responsible for:
+\begin{itemize}
+\item a
+\item b
+\end{itemize}
 
-%Did you achieve the objectives that you set for the project?  Discuss.
+\item GC Wehemeyer was responsible for:
+\begin{itemize}
+\item c
+\item d
+\end{itemize}
 
-%How successful were you in managing the project and meeting target dates?  Discuss.
+\item Rickus Trollip was responsible for:
+\begin{itemize}
+\item e
+\item f
+\end{itemize}
+\end{itemize}
 
-%Comments on group work.  Responsibilities and contribution of each group member.  Problems with cooperation and contributions, and dealing with these problems.
-
-%The reflection must be structured logically.
-
-%Conclude the reflection with a summary that is a critical evaluation of the process followed with the honours project
+\noindent As indicated in the lists above, there was a roughly equal contribution from each group member.
+There was also no major problems with group dynamics throughout the duration of this project as each member was respectful and eager to learn about the aspects which the others were responsible for.
+\\\\
+\indent \textit{The reflection must be structured logically.}
+\\
+Sure....
+\\\\
+\indent \textit{Conclude the reflection with a summary that is a critical evaluation of the process followed with the honours project.}
+\\
+What?

### 2021-11-04 Final Doc/Chapters/Chapter5.tex
Added group cont. table

@@
 As mentioned in the sections and chapters above each group member was responsible for certain aspects of the artefact development. These were: %itemise and itemise again
-\begin{itemize}
-\item Joshua Esterhuizen was responsible for:
-\begin{itemize}
-\item a
-\item b
-\end{itemize}
-
-\item GC Wehemeyer was responsible for:
-\begin{itemize}
-\item c
-\item d
-\end{itemize}
-
-\item Rickus Trollip was responsible for:
-\begin{itemize}
-\item e
-\item f
-\end{itemize}
-\end{itemize}
+\begin{table}[H]
+\begin{tabular}{l|l|l}
+\hline
+Joshua Esterhuizen       & GC Wehmeyer          & Rickus Trollip           \\ \hline
+Player Movement          & Player Animation     & Main Menu                \\
+Ball physics             & Health Bar           & Enemy AI                 \\
+Moving platforms         & Player Model         & Game music aquisition    \\
+Portal asset development & Enemy Models         & Controller configuration \\
+Teleportation            & Environment assets   & Second Level designer    \\
+Pause Menu               & Third Level designer &                          \\
+Level Transition         &                      &                          \\
+Tutorial level designer  &                      &                          \\ \hline
+\end{tabular}
+\end{table}
 

### 2021-11-06 Final Doc/Chapters/Chapter3.tex
Updated Final Docs

--- 2021-11-03 Final Doc/Chapters/Chapter3.tex
@@
 
-\label{Chapter3} % For referencing the chapter elsewhere, use \ref{Chapter1}
+\label{Chapter3} % For referencing the chapter elsewhere, use \ref{Chapter3}
 
@@
 %Comprehensive report on the way in which each phase of the life cycle was applied in the development of this artefact.
+
+%Full Level
+\begin{figure}[H]
+\centering
+\begin{subfigure}{0.5\textwidth}
+  \centering
+  \includegraphics[width=1\linewidth]{Figures/fullplan.png}
+  \caption{Provisional Plan}
+\end{subfigure}%
+\begin{subfigure}{0.5\textwidth}
+  \centering
+  \includegraphics[width=1\linewidth]{Figures/full.png}
+  \caption{Screenshot in Unity Editor}
+\end{subfigure}
+\caption{Layout of Full Level (Tutorial)}
+\end{figure}
+
+%Hub
+\begin{figure}[H]
+\centering
+\begin{subfigure}{0.5\textwidth}
+  \centering
+  \includegraphics[width=1\linewidth]{Figures/hubplan.png}
+  \caption{Provisional Plan}
+\end{subfigure}%
+\begin{subfigure}{0.5\textwidth}
+  \centering
+  \includegraphics[width=1\linewidth]{Figures/hub.png}
+  \caption{Screenshot in Artefact}
+\end{subfigure}
+\caption{Layout of Hub Room}
+\end{figure}
+
+%Platform
+\begin{figure}[H]
+\centering
+\begin{subfigure}{0.5\textwidth}
+  \centering
+  \includegraphics[width=1\linewidth]{Figures/platformplan.png}
+  \caption{Provisional Plan}
+\end{subfigure}%
+\begin{subfigure}{0.5\textwidth}
+  \centering
+  \includegraphics[width=1\linewidth]{Figures/platform.png}
+  \caption{Screenshot in Artefact}
+\end{subfigure}
+\caption{Layout of Platforming Tutorial}
+\end{figure}
+
+%WallRun
+\begin{figure}[H]
+\centering
+\begin{subfigure}{0.5\textwidth}
+  \centering
+  \includegraphics[width=1\linewidth]{Figures/wallplan.png}
+  \caption{Provisional Plan}
+\end{subfigure}%
+\begin{subfigure}{0.5\textwidth}
+  \centering
+  \includegraphics[width=1\linewidth]{Figures/wall.png}
+  \caption{Screenshot in Artefact}
+\end{subfigure}
+\caption{Layout of Wall Running Tutorial}
+\end{figure}
+
+%Throw
+\begin{figure}[H]
+\centering
+\begin{subfigure}{0.5\textwidth}
+  \centering
+  \includegraphics[width=1\linewidth]{Figures/throwplan.png}
+  \caption{Provisional Plan}
+\end{subfigure}%
+\begin{subfigure}{0.5\textwidth}
+  \centering
+  \includegraphics[width=1\linewidth]{Figures/throw.png}
+  \caption{Screenshot in Unity Editor}
+\end{subfigure}
+\caption{Layout of Throw Tutorial}
+\end{figure}
+
+%Mcap
+\begin{figure}[H]
+\centering
+\begin{subfigure}{0.5\textwidth}
+  \centering
+  \includegraphics[width=1\linewidth]{Figures/mcapplan.png}
+  \caption{Provisional Plan}
+\end{subfigure}%
+\begin{subfigure}{0.5\textwidth}
+  \centering
+  \includegraphics[width=1\linewidth]{Figures/mcap.png}
+  \caption{Screenshot in Artefact}
+\end{subfigure}
+\caption{Layout of Movement Tutorial}
+\end{figure}
+
+%Enemy
+\begin{figure}[H]
+\centering
+\begin{subfigure}{0.5\textwidth}
+  \centering
+  \includegraphics[width=1\linewidth]{Figures/enemyplan.png}
+  \caption{Provisional Plan}
+\end{subfigure}%
+\begin{subfigure}{0.5\textwidth}
+  \centering
+  \includegraphics[width=1\linewidth]{Figures/enemy.png}
+  \caption{Screenshot in Unity Editor}
+\end{subfigure}
+\caption{Layout of Enemy Tutorial}
+\end{figure}
+
+\section{Conclusion}

### 2021-11-06 Final Doc/Chapters/Chapter4.tex
Final Doc Updated
Updated Final Docs

@@
 \label{Chapter4}
+
+\section{Artefact}
+The artefact that was developed is a computer game and is titled \textit{"Puzzle Ball: Spherical Shadows"} and is a self-contained application that can be launched standalone without any additional software needed.
+While it is fairly lightweight on hardware resources for a computer game, it does require more resources than a typical application and may stutter on older systems due to the effects used.
+In terms of the genres it encompass, it would full under the platformer, puzzle and action genres for games and as such is described as a 3D puzzle platformer with aspects of action gameplay played in first person.
+\\\\
+Once the application is launched, the user is taken to the \textit{Main Menu} screen (depicted below) where clicking the text \textit{Play} triggers a function to start the first level - that being the the Tutorial.
+Each group member was responsible for the design of an individual level where the Tutorial/First level being the level undertaken in this project.
+The reason for this is that the research aspect of this project aligns with the goals of a tutorial level.
+
+\begin{figure}[H]
+\centering
+\begin{subfigure}{0.5\textwidth}
+  \centering
+  \includegraphics[width=1\linewidth]{Figures/menu.png}
+  \caption{The Main Menu of the Artefact}
+\end{subfigure}%
+\begin{subfigure}{0.5\textwidth}
+  \centering
+  \includegraphics[width=1\linewidth]{Figures/start.png}
+  \caption{The Starting Point of the Level}
+\end{subfigure}
+\caption{Starting the Game}
+\end{figure}
+
+\noindent One the tutorial level has started, the user is shown the basic character movement controls on the right side of the screen and can continue forward.
+Text based signs were used throughout the level to explain various mechanics or tasks to be completed - an example of this is shown in Figure 4.2 below.
+
+\begin{figure}[H]
+\centering
+\centerline{\includegraphics[scale=0.33]{tutSignEg.png}}
+\caption{A Further Example of the Tutorial Signs}
+\end{figure}
+
+\noindent The user must then make there way to a central area, referred to as the Hub Room, where they are given the choice in what order they would like to complete the five main tutorials.
+These will be discussed and shown below.
+As the user completes the several tutorials, a blockade that restricted movement to the next level is slowly removed as shown below.
+
+\begin{figure}[H]
+\centering
+\begin{subfigure}{0.3\textwidth}
+  \centering
+  \includegraphics[width=1\linewidth]{Figures/barrier5.png}
+  \caption{No Tutorials Completed}
+\end{subfigure}%
+\begin{subfigure}{0.3\textwidth}
+  \centering
+  \includegraphics[width=1\linewidth]{Figures/barrier3.png}
+  \caption{Two Tutorials Completed}
+\end{subfigure}
+\begin{subfigure}{0.3\textwidth}
+  \centering
+  \includegraphics[width=1\linewidth]{Figures/barrier0.png}
+  \caption{All Tutorials Completed}
+\end{subfigure}
+\caption{Progress Blocker in Tutorial}
+\end{figure}
+
+\noindent Once all the tutorials in this level are completed and the blockade removed, the user is allowed to move towards the final room where they must throw the ball object into the centre of the desk-like object with a particle effect on it.
+
+\begin{figure}[H]
+\centering
+\centerline{\includegraphics[scale=0.33]{Figures/endgoal.png}}
+\caption{The End Goal Object}
+\end{figure}
+
+\noindent Once the ball object collides with the end goal object, the user is taken to the next level where the main aim to to traverse the level and throw the ball object into the next end goal.
+This process is followed for two additional levels for three in total  after which the user is taken to a scene where the group members and their contributions are listed with a prompt to close the application.
+
+\begin{figure}[H]
+\centering
+\centerline{\includegraphics[scale=0.33]{Figures/credits.png}}
+\caption{The Credits Screen}
+\end{figure}
+
+\section{Article}
+A literary analysis on the fields of pedagogy, ludology and gamification was conducted and an article written in order to answer the question posed; \textit{What qualities and principles can be applied to a video game to allow it to be used in a learning environment as a means to provide better engagement among certain students by providing an enjoyable delivery of information?}
+\\\\
+This question was then refined and phrased as \textit{What qualities are required for a serious game to be effectively used in an educational environment on various topics?} within the article.
+\\\\
+The results of the research aspect of this project is the answer to these questions which were synthesised from various case studies and the literature analysis conducted.
+
+\section{Conclusion}

### 2021-11-06 Final Doc/Chapters/Chapter5.tex
Updated Final Docs

@@
 
-\label{Chapter5} % For referencing the chapter elsewhere, use \ref{Chapter1} 
+\label{Chapter5} % For referencing the chapter elsewhere, use \ref{Chapter5} 
 This chapter will focus on the personal reflections held about this project at its' completion. This process is conducted by answering several questions about the project.
+
+\section{What was Learnt Throughout this Project}
+In terms of what was learnt during the duration of this project, there were several new technologies and software in addition to a vast amount of knowledge from various fields.
 \\\\
-\indent \textit{What did you learn while completing this project?
-Refer to the decisions that you took, and evaluate them.
-Analyse the strong and weak points of the product and the process that you followed.
-What would you do differently?}
-\\
-learn stuff
+On the software side of things, the largest one was the Unity Editor, specifically the 2019.4.22f build of it, which was the main tool in developing the artefact.
+The choice of using Unity over another game engine, such as Unreal or Godot, was mainly due to the programming language it used (that being C\#).
+This was the language that most of the group, excluding myself, was familiar with and most experienced with when compared to the alternatives.
+Following this, C\# was also a new language learnt for this project and while the initial usage of it was difficult, with the experience  Java, another object-oriented language, it became easy to write and implement the scripts needed.
 \\\\
-\indent \textit{Did you achieve the objectives that you set for the project? Discuss.}
-\\
-list original goals and discuss
+Another technology made use of, and consequently learnt, is GitHub. This was used for version control and was the simplest way to handle it. The GitHub application was used for facilitating this. 
 \\\\
-\indent \textit{How successful were you in managing the project and meeting target dates? Discuss.}
-\\
+\LaTeX was another technology used in the latter half the project.
+It is a software tool that allows for the creation of PDF's and was used for the Article as well as the final documentation.
+While it was initially hard to pick up and use, it also became easier with time.
+It allowed for these respective documents to be presented very neatly and should have been used earlier on in the project's development.
+\\\\
+A fair amount of information concerning game design was also learnt form how psychology plays a factor in the choices game designers take when developing a game or user interface.
+While a fair amount of this knowledge was used when designing the artefact, there is still much more that could have been incorporated - such as the aforementioned use of psychology to style the game better.
+\\\\
+Additionally, various knowledge in the fields used for the research article was learnt.
+These were fields concerning educational and instructional theories, the study of games as well as turning tasks into some form of game be it digital or not.
+These topics were interesting to examine and read about and were a tremendous help on how to approach any future educational endeavours such as tutoring.
+\\\\
+As this project was described to be under \textit{Entertainment Computing}, being able to analyse other computer games was vital to garner a proper understanding of how to go about the development of both the artefact and article.
+This process was heavily aided by Prof.
+Günther Drevin where we were tasked with various presentations on the field of ludology itself and on the analysis of a game - Myst.
+
+\section{Development of Artefact}
+The primary aim of this study was stated as, \textit{to identify what qualities and principles can be applied to a video game to allow it to be used in a learning environment as a means to provide better engagement among certain students by providing an enjoyable delivery of information.}
+
+The objectives needed for the article development were given as:
+\begin{enumerate}
+\item A literature study will need to be performed to gather information with a focus on:
+\begin{enumerate}
+\item Ludology, narratology and simulation to better understand the academia centred around this project;
+\item Other implementations of serious games and the qualities they possess;
+\item The impact and effects of games in early development as this is the main “target audience” if this project were to be implemented as well as in a more general sense;
+\item Previous attempts to integrate game use in learning.
+\end{enumerate}
+\item Collect examples of games that employ some form of teaching 
+(\textit{Where objective 1-b focuses on examples already discussed in an academic sense, this objective will make use of more informal analysis})
+\end{enumerate}
+
+\noindent The primary aim was reached with the outcome of the article finding several qualities that are common amongst most educational games.
+As for the provisional objectives set, all of these were also completed albeit some not being to the standard set out in the beginning.
+For example, while the objective to study the impact of games was discussed in the literature study, there is still a substantial amount of avenues that needed to be considered under this topic as well - such as the psychological effects of games.
+Beyond that, the primary aim was reached in a satisfactory way.
+\\\\
+\noindent Additionally, a secondary aim of this project was to develop an artefact in the form of a computer game which required the following objectives:
+\begin{enumerate}
+\item Learn and understand how to use the chosen development platform and associated environments;
+\item Develop a base to build other levels/scenes off of;
+\begin{enumerate}
+\item Development of basic scripts needed.
+\end{enumerate}
+\item Create a specific scene/level within the aforementioned artefact that specialises in delivering information through various audio-visual stimuli that incorporates the principles and qualities found.
+\end{enumerate}
+
+\noindent The artefact was successfully developed meaning the overall aim was indeed also met.
+While the first two objectives set were also met in full the last objective was only met in part.
+The artefact and research aspects of this project are distinct with no correlation between each other bar the main topic at hand being \textit{Entertainment Computing} and this aim sought to combine them.
+The research was focused on educational games and the level designed was the tutorial level which intends to teach players and as such there is a correlation.
+The qualities identified by the research study were implemented, such as with Reflection being done by giving the user time after each section before continuing to the next.
+However, the objective stated the use of both audio and visual stimuli where the final implementation of the artefact makes use of only visual.
+While this is a small distinction to make on a self-imposed objective, it would have been a fine inclusion to make which would have also aided users who struggle with reading.
+\\\\
+Another aspect of the artefact and article development to discuss is the tame management of it all.
 While all milestone submissions were delivered on time, the time management of the individual aspects of the project were lacking.
-The group aspect of this project was completed roughly three weeks before final submissions while the individual research project elements, the article and documentation were only completed a few days prior to the deadlines with final checks typically happing on the day of submission.
+The group aspect of this project was completed roughly three weeks before final submissions while the individual research project elements, the article and documentation, were only finalised a few days prior to the deadlines with final checks typically happing on the day of submission.
+As such, individual time management on this project was lacking, especially nearing deadlines while the group aspects were handled especially well - even when issues in development arose.
 \\\\
-\indent \textit{Comments on group work. Responsibilities and contribution of each group member. Problems with cooperation and contributions, and dealing with these problems.}
-\\
-As mentioned in the sections and chapters above each group member was responsible for certain aspects of the artefact development. These were: %itemise and itemise again
+Following on from that point, the group aspects of this project were exceptionally well handled.
+As mentioned in the sections and chapters above each group member was responsible for certain aspects of the artefact development.
+These were: %itemise and itemise again
 \begin{table}[H]
@@
 \\\\
-\indent \textit{The reflection must be structured logically.}
-\\
-Sure....
+The only notable incident during development was an issue with the standalone build where certain script references were not working when they did while in the editor.
+While this issue was a stressful issue as it concerned a cornerstone of the game, it was resolved after a few hours debugging of the issue.
+
+\section{Future Work Possibilities}
+While the project is considered to completed as it stands, there are still aspects that can be improved or others added.
+In terms of the artefact, there are numerous game design techniques that could still be taken advantage of.
+One example of this is Culling.
+This is a process by which certain elements within a game are unloaded and removed while the user is not viewing or interacting with them.
+The Unity Editor does include a simple version of this, however, a more robust means of it could be implemented with additional research into the feature.
 \\\\
-\indent \textit{Conclude the reflection with a summary that is a critical evaluation of the process followed with the honours project.}
-\\
-What?
+With respect to the research study and article, there are two possibilities for future work.
+One is to simply continue the research and expand on what was already found and including additional fields to perhaps describe new qualities.
+For a more practical approach, an actual serious game could be designed and developed once a suitable topic is found to present in this format.
+
+\section{Conclusion}
+The process of working through a project in this capacity was an exciting learning experience.
+Being able to work on a topic that has always been a personal interest was an immense help to keep the motivation of working on both an individual research assignment and a group artefact at an all time high.
+The process of creating a provisional plan, performing literary research and documenting the entire development process was certainly a new way of approaching a project for myself.
+This way of completing a project is certainly a major help to finishing the project while maintaining the original aim and scope at all times.
+It was certainly a valuable educational and personal experience which will be useful in all future projects I take part in.

### 2021-11-06 Article/main.tex
Article Proofread

@@
 Due to this teaching and learning methods can be seen as stale to certain students.
-One way to solve this issue is with the implementation of some from of the technology that has developed over the years.
+One way to solve this issue is with the implementation of some form of technology that has developed over the years.
 This study looks at the possibility of adapting various domains of knowledge into digital games referred to as Serious Games.
 The implementation of serious games within teaching may help keep certain students engaged with the content being presented and create further interest in the topic.
-However, before reaching this stage the means to transform these knowledge domains into a serious games must be studied.
-This is done by focusing on three fields in particular, those being Gamification, Ludology and Pedagogy.
+However, before reaching this stage the means to transform these knowledge domains into serious games must be studied.
+This is done by focusing on three fields, in particular, those being Gamification, Ludology and Pedagogy.
 \end{abstract}
@@
 \\\\
-Ackoff and Greenberg\cite{Ackoff2008} explain that the current traditional means of teaching are no longer as relevant as they once were as it is aimed to produce members of society that were likely to not question any fundamental aspects of how things operated.
+Ackoff and Greenberg\cite{Ackoff2008} explains that the current traditional means of teaching are no longer as relevant as they once were as it is aimed to produce members of society that were likely to not question any fundamental aspects of how things operated.
 It is largely a system that focuses on teaching while disregarding learning as the last major stride in development in education was to industrialise it – having them operate efficiently like factories\cite{Ackoff2008}.
@@
 The industrial age being a time of mass-production with the emergence of various new processing technologies and the information age being characterised by the fact that information is being transmitted and generated at an ever-increasing rate due to further technological developments\cite{gibson2006games, Reigeluth1996}.
-The most notable changes between these ages is that the industrial age focused on conformity and compliance while initiative and diversity - where greater value is placed on each individual’s strengths and contribution to a project or organisation – is the focus of the information age\cite{Reigeluth1996}.
+The most notable changes between these ages are that the industrial age focused on conformity and compliance while initiative and diversity - where greater value is placed on each individual’s strengths and contribution to a project or organisation – is the focus of the information age\cite{Reigeluth1996}.
 \\\\
@@
 \\\\
-With the recent developments in technology and the fact that technology, in general, is becoming more accessible, some institutions have adopted some forms of digital learning or supplement traditional teaching with digital assistance.
+With the recent developments in technology and the fact that technology, in general, is becoming more accessible, some institutions have adopted some forms of digital learning or supplemented traditional teaching with digital assistance.
 Deshpande and Huang\cite{Deshpande2011} state that the current generation of students is the first to grow up with abundant access to technology.
@@
 \\\\
-As such, the motivation behind this study is to further investigate the possibility of using video games as a means to encourage learning in teaching environments as current means of teaching may not be optimal for some individuals.
+As such, the motivation behind this study is to further investigate the possibility of using video games as a means to encourage learning in teaching environments as the current means of teaching may not be optimal for some individuals.
 This will be accomplished through studying literature in the relevant fields and identifying the instances where it is viable.
@@
 Ludology is the formal and academic study of games and has roots in studying games through a cultural and social lens by discussing how each interacts with the so-called “spirit of play”\cite{Huizinga1949}.
-However, relatively recently, as early as 2001, the field has shifted and now encompasses the study of digital computer-based games as this is when the first academic peer reviewed journal on the topic was published as well as several international conferences taking place\cite{Frasca2013}.
+However, relatively recently, as early as 2001, the field has shifted and now encompasses the study of digital computer-based games as this is when the first academic peer-reviewed journal on the topic was published as well as several international conferences taking place\cite{Frasca2013}.
 \\\\
@@
 \\\\
-Virvou, Katsionis and Manos\cite{Virvou2005} mention that the endeavour to create serious games has yet to reach schools due to certain criticisms about games in general that hinders this.
+Virvou, Katsionis and Manos\cite{Virvou2005} mention that the endeavour to create serious games have yet to reach schools due to certain criticisms about games in general that hinders this.
 This is due to the fact that discussions around games by educators have largely focused on the social consequences of playing games instead of the educational potential games hold\cite{Squire2003}.
@@
 \subsection{A Pedagogical Approach}
-Pedagogy is the filed that deals with the transferal of knowledge in an educational environment through several lenses such as social, political and cultural\cite{Li2012}.
+Pedagogy is the field that deals with the transferral of knowledge in an educational environment through several lenses such as social, political and cultural\cite{Li2012}.
 As such it encompasses the fields and discussions of instructional design and theory as well as any learning theories – of which several are particularly useful to this study.
@@
 Before discussing the principles that the name refers to in this theory, Merrill\cite{Merrill2002} provides a few definitions for the terms made use of.
-A principle in this context is a relationship that is always true regardless of the environment it is applied within – this being the driving factor for deciding to make use of this theory\cite{Merrill2002}.
-A practice is any instructional activity\cite{Merrill2002}.
+A Principle in this context is a relationship that is always true regardless of the environment it is applied within – this being the driving factor for deciding to make use of this theory\cite{Merrill2002}.
+A Practice is any instructional activity\cite{Merrill2002}.
 A program is a means of instruction that makes use of several practices\cite{Merrill2002}.
@@
 “Demonstration Consistency” explains that any examples or visualisation should be kept in line with the original learning goals\cite{Merrill2002}.
-The next is “Learner Guidance” and states that learners should be shown where the relevant information for problems can be found be it in the form of comparative examples or various representation of one source\cite{Merrill2002}.
+The next is “Learner Guidance” and states that learners should be shown where the relevant information for problems can be found be it in the form of comparative examples or various representations of one source\cite{Merrill2002}.
 “Relevant Media” explains that when media is used as a means of demonstration, different types can be used provided that they do not fight for a learner’s attention\cite{Merrill2002}.
@@
 Kapp\cite{Kapp2012a} describes various types of knowledge and how to begin developing a gamified system to effectively teach each of them.
-This provides the ground work for answering the question this study poses and as such allows for a more in depth discussion on how to implement serious games.
+This provides the groundwork for answering the question this study poses and as such allows for a more in-depth discussion on how to implement serious games.
 These knowledge domains are described as\cite{Kapp2012a}:
@@
 \subsection{Sampling of Literature}
-During this phase key fields of study were identifies for use in working towards the goal of this study.
+During this phase, key fields of study were identified for use in working towards the goal of this study.
 As discussed above, these included the fields of pedagogy (the study of instructional theory), ludology (the study of games with a focus on digital games) and gamification (the use of game-like elements to solve problems).
-Studying the literature in each of these fields yielded literature that is undoubtedly useful to this study as pedagogy gave insight into instructional theories used in education, ludology provided the necessary understanding of how to study games and the elements that each uses and gamification provided insight into the different knowledge domains and how to best approach each in a teaching environment in addition acting as a bridge for connecting pedagogy to the serious games in ludology.
+Studying the literature in each of these fields yielded literature that is undoubtedly useful to this study as pedagogy gave insight into instructional theories used in education, ludology provided the necessary understanding of how to study games and the elements that each uses and gamification provided insight into the different knowledge domains and how to best approach each in a teaching environment, in addition, acting as a bridge for connecting pedagogy to the serious games in ludology.
 \\\\
@@
 Once enough literature had been acquired and studied, the connections between each of the fields' theory and case studys' design principles were noted.
-This was in attempt to identify an overall pattern in the development of serious games for use particularly for educational or training purposes.
-This included mapping the similarities between the instructional theories to the deign principles of each case study while noting which fields of knowledge the games are a part of.
+This was in an attempt to identify an overall pattern in the development of serious games for use particularly for educational or training purposes.
+This included mapping the similarities between the instructional theories to the design principles of each case study while noting which fields of knowledge the games are a part of.
 
@@
 Merrill's First Principles\cite{Merrill2002} provides a basis to begin development on a framework for serious games as it is already rooted in teaching.
-As such, using this theory in conjunction with the information gained from the case studies and the work done by Kapp\cite{Kapp2012a} it allows for a particular stricture to be followed.
+As such, using this theory in conjunction with the information gained from the case studies and the work done by Kapp\cite{Kapp2012a} allows for a particular stricture to be followed.
 \\\\
@@
 Kapp\cite{Kapp2012a}, in addition to providing definitions of the various knowledge domains, provides some ways that each domain can be taught to best relay that particular type of knowledge.
-While these recommendations are derived under a gamification perspective\cite{Kapp2012a}, that can just as easily be applied for a digital game:
+While these recommendations are derived under a gamification perspective\cite{Kapp2012a}, they can just as easily be applied for a digital game:
 
@@
 \subsection{Case Studies and the Similarities in Design Principles}
-Several case studies were examined in which some form of gamified system or serious game was developed in addition to the author(s) detailing what design principles were followed during the development process.
+Several case studies were examined in which some form of a gamified system or serious game was developed in addition to the author(s) detailing what design principles were followed during the development process.
 There are three main case studies that will be focused on in this study\cite{Dincelli2020,Sheng2007,allers2021children}.
@@
 \\\\
-For the development of the artefact Dincelli and Chengalur-Smith\cite{Dincelli2020} made use of literature from instructional theory and gamification and as a result made use of a few key design principles.
+For the development of the artefact, Dincelli and Chengalur-Smith\cite{Dincelli2020} made use of literature from instructional theory and gamification and as a result made use of a few key design principles.
 The first design principle followed is that the gamified system should make use of a \textit{story-based agent}\cite{Dincelli2020}.
 This means that a game should include some figure or character to guide users through the content as well as making use of story-telling in some capacity which is found to create curiosity within users\cite{Dincelli2020, Kapp2012a}.
-Furthermore, the use of a "choose your own adventure" style creates an interactive narrative by which the user is in control of certain decisions that change how the story plays out also improves learning\cite{Dincelli2020}.
-The second design principle used was that of \textit{reflection} which states that users should be given a moment of respite to dwell on what has previously been presented to them\cite{Dincelli2020,Sheng2007}.Feedback on various metrics of a users performance is also a design principle followed which allows for users to perform self evaluation\cite{Dincelli2020}.
+Furthermore, the use of a "choose your own adventure" style creates an interactive narrative by which the user is in control of certain decisions that change how the story plays out also improve learning\cite{Dincelli2020}.
+The second design principle used was that of \textit{reflection} which states that users should be given a moment of respite to dwell on what has previously been presented to them\cite{Dincelli2020,Sheng2007}.
+Feedback on various metrics of a users performance is also a design principle followed which allows for users to perform self evaluation\cite{Dincelli2020}.
 \\\\
-The findings of this case study was that making use of a gamified system that used either visual stimuli or text were better at relaying information that traditional means and visual stimuli were better than text in terms of recognition, redintegration and ease of learning and they performed similarly in terms of recall, satisfaction and usability\cite{Dincelli2020}.
+The findings of this case study were that making use of a gamified system that used either visual stimuli or text were better at relaying information than traditional means and visual stimuli were better than text in terms of recognition, redintegration and ease of learning and they performed similarly in terms of recall, satisfaction and usability\cite{Dincelli2020}.
 \\\\
 %---------------No. 2
-The next case study is titles \textit{"Anti-phishing phil: the design and evaluation of a game that teaches people not to fall for phish"} and focused on teaching people about phishing and how to avoid becoming a victim to these attacks\cite{Sheng2007}.
+The next case study is titled \textit{"Anti-phishing phil: the design and evaluation of a game that teaches people not to fall for phish"} and focused on teaching people about phishing and how to avoid becoming a victim to these attacks\cite{Sheng2007}.
 \\
-Sheng \textit{et al.}\cite{Sheng2007} made use of learning science theories in the games development and to refine the various iterations throughout the development process.
+Sheng \textit{et al.}\cite{Sheng2007} made use of learning science theories in the development of the game and to refine the various iterations throughout the development process.
 The first two design principles discussed are \textit{reflection} and \textit{story-based agent encironment}\cite{Sheng2007}.
 These have already been mentioned in the previous case study.
-Additionally, \textit{feedback} is also discussed in this study but specifically to how it was implemented.
+Additionally, \textit{feedback} is also discussed in this study but specifically how it was implemented.
 Anti-phishing Phil makes use of feedback both during, though displaying a short message for each choice during gameplay, and after a round of the game, through a score sheet and brief explanation of the links used\cite{Sheng2007}.
@@
 It should be noted that Sheng \textit{et al.}\cite{Sheng2007} mention that procedural knowledge is also referred to as declarative knowledge.
-A similar definition to the one Kapp\cite{Kapp2012a} provides for procedural knowledge is given and as such the definition for declarative knowledge used in this study will be the one provided by Kapp\cite{Kapp2012a}.
+A similar definition to the one Kapp\cite{Kapp2012a} provides for procedural knowledge is given and as such, the definition for declarative knowledge used in this study will be the one provided by Kapp\cite{Kapp2012a}.
 This principle states that these two knowledge domains, conceptual and procedural, hold a mutually supportive influence over the other\cite{Sheng2007}.
@@
 The findings of Anti-phishing phil showed that the serious game approach made users more knowledgeable on the topic and how to go about dealing with phishing\cite{Sheng2007}.
-While the game was a success for the most part, Sheng \textit{et al.}\cite{Sheng2007} mention that the game falls behind in one aspect - some users may become more susceptible to phishing as the game provided a fixed number of indicators to be aware of.
+While the game was a success, for the most part, Sheng \textit{et al.}\cite{Sheng2007} mention that the game falls behind in one aspect - some users may become more susceptible to phishing as the game provided a fixed number of indicators to be aware of.
 \\\\
 %---------------No. 3
-The final case study used is titled \textit{"Children’s Awareness of Digital Wellness: A Serious Games Approach"} and was targeted towards teaching children, particularly preschoolers, about digital well-being and foster cyber security awareness by means of a mobile-based serious game\cite{allers2021children}.
+The final case study used is titled \textit{"Children’s Awareness of Digital Wellness: A Serious Games Approach"} and was targeted towards teaching children, particularly preschoolers, about digital well-being and fostering cyber security awareness employing a mobile-based serious game\cite{allers2021children}.
 One thing to be noted before discussing this case study is that it focused on the design and research needed for such a serious game and stated that future work could include the development and deployment of the game\cite{allers2021children}.
@@
 \\\\
-While this case study\cite{allers2021children} made use of instructional theory targeted towards preschool children\cite{matthews2007,callaghan2018} some the frameworks and learning theory used can also be applied to all serious games.
+While this case study\cite{allers2021children} made use of instructional theory targeted towards preschool children\cite{matthews2007,callaghan2018} some of the frameworks and learning theory used can also be applied to all serious games.
 The first design principle followed was \textit{simplicity} as it allows a user to follow the content adequately and as such learn effectively\cite{allers2021children}.
-This principle is specified to the success of a awareness campaign however can also be applied to a serious game as, depending on the specific level of education, simplicity is vitally important.
+This principle is specified to the success of an awareness campaign however can also be applied to a serious game as, depending on the specific level of education, simplicity is vitally important.
 \\\\\\
@@
 \\\\
-In addition to the above, the study also made use of several elements identified by Callaghan \textit{et al.}\cite{callaghan2018} which are based off how young children, namely preschoolers, learn.
+In addition to the above, the study also made use of several elements identified by Callaghan \textit{et al.}\cite{callaghan2018} which are based on how young children, namely preschoolers, learn.
 The first of these is \textit{clear and simple goals} which is concerned with presenting a user with concise outcomes to work towards\cite{callaghan2018}.
-Similarly with Anti-phishing phil\cite{Sheng2007}, is the element of \textit{quality of feedback and rewards} which deals with how feedback is presented to a user - for example preschoolers may not yet be able to read and as such the feedback must be structured accordingly such as making use of simple visuals\cite{allers2021children}.
-The next element is \textit{Structure of the challenge} consists of setting the difficulty of tasks and changing the difficulty depending on how the user is performing\cite{callaghan2018}.
+Similarly with Anti-phishing phil\cite{Sheng2007}, is the element of \textit{quality of feedback and rewards} which deals with how feedback is presented to a user - for example, preschoolers may not yet be able to read and as such, the feedback must be structured accordingly such as making use of simple visuals\cite{allers2021children}.
+The next element is \textit{Structure of the challenge} consisting of setting the difficulty of tasks and changing the difficulty depending on how the user is performing\cite{callaghan2018}.
 This element can also be described using some of the corollaries from Merril's First Principles\cite{Merrill2002} - which will be discussed in the following section.
@@
 As previously mentioned, this case study has not yet developed the serious game and as such cannot be tested by users.
-However, a expert review was conducted on the design of this serious game of which the outcomes were largely positive as the reviewers "found the implementations of each element satisfactory"\cite{allers2021children}.
+However, an expert review was conducted on the design of this serious game of which the outcomes were largely positive as the reviewers "found the implementations of each element satisfactory"\cite{allers2021children}.
 
@@
 From the literature and case studies examined, there are several key qualities that they share among each other either under the same descriptor or with similar descriptions with different names.
-It is these qualities that will form the basis to answer the question posed in the beginning of this study.
+It is these qualities that will form the basis to answer the question posed at the beginning of this study.
 \\\\
@@
 A user should be presented with feedback on how they are progressing on a given set of tasks within the game at some point and as they progress the amount of feedback should be slowly diminished.
-The feedback amount should also be tied to the performance of the user - increasing if they begin to struggle and decrease if not.
-Since feedback can take on many different forms, the type of feedback as well as the method of delivery is dependant on the topic being taught.
+The feedback amount should also be tied to the performance of the user - increasing if they begin to struggle and decreasing if not.
+Since feedback can take on many different forms, the type of feedback, as well as the method of delivery, is dependant on the topic being taught.
 As part of this quality, a serious game should also be designed to create an environment in which users are able to complete smaller tasks and are rewarded for these smaller successes - as per the ARCS model\cite{keller1987development}.
@@
 From the ARCS model\cite{keller1987development}, specifically Confidence, and Callaghan's\cite{callaghan2018} framework it is clear that a serious game should be structured with simple goals and clear expectations from the user and by structuring a game's instructions in this manner the user will be motivated to continue playing and therefore learning.
-Structuring the problems and tasks within the game should follow a similar method to how Feedback is provided - increasing the difficulty as a user gets them correct and lessening the difficulty when they are struggling to once again keep engagement with the game high.
+Structuring the problems and tasks within the game should follow a similar method to how Feedback is provided - increasing the difficulty as a user gets them correct and lessening the difficulty when they are struggling to once again keep engagement with the game at a high level.
 Merrill's First Principles\cite{Merrill2002} discusses this quality in several Principles and their subsequent corollaries - some of which refer to the difficulty scaling mentioned above.
@@
 \\\\
-The remaining knowledge domains tend to have some heavy overlap depending of the topic being covered.
+The remaining knowledge domains tend to have some heavy overlap depending on the topic being covered.
 Sheng \textit{et al.}\cite{Sheng2007} discussed the Conceptual-Procedural principle in their game's development.
@@
 This study made use of various fields of study as well as case studies of serious games and their design in order to answer the question posed.
-The current limitations of answering the question largely center around the amount of literature sourced.
+The current limitations of answering the question largely centre around the amount of literature sourced.
 In terms of the fields looked at (pedagogy, ludology and gamification) these seem to be sufficient in terms of what literature can be used and as such it is the specific literature used that imposes limitations.
@@
 \\\\
-Furthermore, a more practical approach to future research could include the development of a serious game on a topic based in one of the knowledge domains mentioned.
-This could include the development an artefact for user testing, similarly to Anti-phishing phil\cite{Sheng2007}, based off of the findings of this study or the designing of such an artefact more in line with the "Happy Hippo" game\cite{allers2021children}.
+Furthermore, a more practical approach to future research could include the development of a serious game on a topic based on one of the knowledge domains mentioned.
+This could include the development of an artefact for user testing, similarly to Anti-phishing phil\cite{Sheng2007}, based on the findings of this study or the designing of such an artefact more in line with the "Happy Hippo" game\cite{allers2021children}.
 
 \section{Conclusion}
-This study discussed the current state of the paradigms that instructional institutions are based off of and how society has progressed and developed different needs than the systems in place currently provide.
-As such, research into how serious games can be used in an educational environment was conducted with specific focus on the fields of pedagogy, ludology and gamification in order to answer the question, \textit{what qualities are required for a serious game to be effectively used in an educational environment on various topics}.
+This study discussed the current state of the paradigms that instructional institutions are based on and how society has progressed and developed different needs than the systems in place currently provide.
+As such, research into how serious games can be used in an educational environment was conducted with a specific focus on the fields of pedagogy, ludology and gamification in order to answer the question, \textit{what qualities are required for a serious game to be effectively used in an educational environment on various topics}.
 Through a literature review in these fields, various instructional theories were found that could be helpful to answer the question as they are able to be translated into the context of games relatively easy.
 Furthermore, several research papers were used as case studies to discover what design principles are typically followed in the development of serious games.
-This information was then used to identify what are the major qualities which a serious game should have in order to be effective in a educational environment as well as providing specific recommendations for various knowledge domains.
+This information was then used to identify what are the major qualities which a serious game should have in order to be effective in an educational environment as well as provide specific recommendations for various knowledge domains.
 The qualities identified were allowing for Reflection, providing Feedback, making use of Story elements and a well thought out Structuring of the game.
@@
 \section*{Acknowledgements}
-This article was part of a research project for an Honours degree and as such I would like to thank my supervisor, Günther Drevin, for their aid throughout the year as well as for the lessons on the field of ludology as well as the School of Computer Science and Information Systems at the North West University for providing this opportunity.
+This article was part of a research project for an Honours degree and as such, I would like to thank my supervisor, Günther Drevin, for their aid throughout the year as well as for the lessons on the field of ludology as well as the School of Computer Science and Information Systems at the North-West University for providing this opportunity.
 

### 2021-11-06 Final Doc/Chapters/Chapter4.tex
Article Proofread

@@
 \section{Article}
-A literary analysis on the fields of pedagogy, ludology and gamification was conducted and an article written in order to answer the question posed; \textit{What qualities and principles can be applied to a video game to allow it to be used in a learning environment as a means to provide better engagement among certain students by providing an enjoyable delivery of information?}
-\\\\
-This question was then refined and phrased as \textit{What qualities are required for a serious game to be effectively used in an educational environment on various topics?} within the article.
+A literary analysis on the fields of pedagogy, ludology and gamification was conducted and an article written in order to answer the question posed; \textit{What qualities and principles can be applied to a video game to allow it to be used in a learning environment as a means to provide better engagement among certain students by providing an enjoyable delivery of information?} This question was then refined and phrased as \textit{What qualities are required for a serious game to be effectively used in an educational environment on various topics?} within the article.
 \\\\
 The results of the research aspect of this project is the answer to these questions which were synthesised from various case studies and the literature analysis conducted.
+The literature study of the article is similar to the one conducted in this document with the addition to an analysis of three case studies in detail, one of which was mentioned in the literature study above in Chapter \ref{Chapter2}.
+\\\\
+The three case studies made use of are all titled:
+\begin{itemize}
+\item \textit{"Choose your own training adventure: designing a gamified SETA artefact for improving information security and privacy through interactive storytelling"}
+\item \textit{"Anti-phishing phil: the design and evaluation of a game that teaches people not to fall for phish"}
+\item \textit{"Children’s Awareness of Digital Wellness: A Serious Games Approach"}
+\end{itemize}
+
+\noindent Each case study was analysed to determine how the serious games were developed and which principles, qualities or frameworks were a large contributing factor to the development.
+A summary of the findings from the case studies alone is shown in Table \ref{tab4.1}
+
+\begin{table}[H]
+\caption{Design Principles Defined by Case Study (\cite{Dincelli2020,Sheng2007,allers2021children})}
+\begin{center}
+\begin{tabular}{|c|c|c|c|}
+\hline
+
+\textbf{SETA Artefact} & \textbf{\textit{Anti-Phishing Phil}}& \textbf{\textit{Happy Hippo}} \\
+\hline
+Story-based	& Story-based 			& Simplicity  \\
+Reflection	& Reflection			& Clear and Simple Goals  \\
+Feedback	& Feedback 				& Quality of Feedback and Rewards  \\
+	-		& Conceptual-Procedural	& Structure of the Challenge  \\
+	-		& 		-				& Motion-based Interaction  \\
+\hline
+
+\end{tabular}
+\label{tab4.1}
+\end{center}
+\end{table}
+
+\noindent
 

### 2021-11-06 Final Doc/Chapters/Chapter1.tex
Updated Final Doc with Results

@@
 \indent \textbf{Chapter 3: Development of Artefact and Article} \\
-The accompanying artefact that will be developed as a part of the study will be discussed along with the development process of the artefact.
+The accompanying artefact that will be developed as a part of the study will be discussed along with the development process of the article.
 \\
 \indent \textbf{Chapter 4: Results} \\
-A discussion on the results obtained will be presented in this chapter.
-This chapter will focus more on the application of the acquired knowledge and principles towards the development of the artefact.
+A discussion on the results obtained will be presented in this chapter. This chapter will focus on the main use of the artefact and the qualities an educational game needs.
 \\

### 2021-11-06 Final Doc/Chapters/Chapter4.tex
Updated Final Doc with Results

@@
 \section{Article}
+The individual research aspect of this project yielded a academic article titled \textit{"Linking Gamification, Ludology and Pedagogy: How to Use Serious Games for Various Knowledge Domains"}.
+\\\\
 A literary analysis on the fields of pedagogy, ludology and gamification was conducted and an article written in order to answer the question posed; \textit{What qualities and principles can be applied to a video game to allow it to be used in a learning environment as a means to provide better engagement among certain students by providing an enjoyable delivery of information?} This question was then refined and phrased as \textit{What qualities are required for a serious game to be effectively used in an educational environment on various topics?} within the article.
@@
 
-\noindent
+\noindent In addition to these, qualities were derived from several educational theories discussed in the literature study as well as the findings section of the article.
+These include Merrill's First Principles, the ARCS model for motivation and a framework specific to teaching preschool children.
+\\\\
+The results of this encompass four archetypal qualities needed as well as a few qualities recommendations needed to be taken into account depending on the knowledge domain a topic falls under.
+The reasoning for choosing these specific qualities and recommendations is elaborated in detail in the article itself which can be found in Appendix \ref{AppendixC}.
+In short these qualities are named:
+\begin{enumerate}
+\item Reflection
+\item Feedback
+\item Story-telling
+\item Structuring
+\end{enumerate}
+
+\noindent Reflection is described and giving a user enough time after they have completed a task or presented with new knowledge to think about it on their own without further instruction.
+\\\\
+The next quality is Feedback.
+Users should be given feedback on how they are progressing on a given set of tasks within the game at some point.
+Feedback should also be scaled up or down depending on how a user is progressing - that is, if a user is doing well they require less feedback on where to improve as compared to another user who may be struggling and should require more feedback on how to improve.
+Further than this, the means of presenting feedback is heavily dependant on the topic being taught, how tasks are handles and the general loop of the game.
+In addition to this.
+Feedback also includes the stipulation that the game should foster an environment of smaller accomplishments to keep users engaged with the game.
+\\\\
+Story-telling is also an important quality which centres around keeping engagement with the game high.
+It entails making use a story or role-play within the game or the use of a story-based agent such as a character that would guide users through the material and tasks.
+This can be done through contextual story-telling by having the tasks form part of a story's progression or as the main means of relaying information on a topic.
+\\\\
+The next quality encompasses a major part of the design of the game.
+Structuring refers to both the overall design of a serious game as well as how the tasks within it are designed.
+This quality has several key requirements that should be met for the most optimal experience by a user.
+Goals and expectations should be made simple and clear to a user from the beginning.
+Tasks and problems within the game should also scale in difficulty depending on a user's skill and progression - that is, when a user is struggling the tasks should be made easier until they demonstrate understanding with them upon which the difficulty is increased.
+A serious game in this context should also be designed around the topic making the information or tasks and problems the main focus of the game.
+\\\\
+While the above qualities are intended for use in any serious game being developed, the following section details certain recommendations for various knowledge domains.
+The definitions for each of these was also given in the literature study in Chapter \ref{Chapter2}.
+\\\\
+Both Hi-fidelity and low fidelity simulation games, these being a subset of serious games, are the most useful for teaching content found in the Affective, Soft Skills and Psychomotor domains since the best means to teach these is through immersing the user in the phenomena, repeated application of skills and observation respectively.
+Simulation-type serious games can also be used in the other domains such as with the game used to aid in teaching physics.
+These types of games are also the most effective means for the Psychomotor domain.
+\newpage
+\noindent The remaining knowledge domains tend to have some heavy overlap depending on the topic being covered.
+The Conceptual-Procedural principle is an example of this.
+To reiterate, it simply states that a topic cannot be fully understood from only the procedures or context - both are needed for a deeper understanding.
+As such if a topic where to fall under these domains it is vital to present information in a manner that all aspects are clear to a user.
 
 \section{Conclusion}
+This section dealt with the results generated as part of this research project.
+This included a digital computer game as well as various qualities needed in order for a serious game to be effectively used in an educational environment.
+In brief, these qualities were, Reflection, Feedback, Structuring and Story-telling.

### 2021-11-06 Final Doc/Chapters/Chapter1.tex
Scrum added to Ch3

@@
 \\\\
-Design Science also provides a general structure as to how this project will be completed as shown in Figure 3 below taken from Vaishnavi and Kuechler’s (2004) work.
+Design Science also provides a general structure as to how this project will be completed as shown in Figure \ref{des} below taken from Vaishnavi and Kuechler’s (2004) work.
 This process allows for the development of an artefact alongside the collection of information and knowledge that can be incorporated into the design and development of the artefact as well as the evaluation of the implementation of the qualities onto the artefact.
@@
 \caption{The Design Science Research Process (\cite{vaishnavi2004design})}
+\label{des}
 \end{figure}

### 2021-11-06 Final Doc/Chapters/Chapter3.tex
Added Figures to Ch3
Scrum added to Ch3

@@
 
-\section{Artefact Life Cycle Followed and its Different Phases}
+\section{Development Methodologies Followed and the Phases}
 % Briefly provide general background on the life cycle that was followed and why it is appropriate to this artefact.
+\subsection{Artefact}
+The development of the artefact, that being the computer game, made use of an Agile approach to its' development.
+Specifically, the Scrum methodology was used as it allows for incremental and iterative development and testing of the artefact throughout the development life cycle.
+\\\\
+The Scrum methodology is based on the values and principles set out by the inception of Agile Methodologies in addition to having a foundation of five new values - those being commitment, focus, openness, respect and courage \citep{scrumhermes}.
+The Scum methodology is intended to be used in a team to facilitate development of a system while also assigning certain roles to the members of a team \citep{scrumhermes}.
+These roles are:
+\begin{itemize}
+\begin{multicols}{3}
+\item Scrum Master
+\item Product Owner
+\item Team
+\end{multicols}
+\end{itemize}
+\noindent In the context of this project, the Scum Master role was left unfilled by an individual as
+each group member was responsible for the planning and facilitation as a whole and, as such, technically each member acted as a Scrum Master.
+The Product owner role was held by our supervisor, Prof.
+Günther Drevin, as they were the one the artefact was being developed for as well as demonstrated to throughout the life cycle.
+The Team role was filled by the members of the group as previously mentioned.
+\\\\
+The Scrum methodology makes use of so-called Sprints in the development process with each Sprint being comprised of multiple tasks to be completed.
+Each Sprint is also comprised of five main activities, those being:
+\begin{enumerate}
+\begin{multicols}{2}
+\item Sprint Planning 1
+\item Sprint Planning 2
+\item Sprint
+\columnbreak
+\raggedcolumns
+\item Review
+\item Retrospective
+\end{multicols}
+\end{enumerate}
+
+\noindent The development of this project, due to the smaller size of the group, only made use of one initial planning phase for each Sprint and the Review and Retrospective activities were consolidated into discussing what had been done at each Sprint and what should be moved forward to the next Sprint.
+
+\subsection{Article}
+The development of the article followed the interpretivist paradigm and made use of a combination of Design Science and the Scrum Agile Methodology throughout the development life cycle.
+The Scrum Methodology was discussed above and as such only the design science and interpretivist paradigm will be discussed here.
+\\\\
 
@@
 %Comprehensive report on the way in which each phase of the life cycle was applied in the development of this artefact.
+
+\subsection{Sprint 1: Know the Basics}
+
+\begin{figure}[H]
+\centering
+\includegraphics[scale=0.33]{Figures/level.png}
+\caption{Individual First Level}
+\end{figure}
+
+\subsection{Sprint 2: Initial Development}
+
+\begin{figure}[H]
+\centering
+\includegraphics[scale=0.8]{Figures/floor.png}
+\caption{Floor Detection Visualisation (Own Creation)}
+\end{figure}
+
+\begin{figure}[H]
+\centering
+\includegraphics[scale=0.33]{Figures/testold.png}
+\caption{Test Scene for Initial Player Movement}
+\end{figure}
+
+\subsection{Sprint 3: Full Scale Development}
+
+\begin{figure}[H]
+\centering
+\includegraphics[scale=0.33]{Figures/portalconcept.png}
+\caption{Original Portal Concept}
+\end{figure}
+
+\begin{figure}[H]
+\centering
+\begin{subfigure}{0.5\textwidth}
+  \centering
+  \includegraphics[width=1\linewidth]{Figures/finporta.png}
+  \caption{Main Portal Asset}
+\end{subfigure}%
+\begin{subfigure}{0.5\textwidth}
+  \centering
+  \includegraphics[width=1\linewidth]{Figures/finportb.png}
+  \caption{Tutorial Specific Re-colouration}
+\end{subfigure}
+\caption{Finalised Portal Assest}
+\end{figure}
 
@@
 
+\begin{figure}[H]
+\centering
+\includegraphics[scale=0.45]{Figures/pause.png}
+\caption{Pause Menu}
+\end{figure}
+
+\subsection{Sprint 4: Build and Publish}
+
+\begin{figure}[H]
+\centering
+\includegraphics[scale=0.6]{Figures/thumb.png}
+\caption{The Icon Used for Publication}
+\end{figure}
+
+\section{Description of the Development of the Article}
+%Comprehensive report on the way in which each phase of the life cycle was applied in the development of this artefact.
+
+\subsection{Sprint 1: Research Proposal}
+
+\subsection{Sprint 2: Project Planning}
+
+\subsection{Sprint 3: Sampling and Literature Collection}
+
+\subsection{Sprint 4: Write Article}
+
+\subsection{Sprint 5: Finalise Article}
+
 \section{Conclusion}

### 2021-11-07 Final Doc/Chapters/Chapter3.tex
Updated Final Docs

@@
 \\\\
+The interpretivistic paradigm was chosen as it focuses on research that encompasses various aspects of the social world and society as each individual's  experience is subjective to them \citep{kivunja2017understanding}.
+This paradigm further states that understanding of any aspect of the social world cannot be fully understanded through just one lens which is why this project focused on the three fields of pedagogy, ludology and gamification \citep{kivunja2017understanding}.
+\\\\
+Design Science was used in combination with the Scrum Agile methodology for the development of the article where each Sprint from the Scrum Methodology would mostly correlate to the Process steps of design science as shown in Figure \ref{des}.
+As such the following Sprints were used throughout the project for the article:
+\begin{itemize}
+\item Sprint 1: Research Proposal which is the Awareness of Problem step
+\item Sprint 2: Project Planning which is the Suggestion step
+\item Sprint 3: Sampling and Literature Collection which is the Development step
+\item Sprint 4: Write Article which is the Development step
+\item Sprint 5: Finalise Article which is the Evaluation and Conclusion steps
+\end{itemize}
+
+\noindent
 
@@
 
+\begin{minted}[
+frame=lines,
+framesep=2mm,
+baselinestretch=1.2,
+bgcolor=gray!10,
+fontsize=\footnotesize,
+breaklines, 
+linenos,
+]{csharp}
+/*OnFloor() checks if player is on ground
+     * part of ground detection system
+     */
+    private bool OnFloor() 
+    {
+        //array of raycasts? to check if touching "floor"
+        Collider[] hitColliders = Physics.OverlapBox(transform.position, transform.localScale / 3f, Quaternion.Euler(0, 0, 0), floorMask);
+        bool check = false;
+        //cycle through array >> if none true then not on floor, if just one, on floor
+        for (int i = 0; i < hitColliders.Length; i++)
+        {
+            if (hitColliders[i]) 
+            {
+                check = true;
+            }
+        }
+        return check;
+    }
+\end{minted}
+
 \begin{figure}[H]
@@
 \caption{Floor Detection Visualisation (Own Creation)}
+\label{floor}
 \end{figure}

### 2021-11-07 Final Doc/Chapters/Chapter1.tex
Updated Final Docs

@@
 \\\\
-With the recent developments in technology and the fact that technology, in general, becoming more accessible, some institutions have adopted some forms of digital learning or assist traditional teaching with digital assistance.
+With the recent developments in technology and the fact that technology, in general, is becoming more accessible, some institutions have adopted some forms of digital learning or assist traditional teaching with digital assistance.
 Deshpande and Huang (2011) state that the current generation of students is the first to grow up with abundant access to technology.
@@
 Another is that knowledge and its’ understanding is developed through the findings of the study itself.
-\pagebreak
-Design science is a methodology composed of using analytical techniques and can be used according to many paradigms to perform research in the information systems field (\cite{vaishnavi2004design}).
+\newpage
+\noindent Design science is a methodology composed of using analytical techniques and can be used according to many paradigms to perform research in the information systems field (\cite{vaishnavi2004design}).
 This means of research centres on the development of artefacts to better understand certain aspects through the creation of new knowledge and that assessment of an artefacts performance (\cite{vaishnavi2004design}).
@@
 This process allows for the development of an artefact alongside the collection of information and knowledge that can be incorporated into the design and development of the artefact as well as the evaluation of the implementation of the qualities onto the artefact.
+In  this case, the artefact will take the form of an article.
 
@@
 
-A more detailed breakdown of the project plan is presented in Figure 4 below with provisional dates for the deliverables and the anticipated objectives required to meet them.
+\noindent A more detailed breakdown of the project plan is presented in Figure 4 below with provisional dates for the deliverables and the anticipated objectives required to meet them.
 

### 2021-11-07 Final Doc/Chapters/Chapter2.tex
Updated Final Docs

@@
 
-This current paradigm of education is operated on the basis of standardisation to accommodate the change in societal needs and requirements that the industrial age brought with it (\cite{Reigeluth1996}).
+\noindent This current paradigm of education is operated on the basis of standardisation to accommodate the change in societal needs and requirements that the industrial age brought with it (\cite{Reigeluth1996}).
 Reigeluth (1996) states that this system was developed on the fundamental need of sorting students into different categories and to allow for comparisons so that the training of the workforce could also be separated into different groups, those being labourers, having “hands-on” skills, and managers, who mainly had a managerial skill set.

### 2021-11-07 Final Doc/Chapters/Chapter3.tex
Updated Final Docs

@@
 The artefact is titled \textit{"Puzzle Ball: Spherical Shadows"} and is further categorised as a 3D puzzle platformer with aspects of action gameplay played in first person.
-A playable version of the artefact is available on the website itch.io website\footnote{\url{https://josh-scg.itch.io/puzzle-ball-spherical-shadows}} and the source code of the artefact is available on GitHub\footnote{\url{https://github.com/GCWehmeyer/Spherical_Shadows}}$^{,}$\footnote{\url{https://github.com/Josh-SCG/Spherical_Shadows}}
+A playable version of the artefact is available on the website itch.io\footnote{\url{https://josh-scg.itch.io/puzzle-ball-spherical-shadows}} and the source code of the artefact is available on GitHub\footnote{\url{https://github.com/GCWehmeyer/Spherical_Shadows}}$^{,}$\footnote{\url{https://github.com/Josh-SCG/Spherical_Shadows}}
 
@@
 
-\noindent
+\newpage
 
 \section{Description of the Development of the Artefact}
-%Comprehensive report on the way in which each phase of the life cycle was applied in the development of this artefact.
+This section will detail the development of the computer game artefact but will only include specifics on the aspects which were worked on individually - as such the contributions and accompanying processes of the other group members will not be discussed.
 
 \subsection{Sprint 1: Know the Basics}
+The initial sprint for development of the artefact had a main focus on each group member learning the basics of both game design in general as well the how to use the Unity Editor, specifically the 2019.4.22f version.
+The reason for going with this build of the editor was due to the fact that at the time, it was one that was targeted for long term support by Unity.
+\\\\
+The aim of learning the basics of game design saw each member in the group informally gathering information on various related topics within game design.
+This included topics such as level design and the psychology used during game design in addition to examining so-called "Developer Logs", which is typically a video presentation on the progress made at certain increments during the overall development of a game, by other game designers to gain insight into how the structure of game development typically flows.
+\\\\
+As a part this process, each member of the group was tasked with developing a singular level.
+This was done with the aim to gain practical experience with the Unity Editor as well as serve as a means for each group member to discuss what had been discovered while gathering insight into game design and share that acquired knowledge with the other members.
+Figure \ref{1lvl} shows one of the levels created.
 
@@
 \caption{Individual First Level}
+\label{1lvl}
 \end{figure}
 
+\noindent The resources made use of for this particular sprint, those being any material used in the knowledge gathering phase, were mostly found through a publicly available online excel sheet\footnote{\url{https://docs.google.com/spreadsheets/d/1QhFyPfYSjHv7PjibGrslF3mNW_CIDXWv9o-iQgLbu1o}} which contains information of various aspects of game design.
+\\\\
+This sprint was concluded upon the discussion of what each group member had learnt and with the next sprint being planned. 
+\\\\
+The key aspects from this sprint's knowledge gathering phase were that the ProBuilder tool kit within the Unity Editor would be used for the construction and development of levels moving forward as it allowed for the creation on a singular large object which could be adjusted and shaped.
+Using this one object in place of many smaller ones arranged in the same shape allowed for a less computational intensive process when the application is run due to the way a scene is loaded.
+\\\\
+Additionally, the character controller, that being how the in-game character is affected by a user's inputs, would be developed from the ground up in place of using the one pre-built by Unity as it allows for the most customisation of features.
+
 \subsection{Sprint 2: Initial Development}
-
-\begin{minted}[
-frame=lines,
-framesep=2mm,
-baselinestretch=1.2,
-bgcolor=gray!10,
-fontsize=\footnotesize,
-breaklines, 
-linenos,
-]{csharp}
-/*OnFloor() checks if player is on ground
-     * part of ground detection system
-     */
-    private bool OnFloor() 
-    {
-        //array of raycasts? to check if touching "floor"
-        Collider[] hitColliders = Physics.OverlapBox(transform.position, transform.localScale / 3f, Quaternion.Euler(0, 0, 0), floorMask);
-        bool check = false;
-        //cycle through array >> if none true then not on floor, if just one, on floor
-        for (int i = 0; i < hitColliders.Length; i++)
-        {
-            if (hitColliders[i]) 
-            {
-                check = true;
-            }
-        }
-        return check;
-    }
-\end{minted}
 
@@
 \caption{Test Scene for Initial Player Movement}
+\end{figure}
+
+\begin{figure}[H]
+\centering
+\begin{subfigure}{0.5\textwidth}
+  \centering
+  \includegraphics[scale=1.4]{Figures/crossold.png}
+  \caption{Place holder Crosshair}
+\end{subfigure}%
+\begin{subfigure}{0.5\textwidth}
+  \centering
+  \includegraphics[scale=1]{Figures/crosshair.png}
+  \caption{Finalised Crosshair made with GIMP}
+\end{subfigure}
+\caption{Crosshair Development}
 \end{figure}

### 2021-11-07 Final Doc/Chapters/Chapter5.tex
Updated Final Docs

@@
 \\\\
-Another technology made use of, and consequently learnt, is GitHub. This was used for version control and was the simplest way to handle it. The GitHub application was used for facilitating this. 
+Another technology made use of, and consequently learnt, is GitHub.
+This was used for version control and was the simplest way to handle it.
+The GitHub Desktop application was used for facilitating this.
 \\\\
@@
 It allowed for these respective documents to be presented very neatly and should have been used earlier on in the project's development.
-\\\\
+\\
 A fair amount of information concerning game design was also learnt form how psychology plays a factor in the choices game designers take when developing a game or user interface.

### 2021-11-07 Final Doc/Chapters/Chapter3.tex
Update Final Docs

@@
 \subsection{Sprint 2: Initial Development}
+During this sprint, the basis to develop future levels was completed.
+This included, from this contribution, the development of various back-end scripts.
+These scripts form the basic character controller of the game are used in conjunction.
+These included scripts for:
+\begin{itemize}
+\item Camera Movement and the Input Controls\footnote{\href{https://github.com/Josh-SCG/Spherical_Shadows/blob/main/Assets/Scripts/PlayerCameraLook.cs}{PlayerCameraLook.cs}}
 
-\begin{figure}[H]
-\centering
-\includegraphics[scale=0.8]{Figures/floor.png}
-\caption{Floor Detection Visualisation (Own Creation)}
-\label{floor}
-\end{figure}
+\item Player Movement and the Input Controls\footnote{\href{https://github.com/Josh-SCG/Spherical_Shadows/blob/main/Assets/Scripts/PlayerMovement.cs}{PlayerMovement.cs}}
+
+\item Linking two objects together\footnote{\href{https://github.com/Josh-SCG/Spherical_Shadows/blob/main/Assets/Scripts/LinkObjectMovement.cs}{LinkObjectMovement.cs}}
+
+\item Ability to pick up objects\footnote{\href{https://github.com/Josh-SCG/Spherical_Shadows/blob/main/Assets/Scripts/PickUp.cs}{PickUp.cs}}
+\end{itemize}
+\newpage
+\noindent \textbf{Camera Movement}\\
+The camera movement script handles inputs from the mouse and converts them into how the main character perspective camera should be rotated.
+Additionally, it also rotates the player model and a hidden orientation object which is used to keep track of the direction the user is looking for other functions.
+The range of motion is restricted with the \texttt{Mathf.Clamp()} function from Unity's Library in such a manner that the user can freely move horizontally but not vertically.
+\\\\
+\textbf{Player Movement}\\
+The player movement script is responsible for handling all movement based interactions and as such was tested intensively with the values for variables being tweaked constantly.
+Figure \ref{flrtst} shows the in engine scene where the testing took place at first.
 
@@
 \caption{Test Scene for Initial Player Movement}
+\label{flrtst}
+\end{figure}
+
+\noindent At this point of development this included the following:
+\begin{itemize}
+\item Floor detection and what type of floor
+\item Tracking and modifying the velocity and direction of the player's movement
+\item Amount of friction and drag to apply to the player
+\item Other functionality such as jumping, crouching and dashing
+\end{itemize}
+
+\noindent The floor detection aspect of this script is vital to the entire functionality of the movement system as it declares when, and what type of, movement is being applied to the player from a user's inputs.
+At this point, there are two main components to this functionality - checking when the player is on flat ground as well as a slanted area such as a slope or hill.
+\\\\
+The \texttt{OnFLoor()} function is used to determine whenever the player is on an object with the Floor layermask and returns a boolean based on the result.
+A layermask is an editor based flag that interacts with any raycast or collider based functions.
+When the \texttt{OnFLoor()} returns false, the user's inputs are greatly reduced resulting in it having no impact in some cases.
+Due to this, the function went through several iterations until one was found to be effective in all use cases.
+\\\\
+The initial function made use of a singular downward raycast, that being an object used which returns a boolean depending on if an object with the appropriate mask or tag is in its' path, which caused issues when a player would be halfway over some edge within a scene.
+The second iteration saw use of the \texttt{CheckSphere()} function which returns a boolean if the object with a specific mask is within the bounds of a sphere originating at a certain point.
+This method of implementation had issues where a user would be classified as "on the floor" if they were close enough to a wall while in the air.
+The final implementation of this function took inspiration from how the colliders in a two dimensional game work within Unity - that being a box collider.
+The \texttt{OverlapBox()} works similarly to the \texttt{CheckSphere()} function with the distinction bring the shape of the object.
+This allowed for a tighter fitting method of detection which has no known issues.
+Figure \ref{floor} illustrates these issues visually.
+
+\begin{figure}[H]
+\centering
+\includegraphics[scale=0.61]{Figures/floor.png}
+\caption{Floor Detection Visualisation (Own Creation)}
+\label{floor}
+\end{figure}
+
+\noindent The user's input for movement consisted of the W, A, S and D key on the keyboard with W and S affecting vertical movement and A and D affecting the horizontal movement.
+The movement direction was calculated from these and the current state of the orientation object with a force added in that direction through the \texttt{AddForce()} function.
+The friction and drag variables were handled by Unity with the script altering the values depending on where the player is - either on the floor or the air.
+\\\\
+The remaining functions this script implements are \texttt{Jump()} using the Space Bar, \texttt{Dash()} with the Left Shift key, \texttt{Crouch()} and \texttt{unCrouch()} which are activated with the Left Control key.
+The \texttt{Jump()} adds a vertical force to the player which simulates a jump and can only be done if they are on the floor.
+\texttt{Dash()} on the other hand can be used either on the floor, where an additional force as added to the player launching them forward, or in the air, where the player is moved in the direction the camera is facing.
+This function can also be used infinitely.
+\texttt{Crouch()} and \texttt{unCrouch()} are inverse functions, meaning the effects of one are undone by the other.
+When used, the player is shrunken down slightly and has their movement speed reduced.
+\\\\
+\textbf{Linking Objects}\\
+This script caused two objects, which are set in the editor, as shown in Figure \ref{link}, where the script is placed on one of the objects and the other assigned as the "Linked Object Position" variable.
+This caused the object the script is placed on to warp to and follow the other object.
+This was used for the ball object the player interacts with and the camera.
+
+\begin{figure}[H]
+\centering
+\includegraphics[scale=1]{Figures/link.png}
+\caption{Linking Objects in Editor}
+\label{link}
 \end{figure}

### 2021-11-07 Final Doc/Chapters/Chapter4.tex
Update Final Docs

@@
 \centering
-\centerline{\includegraphics[scale=0.33]{Figures/credits.png}}
+\centerline{\includegraphics[scale=0.25]{Figures/credits.png}}
 \caption{The Credits Screen}
@@
 
+\noindent A list of all assets made use of during the development of the artefact, such as models and music, can be found on the GitHub repositories\footnote{\url{https://github.com/GCWehmeyer/Spherical_Shadows/blob/main/References.txt}}$^{,}$\footnote{\url{https://github.com/Josh-SCG/Spherical_Shadows/blob/main/References.txt}}
 \section{Article}

### 2021-11-07 Final Doc/Chapters/Chapter3.tex
Updated Final Doc

@@
 
+\noindent \textbf{Pick Up}\\
+This script provides functionality for the user to interact with objects, specifically the ball object used throughout the game, and be able to pick them up, hold them for a time and throw them when required.
+It is comprised of three main functions - \texttt{PickUpObject()}, \texttt{DropThrowObject()} and \texttt{MoveObject()}.
+This script uses a raycast sent towards the centre of the screen and if an object with a rigid body, such as the player (excluded from this script) which is an object that is capable of interacting with the physics engine of the game, is in the path it is picked up by using the E key.
+Once this is done the object is moved toward the player's hand, shrunken down slightly and the collider of the object made inert.
+From this point, the object is then moved alongside the player with the linking script and when E is pressed while the player has an object it is launched in the direction the player is looking - that is the centre of the screen.
+\\\\
+Aside from scripts, a player prefab and crosshair were created.
+A prefab is a collection of objects, scripts and/or relations set in the editor that can be stored as if it were one object so that it can be "dragged and dropped" as needed.
+Figure \ref{cross} shows the place holder crosshair that was used until this point and the finalised crosshair.
+This was implemented to display where the centre of the screen is to a user.
+
 \begin{figure}[H]
@@
 \caption{Crosshair Development}
+\label{cross}
 \end{figure}
+
+\noindent This sprint was concluded when all the above mentioned items were completed in addition to certain others from the remaining group members.
+During the review and retrospective stages, other functions and scripts were discussed for implementation in the following sprint.
 

### 2021-11-08 Final Doc/Chapters/Chapter3.tex
Updated Final Docs Abstract

@@
 \item Ability to pick up objects\footnote{\href{https://github.com/Josh-SCG/Spherical_Shadows/blob/main/Assets/Scripts/PickUp.cs}{PickUp.cs}}
+
+\item Object Rotation\footnote{\href{https://github.com/Josh-SCG/Spherical_Shadows/blob/main/Assets/Scripts/ObjectRotateScript.cs}{ObjectRotateScript.cs}}
 \end{itemize}
@@
 \\\\
-Aside from scripts, a player prefab and crosshair were created.
+\textbf{Object Rotation}\\
+This script, when placed onto any game object like as with the linking script, will cause the object to rotate at a specific speed set in the editor.
+Figure \ref{rot} demonstrated how this looks.
+It makes use of the \texttt{RotateAround()} function where the object was rotated around its' downward facing vector.
+
+\begin{figure}[H]
+\centering
+\includegraphics[scale=1]{Figures/rot.png}
+\caption{Object Rotation Set in Editor}
+\label{rot}
+\end{figure}
+
+\noindent Aside from scripts, a player prefab and crosshair were created.
 A prefab is a collection of objects, scripts and/or relations set in the editor that can be stored as if it were one object so that it can be "dragged and dropped" as needed.
@@
 \subsection{Sprint 3: Full Scale Development}
+This sprint made use of the base developed in the previous one.
+During this sprint, the main focus was on developing the game in full based of the work already done.
+It also included the creation of certain assets, additional scripts, "quality of life" features and the final individual levels.
+These included:
+\begin{itemize}
+\item Ball return functionality\footnote{\href{https://github.com/Josh-SCG/Spherical_Shadows/blob/main/Assets/Scripts/BallReturn.cs}{BallReturn.cs}}
+
+\item Teleportation functionality \footnote{\href{https://github.com/Josh-SCG/Spherical_Shadows/blob/main/Assets/Scripts/TeleportScript.cs}{TeleportScript.cs}} with the inclusion of a portal prefab
+
+\item Implementation of moving platforms\footnote{\href{https://github.com/Josh-SCG/Spherical_Shadows/blob/main/Assets/Scripts/MovingPlatforms.cs}{MovingPlatforms.cs}}
+
+\item Level Switching after completion\footnote{\href{https://github.com/Josh-SCG/Spherical_Shadows/blob/main/Assets/Scripts/EndLevel.cs}{EndLevel.cs}}
+
+\item The development of the first level - that being the tutorial.
+
+\item Ability to pause the game and navigate scenes\footnote{\href{https://github.com/Josh-SCG/Spherical_Shadows/blob/main/Assets/Scripts/PauseMenu.cs}{PauseMenu.cs}}
+\end{itemize}
+
+\textbf{Ball Return}\\
+
+\textbf{Teleportation and Portal Prefab}\\
 
@@
 \end{figure}
+
+\textbf{Ending a Level}\\
+
+\textbf{Tutorial Level Development}\\
 
@@
 
+\textbf{Pause Menu}\\
+
 \begin{figure}[H]
@@
 \caption{Pause Menu}
+\label{pause}
 \end{figure}
@@
 %Comprehensive report on the way in which each phase of the life cycle was applied in the development of this artefact.
+This section will detail the development of the article and the specific sprints taken to complete it.
 
 \subsection{Sprint 1: Research Proposal}
+As stated, this is the "Awareness of Problem" process within design science.
+As the topic the research was to be conducted on was open-ended, this sprint focused on finding a topic.
+There was a personal interest in educational games and as such it became the first topic to be examined if it was viable for a research study.
+This included doing research into what issues educational games could solve.
+The results of this were a list of potential issues ranging from using them to aid psychological treatment to the use of simulations for training.
+The issue settled on was how they can be used in educational institutions which then lead into further research into acceptance of games and existing academically developed games.
+\\\\
+Once this research was completed, a research proposal was drafted and submitted as the conclusion to this step.
 

### 2021-11-08 Final Doc/main.tex
Final Docs Updated
Added group cont. table
Updated Final Docs
Updated Final Docs Abstract

@@
 ]{MastersDoctoralThesis} % The class file specifying the document structure
-
+\usepackage{minted}
+\usepackage{multicol}
 \usepackage{graphicx}
@@
 \usepackage[utf8]{inputenc} % Required for inputting international characters
-\usepackage[T1]{fontenc} % Output font encoding for international characters
+\usepackage[T1]{fontenc} % Output font encoding for international =
+
 \usepackage{booktabs}
@@
 \faculty{\href{http://natural-sciences.nwu.ac.za/}{Faculty of Natural and Agricultural Sciences}} % Your faculty's name and URL, this is used in the title page and abstract, print it elsewhere with \facname
+
+\newcommand{\titleAfrikaans}{Die Eienskappe van Speletjies vir Gebruik in Onderwys}
 
@@
 \addchaptertocentry{\abstractname} % Add the abstract to the table of contents
-The Thesis Abstract is written here (and usually kept to just this page). The page is kept centered vertically so can expand into the blank space above the title too\ldots
+Education is a system that had its' last major revision during the industrial age which saw instructional institutions act like factories with the goal of propelling students through the system as quick as possible.
+Due to this, a curriculum is often standardised and used as a means to teach all students in the same way.
+The issue with this is that some students may not learn effectively with the modes of education presented.
+One possible implementation to aid in solving this problem is the inclusion of digital and computer-based serious games into the modes of instruction.
+\\\\
+This study was focused on identifying possible qualities these types of games should possess to be used effectively within an educational environment.
+In order to reach this goal, a literature study was conducted on the fields of pedagogy, ludology and gamification with each playing a role in better understanding the means of developing these qualities.
+Additionally, several case studies concerning serious game artefacts were examined in which the design philosophies of the serious games were discussed and examined to identify any correlation between instructional theories.
+The results of this section of the project are several key qualities required as well as a brief discussion on how different topics could be approached.
+\\\\
+Furthermore, this project included the development of an artefact in the form of a digital computer game.
+These aspects of the project were conducted simultaneously with minimal correlation.
+The artefact was developed using the Unity Editor and C\# as the main developmental tools.
+The result of this is a short computer game that has a focus on simple puzzle-solving, platforming and action-based gameplay.
+\\\\
+\textbf{Keywords:} Game Design and Development, Gamification, Ludology, Pedagogy, Serious Games, Unity
+
 \end{abstract}
+
+\begin{extraAbstract}
+\addchaptertocentry{\abstractnameExtra} % Add the abstract to the table of contents
+Onderwys is 'n stelsel wat sy laaste groot hersiening tydens die industriële era gehad het, waarin onderriginstellings soos fabrieke opgetree het met die doel om studente so vinnig as moontlik deur die stelsel te dryf.
+As gevolg hiervan word 'n kurrikulum dikwels gestandaardiseer en gebruik as 'n manier om alle studente op dieselfde manier te onderrig.
+Die probleem hiermee is dat sommige studente dalk nie effektief leer met die onderrigmetodes wat aangebied word nie.
+Een moontlike implementering om te help om hierdie probleem op te los, is die insluiting van digitale en rekenaargebaseerde ernstige speletjies in die onderrigmodusse.
+\\\\
+Hierdie studie was gefokus op die identifisering van moontlike eienskappe wat hierdie tipe speletjies behoort te besit om effektief binne 'n opvoedkundige omgewing gebruik te word.
+Ten einde hierdie doel te bereik, is 'n literatuurstudie oor die velde van pedagogie, ludologie en gamification gedoen, met elkeen wat 'n rol gespeel het om die maniere om hierdie eienskappe te ontwikkel beter te verstaan.
+Verder is verskeie gevallestudies oor ernstige speletjie-artefakte ondersoek waarin die ontwerpfilosofieë van die ernstige speletjies bespreek en ondersoek is om enige korrelasie tussen onderrigteorieë te identifiseer.
+Die resultate van hierdie afdeling van die projek is verskeie sleuteleienskappe wat vereis word, asook 'n kort bespreking oor hoe verskillende onderwerpe benader kan word.
+\\\\
+Verder het hierdie projek die ontwikkeling van 'n artefak in die vorm van 'n digitale rekenaarspeletjie ingesluit.
+Hierdie aspekte van die projek is gelyktydig uitgevoer met minimale korrelasie.
+Die artefak is ontwikkel met behulp van die Unity Editor en C\# as die belangrikste ontwikkelingsinstrumente.
+Die resultaat hiervan is 'n kort rekenaarspeletjie wat 'n fokus het op eenvoudige legkaartoplossing, platforms en aksie-gebaseerde spel.
+\\\\
+\textbf{Keywords:} Speletjieontwerp en -ontwikkeling, Gamification, Ludologie, Pedagogie, Ernstige Spele, Unity
+
+\end{extraAbstract}
 
@@
 \include{Chapters/Chapter3}
+\include{Chapters/Chapter4} 
+\include{Chapters/Chapter5}
 
@@
 
-\printbibliography[heading=bibintoc]
+\printbibliography[heading=bibintoc,title=Reference List]
 

### 2021-11-08 Final Doc/Chapters/Chapter3.tex
Updated Final Docs

@@
 \subsection{Sprint 4: Build and Publish}
+This sprint was focused on having the artefact being available standalone without the need of the editor.
+\\\\
+The Unity Editor has a function to export the game as a standalone application without the need of the editor.
+The settings for this range from they level of detail to be kept from the original assets, such as the models, and the quality of lighting.
+The overall quality setting of "High" was chosen as it allows for a balance between visual quality and performance.
+Performance in this regard refers to how well the application ran on a system without a dedicated graphics card unit.
+Additionally, an icon for the executable file could be set here.
+\\\\
+Once the build settings had been finalised the artefact was exported from the Unity Editor as a standalone application.
+During this process, unforeseen complications arose.
+The main issue here was that certain references between certain scripts were returning null values.
+These references functioned as intended while within the editor which caused initial confusion.
+As a result from this, certain scripts were slightly reworked so that the necessary references would work again.
+\\\\
+Once the above complication was dealt with, the game was published on itch.io, a video game hosting website, where it is available for download\footnote{\url{https://josh-scg.itch.io/puzzle-ball-spherical-shadows}}.
+Figure \ref{thumb} is the icon used as the icon that is displayed on the website.
 
@@
 \caption{The Icon Used for Publication}
+\label{thumb}
 \end{figure}
@@
 \subsection{Sprint 2: Project Planning}
+This phase of the project included the development of a provisional project plan which included discussions around which paradigm the research would be classified under.
+The interpretivistic paradigm was chosen for the fact that it caters for research which needs to be done through multiple viewpoints, fields or lenses.
+During this phase, the fields that were to be researched were finalised.
+These being pedagogy, ludology and gamification.
+It was also decided during this phase that case studies would be used as well.
+The aims and objectives set out during the previous phase were also refined.
+\\\\
+This phase was completed upon the submission of the planning document.
 
@@
 \section{Conclusion}
+This section detailed the developmental processes and phases of both the artefact and article that form a part of this project as well as the issues faced at certain points.
+For both, an adapted Agile methodology closer to the Scrum methodology was used with the article blending that with design science.

### 2021-11-08 Final Doc/Chapters/Chapter3.tex
Updated Final Doc

@@
 \subsection{Sprint 3: Sampling and Literature Collection}
+This sprint encompasses the collection of all relevant literature required to effectively answer the question posed in the article and the research project. 
+\\\\
+The initial collection of literature was only comprised of the three fields mentioned above.
+Once this step was completed, a literature review on the collected studies and articles was written.
+During this, only certain theories or models were discussed from the relevant fields based on whether they would be helpful when answering the question of this research.
+As such, a robust instructional theory and a theory dealing with motivation were discussed from pedagogy.
+Explanations of the field of ludology in addition to the topics of serious games and games as simulations.
+From gamification, the different classifications of knowledge and how they can each be effectively taught using games was taken.
+\\\\
+Academic papers in which a serous game was designed and/or implemented were also examined during this phase.
+This was done to gain insight into what design philosophies serious games typically make use of and how that affects the successfulness of the game.
+\\\\
+It was also during this sprint that an informal look at video game tutorials took place for additional hands-on understanding.
+This was done as the digital games distributor, Steam, held an event titled "Next Fest" which features demonstrations of many soon to release games and as such were mainly tutorial sections which aimed to teach players the controls of the games.
+While this information was not explicitly used in the study, it did provide certain practical understanding of how select types of games may be structured.
+\\\\
+This sprint was concluded when the literature study was to be submitted.
 
 \subsection{Sprint 4: Write Article}
+This sprint, being the Development step of the design science process, saw an article based off of the research already done until this point be written. 
+\\\\
+This phase included the writing of the article from the introduction until the findings section.
+As such, the content covered at this point was the problem statement, a suggestion to address it, the literature needed to address it and the aforementioned case studies.
+The methodology for the synthesis process was also described during this phase and as such it included the following steps:
+\begin{enumerate}
+\item Literature surrounding the applicable fields was researched (Already completed at this point)
+\item Case studies concerning serious games was studied and similarities noted (Already completed at this point)
+\item Select theories that aid this process were pinpointed 
+\item From this research, recommendations for the knowledge domains were made
+\end{enumerate}
+
+\noindent The remaining two phases are a part of the following sprint in development as this sprint was concluded when the above was completed.
 

### 2021-11-08 Final Doc/Chapters/Chapter3.tex
Updated Final Docs

@@
 This section will detail the development of the computer game artefact but will only include specifics on the aspects which were worked on individually - as such the contributions and accompanying processes of the other group members will not be discussed.
+\\\\
+Before describing the development life cycle of the artefact, there are some definitions to be aware of:
+\begin{enumerate}
+\item \underline{User} refers to the real person making use of the artefact.
+\item \underline{Player} refers to the in artefact character controlled by a user.
+\item A \underline{Level} or \underline{Scene} refers to a specific section within the artefact - for example, the main menu, tutorial and end credits are all scenes while only the tutorial would additionally be classified as a level.
+\item A \underline{Prefab} allows for the creation, configuration and storage of a \underline{GameObject} - this being any object within the artefact - with all its components, properties and child GameObjects for easy drag and drop usage.
+\item \underline{Character Controller} refers to how the in-game character, the Player, is affected by a user's inputs.
+\item The \underline{Raycast} function projects a ray into the scene, returning a boolean value if a target was successfully hit in addition to other information, such as distance.
+\item A \underline{Collider} component refers to the shape of an object for the purposes of physical collisions and is invisible.
+\item \underline{Layer Mask} refers to an editor based flag that interacts with any raycast or collider based functions to filter out any colliders which are not to be included in generating collisions with.
+\item A \underline{Rigid Body} components allows a GameObject to react to the real-time physics engine - this includes gravity, forces, etc.
+\item An \underline{Asset} refers to any digital item that you can use in your game or project.
+\end{enumerate}
 
@@
 This sprint was concluded upon the discussion of what each group member had learnt and with the next sprint being planned.
+The idea to have the game centre around the use of a ball object was also decided at this time.
 \\\\
@@
 \\\\
-Additionally, the character controller, that being how the in-game character is affected by a user's inputs, would be developed from the ground up in place of using the one pre-built by Unity as it allows for the most customisation of features.
+Additionally, the character controller would be developed from the ground up in place of using the one pre-built by Unity as it allows for the most customisation of features.
 
@@
 \noindent \textbf{Camera Movement}\\
-The camera movement script handles inputs from the mouse and converts them into how the main character perspective camera should be rotated.
-Additionally, it also rotates the player model and a hidden orientation object which is used to keep track of the direction the user is looking for other functions.
+The camera movement script handles inputs from the mouse and converts them into how the main perspective camera should be rotated.
+Additionally, it also rotates the player and a hidden orientation object which is used to keep track of the direction the user is looking for other functions.
 The range of motion is restricted with the \texttt{Mathf.Clamp()} function from Unity's Library in such a manner that the user can freely move horizontally but not vertically.
@@
 Figure \ref{flrtst} shows the in engine scene where the testing took place at first.
+The main proponent of this script is that the Player is able to interact, and be interacted on by, the physics engine of the game.
+This is done by giving the Player GameObject a rigid body.
 
@@
 \noindent The floor detection aspect of this script is vital to the entire functionality of the movement system as it declares when, and what type of, movement is being applied to the player from a user's inputs.
-At this point, there are two main components to this functionality - checking when the player is on flat ground as well as a slanted area such as a slope or hill.
+At this point, there are two main components to this functionality - checking when the Player is on flat ground as well as a slanted area such as a slope or hill.
 \\\\
 The \texttt{OnFLoor()} function is used to determine whenever the player is on an object with the Floor layermask and returns a boolean based on the result.
-A layermask is an editor based flag that interacts with any raycast or collider based functions.
 When the \texttt{OnFLoor()} returns false, the user's inputs are greatly reduced resulting in it having no impact in some cases.
@@
 
-\noindent The user's input for movement consisted of the W, A, S and D key on the keyboard with W and S affecting vertical movement and A and D affecting the horizontal movement.
+\noindent The User's input for movement consisted of the W, A, S and D key on the keyboard with W and S affecting vertical movement and A and D affecting the horizontal movement.
 The movement direction was calculated from these and the current state of the orientation object with a force added in that direction through the \texttt{AddForce()} function.
@@
 The remaining functions this script implements are \texttt{Jump()} using the Space Bar, \texttt{Dash()} with the Left Shift key, \texttt{Crouch()} and \texttt{unCrouch()} which are activated with the Left Control key.
-The \texttt{Jump()} adds a vertical force to the player which simulates a jump and can only be done if they are on the floor.
-\texttt{Dash()} on the other hand can be used either on the floor, where an additional force as added to the player launching them forward, or in the air, where the player is moved in the direction the camera is facing.
+\begin{itemize} 
+\item \texttt{Jump()} adds a vertical force to the player which simulates a jump and can only be done if they are on the floor. 
+\item \texttt{Dash()} on the other hand can be used either on the floor, where an additional force as added to the player launching them forward, or in the air, where the player is moved in the direction the camera is facing.
 This function can also be used infinitely.
-\texttt{Crouch()} and \texttt{unCrouch()} are inverse functions, meaning the effects of one are undone by the other.
+\item \texttt{Crouch()} and \texttt{unCrouch()} are inverse functions, meaning the effects of one are undone by the other.
 When used, the player is shrunken down slightly and has their movement speed reduced.
-\\\\
-\textbf{Linking Objects}\\
+\end{itemize}
+
+\noindent \textbf{Linking Objects}\\
 This script caused two objects, which are set in the editor, as shown in Figure \ref{link}, where the script is placed on one of the objects and the other assigned as the "Linked Object Position" variable.
@@
 \noindent \textbf{Pick Up}\\
-This script provides functionality for the user to interact with objects, specifically the ball object used throughout the game, and be able to pick them up, hold them for a time and throw them when required.
+This script provides functionality for the user to interact with objects, specifically the ball GameObject used throughout the game, and be able to pick them up, hold them for a time and throw them when required.
 It is comprised of three main functions - \texttt{PickUpObject()}, \texttt{DropThrowObject()} and \texttt{MoveObject()}.
-This script uses a raycast sent towards the centre of the screen and if an object with a rigid body, such as the player (excluded from this script) which is an object that is capable of interacting with the physics engine of the game, is in the path it is picked up by using the E key.
-Once this is done the object is moved toward the player's hand, shrunken down slightly and the collider of the object made inert.
-From this point, the object is then moved alongside the player with the linking script and when E is pressed while the player has an object it is launched in the direction the player is looking - that is the centre of the screen.
+This script uses a raycast sent towards the centre of the screen and if a GameObject with a rigid body, excluding the player, is in the path it is picked up by using the E key.
+Once this is done the object is moved toward the player's hand, shrunken down slightly and the collider of the GameObject made inert.
+From this point, the GameObject is then moved alongside the player with the linking script and when E is pressed while the player has an GameObject it is launched in the direction the player is looking - that being the centre of the screen.
 \\\\
 \textbf{Object Rotation}\\
-This script, when placed onto any game object like as with the linking script, will cause the object to rotate at a specific speed set in the editor.
+This script, when placed onto any GameObject like as with the linking script, will cause the GameObject to rotate at a specific speed set in the editor.
 Figure \ref{rot} demonstrated how this looks.
-It makes use of the \texttt{RotateAround()} function where the object was rotated around its' downward facing vector.
+It makes use of the \texttt{RotateAround()} function where the GameObject is rotated around its' downward facing vector.
 
@@
 
-\noindent Aside from scripts, a player prefab and crosshair were created.
-A prefab is a collection of objects, scripts and/or relations set in the editor that can be stored as if it were one object so that it can be "dragged and dropped" as needed.
+\noindent Aside from scripts, a Player Prefab and crosshair were created.
+This Prefab is comprised of the Player model, the necessary scripts and relation for the Character Controller to function.
 Figure \ref{cross} shows the place holder crosshair that was used until this point and the finalised crosshair.

### 2021-11-08 Final Doc/Chapters/Chapter3.tex
Article Documentation Complete

@@
 \subsection{Sprint 5: Finalise Article}
+The final phase of developing the article involved formatting it in an academic journal style as well as completing the remaining sections from Sprint 4. 
+\\\\
+From the literature study and review of the case studies, various theories were selected to be used within the synthesis section.
+These included Merrill's First Principles, the ARCS model of motivation, the knowledge domain explanations and a framework for teaching preschool children.
+These were selected on the basis that they provided comprehensive information regarding effective teaching methods which would be combined with the information from the case studies - that being the design principles and philosophies.
+\\\\
+Any and all correlations between these theories and design principles were mapped out and consolidated to produce the several qualities a serious game needs to be effective in an educational context.
+Some principles applied to a certain rule were also applied to others as well when it was deemed to be a helpful factor for the specific quality.
+The results of this are discussed in the following chapter - Chapter \ref{Chapter4}.
+\\\\ 
+The final aspect of development of this article was to format it in an academic journal style. For this, the PDF creation software \LaTeX was used along with an IEEE template document.
 

### 2021-11-08 Final Doc/Chapters/Chapter3.tex
Updated Final Docs

@@
 \item An \underline{Asset} refers to any digital item that you can use in your game or project.
+\item A \underline{Tag} is similar to a layer mask.
 \end{enumerate}
@@
 \centering
-\includegraphics[scale=0.33]{Figures/testold.png}
+\includegraphics[scale=0.28]{Figures/testold.png}
 \caption{Test Scene for Initial Player Movement}
@@
 \centering
-\includegraphics[scale=0.61]{Figures/floor.png}
+\includegraphics[scale=0.665]{Figures/floor.png}
 \caption{Floor Detection Visualisation (Own Creation)}
@@
 \centering
-\includegraphics[scale=1]{Figures/rot.png}
+\includegraphics[scale=1.25]{Figures/rot.png}
 \caption{Object Rotation Set in Editor}
@@
 
-\textbf{Ball Return}\\
-
+\noindent \textbf{Ball Return}\\
+The development of this script was initially intended for use during testing only however the group realised that if a user where to throw the ball GameObject to a place that could not reach or access in the game, they would be unable to progress and as such the script was left in the game.
+\\\\
+The only functionality this script implements is that when a user makes use of the T key, the ball GameObject will be teleported to their current location.
+This was accomplished by setting the ball GameObject's position within the scene to slightly above and in front of the player.
+\\\\
 \textbf{Teleportation and Portal Prefab}\\
-
-\begin{figure}[H]
-\centering
-\includegraphics[scale=0.33]{Figures/portalconcept.png}
-\caption{Original Portal Concept}
-\end{figure}
-
+In a similar fashion, the teleport script works off the same concept to that of the ball return script.
+The difference is that the function implemented within this script, \texttt{OnTriggerEnter()}, makes use of the colliders of a GameObject when it overlaps with another GmaeObject and changes the position accordingly.
+\\\\
+The script can be used in multiple ways as it allows the assignment of both a trigger GameObject and a GameObject to be teleported.
+When the trigger GameObject collides with the GameObject this script is placed on, the GameObject set to teleport will be teleported.
+Figure \ref{tp} illustrates examples of how this was done in the Unity Editor.
 \begin{figure}[H]
@@
   \centering
+  \includegraphics[width=1\linewidth]{Figures/tpp.png}
+  \caption{Trigger is the Player}
+\end{subfigure}%
+\begin{subfigure}{0.5\textwidth}
+  \centering
+  \includegraphics[width=1\linewidth]{Figures/tps.png}
+  \caption{Trigger is the Ball GameObject}
+\end{subfigure}
+\caption{Examples of when the Player is Teleported}
+\label{tp}
+\end{figure}
+
+\noindent The main use of this script is i conjunction with the Portal Prefab.
+This prefab consists of the teleport script, two instances of the moving platform script, two Probuilder GameObjects and a particle system.
+Figure \ref{portals} shows the two types of Portal Prefabs.
+
+\begin{figure}[H]
+\centering
+\begin{subfigure}{0.4\textwidth}
+  \centering
   \includegraphics[width=1\linewidth]{Figures/finporta.png}
@@
 \end{subfigure}%
-\begin{subfigure}{0.5\textwidth}
+\begin{subfigure}{0.4\textwidth}
   \centering
@@
 \caption{Finalised Portal Assest}
+\label{portals}
 \end{figure}
 
+\noindent \textbf{Moving Platforms}\\
+This script works similarly to the rotation script as instead of rotating the object , this script moves an object between two points in a scene. 
+\\\\
 \textbf{Ending a Level}\\
@@
 
+\newpage
 \section{Description of the Development of the Article}

### 2021-11-08 Final Doc/Chapters/Chapter3.tex
Update Final Docs (Loadsheding)

@@
 This script works similarly to the rotation script as instead of rotating the object , this script moves an object between two points in a scene.
+This script makes use of two Empty GameObjects, that being a GameObject with only positional and rotational information without any assets attached, as the two points a GameObject will be moved between.
+The GameOjbect being moved has its' position updated constantly along the path using the \texttt{Lerp()} function which places a GameObject on a path between two points depending on a decimal percentage value.
+When the GameObject reaches a point, it moves back in the opposite direction  towards the other.
+This process is repeated infinitely.
+\\\\
+This script could also be used on any GameObject, such as with the Portal Prefab, but was origionally intended for moving platforms only.
+As such, the player movement script was updated to include the implementation of a platform moving the Player with it.
+This was accomplished by adding a Tag to any GameObject which is intended as a platform and
 \\\\

### 2021-11-08 Final Doc/Chapters/Chapter3.tex
Final Doc Almost Fin

@@
 \end{subfigure}
-\caption{Finalised Portal Assest}
+\caption{Finalised Portal Prefab}
 \label{portals}
@@
 \\\\
-This script could also be used on any GameObject, such as with the Portal Prefab, but was origionally intended for moving platforms only.
+This script could also be used on any GameObject, such as with the Portal Prefab, but was originally intended for moving platforms only.
 As such, the player movement script was updated to include the implementation of a platform moving the Player with it.
-This was accomplished by adding a Tag to any GameObject which is intended as a platform and
+This was accomplished by adding a Tag to any GameObject which is intended as a platform and in the player movement script having a function, \texttt{OnPlatform()}, return a boolean value as with \texttt{OnFloor()} and \texttt{OnSlope()}.
+When true, the raycast used to determine the boolean is also used to get the GameObject platform and apply a subtle force in the direction of the platform.
 \\\\
 \textbf{Ending a Level}\\
-
-\textbf{Tutorial Level Development}\\
-
+This script is used on the completion of a level to load the next level in the gameplay sequence. This is done using the collider of the ball GameObject and Unity's SceneManagement library.
+\\\\
+To progress to the next level, the user must throw the ball GameObject into the designated end goal GameObject and once the \texttt{OnTriggerEnter()} triggers it calls the function \texttt{nextLevel()} which completes a check to identify which scene is loaded and if it is one that has a next level after it, that next level is loaded.
+This also makes use of the build index of each scene.
+\newpage
+\noindent \textbf{Tutorial Level Development}\\
+This next section details the development of the tutorial level.
+This includes level design plans and screenshots of the final version of each section of the level.
+Each section of the tutorial was designed in such a way that it would teach the user the various mechanics implemented in the game.
+\\\\
+The first provisional plan made was for the entire level in a high level overview of what would be handled and the general layout of where.
+This includes laying out each individual rooms location in relation to the level as well the beginning and end points.
+This is shown in Figure \ref{full}.
 %Full Level
@@
 \centering
-\begin{subfigure}{0.5\textwidth}
+\begin{subfigure}{0.45\textwidth}
   \centering
@@
 \end{subfigure}%
-\begin{subfigure}{0.5\textwidth}
+\begin{subfigure}{0.45\textwidth}
   \centering
@@
 \caption{Layout of Full Level (Tutorial)}
+\label{full}
 \end{figure}
+
+\noindent The next piece of the level to be designed was the so-called Hub Room.
+This is the section in the level where the user partakes in the various tutorials.
+The incorporation of portals was intended from the beginning but for a length of time, the hub room made use of the drop-zones as shown in Figure \ref{hub}.
+Nonetheless, once the necessary scripts were developed, the portal prefab was developed and consequently incorporated.
 
@@
 \caption{Layout of Hub Room}
+\label{hub}
 \end{figure}
+
+\noindent The platforming tutorial was designed as a tower to illustrate the vertical movement capabilities of the player and the movement script.
+This tutorial made use of moving platforms and most of the player movement script movement-based functions - i.e.
+\texttt{Jump()} and \texttt{Crouch()}.
+The goal of this tutorial was to climb the tower and drop down the centre towards a portal.
+Figure \ref{platty} shows the plan and final implementation of this section.
 
@@
 \caption{Layout of Platforming Tutorial}
+\label{platty}
 \end{figure}
+
+\noindent Wallrunning was also added to the player movement script during this development phase.
+This makes use of the orientation GameObject mentioned earlier as well as two raycasts to determine if the player is next to a wall and can wallrun.
+Furthermore, a player can only wall run if the function \texttt{OnFloor()} returns false, that is if the player is next to a wall and is not on the floor.
+The basic goal of this tutorial is to reach the other side of the room by using the provided walls.
+If a player were to fall off while attempting this they would be teleported to the nearest floor and given the chance to try again - this being another use of the teleport script.
+Once the player reaches the other side and collides with the particle system the door to the portal in the room is moved and a bridge is brought into the room if the user does not want to wallrun back across the room.
+Figure \ref{wallrun} illustrates the plan and final implementation of this.
 
@@
 \caption{Layout of Wall Running Tutorial}
+\label{wallrun}
 \end{figure}
+
+\noindent The next tutorial is that of throwing.
+This tutorial makes heavy use of the teleport script in multiple forms.
+The first obstacle is a set of barriers that will be moved when hit with the ball GameObject.
+The second is to hit a moving target upon which the player will be moved to the next section of this tutorial.
+The last task is to hit a stationary target which the user must read the sign near it and solve the riddle.
+The player must jump off the ledge and turn around to hit the target.
+Before the target is hit, once the player hits the floor they are teleported back to the top of the ledge.
+Once the target is hit, the player is no longer teleported up and a wall is removed revealing a portal; to conclude this tutorial.
+Figure \ref{throw} shows the plan and finalisation of this section.
 
@@
 \caption{Layout of Throw Tutorial}
+\label{throw}
 \end{figure}
@@
 \caption{Layout of Movement Tutorial}
+\label{moves}
 \end{figure}
@@
 \caption{Layout of Enemy Tutorial}
+\label{enemy}
 \end{figure}
 
-\textbf{Pause Menu}\\
+\noindent \textbf{Pause Menu}\\
+The last feature to be added to the game was the implementation of a pause menu.
+This included a script to handle the toggling of sound on a level and the cursor visibility when the game is paused.
+Additionally, this included the development of the pause screen into the player prefab - it also being toggled on and off.
+The game can be paused with the use of the ESC key.
+Once paused, a user can either resume playing by using ESC again or making use of the button on screen.
+Furthermore, buttons were included on the top right side of the screen which allows a user to select which scene they wish to go to.
+Figure \ref{pause} shows the pause menu along with the associated buttons.
 
@@
 \label{pause}
+\end{figure}
+
+\noindent The construction of the pause menu, other than the script was directly added to the player prefab in the form of images and text overlays.
+These were then linked to the functions in the script which handled all the various buttons shown.
+Figure \ref{pause2} illustrates the relations and links needed for the pause menu - it also shows most of the player prefab configuration.
+
+\begin{figure}[H]
+\centering
+\includegraphics[scale=1]{Figures/pause2.png}
+\caption{Pause Menu}
+\label{pause2}
 \end{figure}

### 2021-11-09 Final Doc/Chapters/Chapter3.tex
Final Doc Finished - pre check

@@
 
+\noindent The next tutorial is meant to get the user acclimated to using the air version of the \texttt{Dash()} function.
+Through this, multiple spherical objects were placed in this section and when the player collides with them a column is removed from in front of the portal of this section.
+The user is introduced to this mechanic by being corralled into one within the view of a similar column.
+There are also multiple signs within this section explaining the goal of this section.
+Figure \ref{moves} depicts the plan and final version of this tutorial.
+
 %Mcap
@@
 \end{figure}
+
+\noindent The final tutorial section developed was the enemy section.
+In this section, the user can make use of all other mechanics to get through this section.
+This involves wallrunning and simple platforming before being confronted with a larger enemy before the portal.
+Figure \ref{enemy} shows the plan and final version of this section.
 
@@
 \centering
-\includegraphics[scale=0.45]{Figures/pause.png}
+\includegraphics[scale=0.3]{Figures/pause.png}
 \caption{Pause Menu}

### 2021-11-09 Final Doc/Chapters/Chapter1.tex
Final Push

@@
 A student's learning experience is typically affected by their enjoyment of interacting with the material and their general interest in the topic material presented.
-As such, a student will have their own individual preferences and style of learning.
+As such, a student will have their individual preferences and style of learning.
 Due to the rapid and prevalent development and accessibility of technology, using digital computer games as a means of teaching has been a topic of discussion.
@@
 This artefact will be developed alongside the individual research projects of the group members.
-It should be noted that this artefact is developed as a standalone project with no links to the research projects of the group members but may be influenced by each members individual research projects as the research may help develop certain aspects of the artefact.
+It should be noted that this artefact is developed as a standalone project with no links to the research projects of the group members but may be influenced by each member's individual research projects as the research may help develop certain aspects of the artefact.
+
 \pagebreak
@@
 \subsection{Problem Description and Background}
-Education as it stands is still built on a system that is no longer needed in modern society.
+Education, as it stands, is still built on a system that is no longer needed in modern society.
 Ackoff and Greenberg (2008) explain that the current traditional methods of teaching are no longer as relevant as they once were as it is aimed to produce members of society that were likely to not question any fundamental aspects of how things operated.
@@
 \\\\
-With the recent developments in technology and the fact that technology, in general, is becoming more accessible, some institutions have adopted some forms of digital learning or assist traditional teaching with digital assistance.
+With the recent developments in technology and the fact that technology, in general, is becoming more accessible, some institutions have adopted some forms of digital learning or assisted traditional teaching with digital assistance.
 Deshpande and Huang (2011) state that the current generation of students is the first to grow up with abundant access to technology.
@@
 Virvou, Katsionis and Manos (2005) echo the point that computer games are popular among individuals who are in schools and as such could provide a means to deliver content in an interesting and engaging manner.
-As such, the motivation behind this study is to further investigate the possibility of using video games as a means to encourage learning in teaching environments as current means of teaching may not be optimal for some individuals.
+As such, the motivation behind this study is to further investigate the possibility of using video games as a means to encourage learning in teaching environments as the current means of teaching may not be optimal for some individuals.
 
@@
 \subsection{Research Question and Expected Outcomes}
-The main research question this project is set out to answers is; “What qualities does a video game require in order for it to be useful in relaying certain information to a user whilst still maintaining proper engagement with the user?”.
+The main research question this project is set out to answer is; “What qualities does a video game require in order for it to be useful in relaying certain information to a user whilst still maintaining proper engagement with the user?”.
 The findings resulting from answering this question will be used in the development of a specific video game level that will attempt to teach users about the games various mechanics and enemy types presented.
 \\\\
-The expected outcomes of this project is the aforementioned game as the artefact as well as a description of the qualities a game must exhibit to effectively relay information in an educational sense.
+The expected outcomes of this project are the aforementioned game as the artefact as well as a description of the qualities a game must exhibit to effectively relay information in an educational sense.
 
@@
 \subsection{Research Paradigm and Methodology Used}
-The research aspect of this project will be conducted in accordance with the interpretivist paradigm.
+The research aspect of this project will be conducted under the interpretivistic paradigm.
 The main undertaking of this paradigm is to understand the world and its’ various aspects according to the subjective experiences of people (\cite{kivunja2017understanding}).
 It is due to this reason that this project uses this paradigm as what each student requires to efficiently learn is subjective to each individual.
-Kivunja and Kuyini  (2017) further mention that the interpretivist paradigm makes use of subjective epistemology which allows the researcher to analyse the data, which in this project is the principles and qualities that allow for a game to be effective in a learning environment, through their individual cognitive processes.
+Kivunja and Kuyini  (2017) further mention that the interpretivistic paradigm makes use of subjective epistemology which allows the researcher to analyse the data, which in this project is the principles and qualities that allow for a game to be effective in a learning environment, through their cognitive processes.
 \\\\
@@
 \\\\
-The second aspect of this project is the development of a computer game as the artefact.
+The second aspect of this project is the development of a computer game as an artefact.
 This artefact will be developed as a group effort with each member focusing on specific areas of development and all members having some contribution to other areas.
@@
 As the planning only depicts and describes the basic structure and aims of the project, once development on the artefact begins the specifications and features may continue to increase in number which may cause the project to fail expectations set.
-As such, the intended features of the artefact should be discussed and solidified early on in its’ development to mitigate this specific risk.
+As such, the intended features of the artefact should be discussed and solidified early on in its' development to mitigate this specific risk.
 \\\\
-The artefact's development and the research aspect of this project is also at risk of unforeseen events.
+The artefact's development and the research aspect of this project are also at risk of unforeseen events.
 In an attempt to mitigate the harm that may be caused by these events, the artefact is being developed in such a manner to facilitate both contact sessions as well as fully digitally.
@@
 \\\\
-However, it should be noted that each member is still solely responsible for their individual research study project that may directly or indirectly link to the artefact.
+However, it should be noted that each member is still solely responsible for their research study project that may directly or indirectly link to the artefact.
 
@@
 \section{Ethical Implications of Project}
-This project will not make use of external participants in a formal manner that would require any ethical implications as the only participants towards the development of this projects is the developers working on the artefact itself.
+This project will not make use of external participants in a formal manner that would require any ethical implications as the only participants towards the development of this project is the developers working on the artefact itself.
 The prescribed ethics form has been completed and attached.
@@
 \indent \textbf{Chapter 1: Introduction} \\	
-The problem that is being researched, the qualities of games needed for use in education, is discussed in Chapter 1.
+The problem that is being researched, the qualities of games needed for use in education, are discussed in Chapter 1.
 Information on the background of this problem, similar research and the research contribution will be discussed.
@@
 \indent \textbf{Chapter 5: Reflection} \\
-The contents and results of the study will be briefly discussed and reiterated in an overview in addition to a brief discussion on how the project could possibly progress.
+The contents and results of the study will be briefly discussed and reiterated in an overview in addition to a brief discussion on how the project could progress.
 \\

### 2021-11-09 Final Doc/Chapters/Chapter2.tex
Final Push

--- 2021-11-03 Final Doc/Chapters/Chapter2.tex
@@
 
-This current paradigm of education is operated on the basis of standardisation to accommodate the change in societal needs and requirements that the industrial age brought with it (\cite{Reigeluth1996}).
+\noindent This current paradigm of education is operated based on standardisation to accommodate the change in societal needs and requirements that the industrial age brought with it (\cite{Reigeluth1996}).
 Reigeluth (1996) states that this system was developed on the fundamental need of sorting students into different categories and to allow for comparisons so that the training of the workforce could also be separated into different groups, those being labourers, having “hands-on” skills, and managers, who mainly had a managerial skill set.
@@
 
-\subsection{Learner's at the Core of Learning}
+\subsection{Learners at Core of Learning}
 Some instructional theories focus on students learning with minimal interaction with a teacher or instructor.
@@
 “Demonstration consistency” explains that any examples or visualisation should be kept in line with the original learning goals (\cite{Merrill2002}).
-The next is “Learner Guidance” and states that learners should be shown where the relevant information for problems can be found be it in the form of comparative examples or various representation of one source (\cite{Merrill2002}).
+The next is “Learner Guidance” and states that learners should be shown where the relevant information for problems can be found be it in the form of comparative examples or various representations of one source (\cite{Merrill2002}).
 “Relevant Media” explains that when media is used as a means of demonstration, different types can be used provided that they do not fight for a learner’s attention (\cite{Merrill2002}).
@@
 
-\subsection{The Influence of Motivation}
+\subsection{Influence of Motivation}
 A learner's motivation is what will drive them to engage with and enjoy the content being studied.
@@
 These types of games have already had an impact on the military, medical and higher business education fields early in their conception and this trend continues to this day with most serious games being used within the medical fields specifically (\cite{Annetta2008, DeGloria2014}).
-However, there were attempts to use serious games, as simulations, within physics and engineering (\cite{Deshpande2011}).
+However, there were attempts to use serious games, like simulations, within physics and engineering (\cite{Deshpande2011}).
 
 \subsection{Games as Simulation}
-Games have also found use as a means to simulate models, environments and a myriad of other systems.
+Games have also found uses as a means to simulate models, environments and a myriad of other systems.
 As mentioned in the previous subsection, there are a few games used for medical training (\cite{Burke2009}) and to be effective at teaching and demonstrating these topics, digital games need to be used as a simulation.
@@
 \\\\
-This section on gamification has thus discussed what gamification entails and how it usually implemented.
+This section on gamification has thus discussed what gamification entails and how it is usually implemented.
 A focus on the types of knowledge it is able to gamify is also presented as well as one way to effectively teach that type of knowledge.
@@
 The study made use of several images and took images of the brain’s activity in participants while showing them these different images, examples of these pictures are shown below in the figure (\cite{Gomez2019}).
-The study found that people who did play Pokémon extensively as children, had different activity in their visual cortex when looking at the image of a Pokémon as compared to the other images in addition to the other participants, those who had no interaction with Pokémon growing up, had almost no activity when looking at images of Pokémon (\cite{Gomez2019}).
+The study found that people who did play Pokémon extensively as children, had different activities in their visual cortex when looking at the image of a Pokémon as compared to the other images in addition to the other participants, those who had no interaction with Pokémon growing up, had almost no activity when looking at images of Pokémon (\cite{Gomez2019}).
 Gomez et al.

### 2021-11-09 Final Doc/Chapters/Chapter4.tex
Article Documentation Complete
Final Push

@@
 While it is fairly lightweight on hardware resources for a computer game, it does require more resources than a typical application and may stutter on older systems due to the effects used.
-In terms of the genres it encompass, it would full under the platformer, puzzle and action genres for games and as such is described as a 3D puzzle platformer with aspects of action gameplay played in first person.
+In terms of the genres it encompasses, it would fall under the platformer, puzzle and action genres for games and as such is described as a 3D puzzle platformer with aspects of action gameplay played in the first person.
 \\\\
-Once the application is launched, the user is taken to the \textit{Main Menu} screen (depicted below) where clicking the text \textit{Play} triggers a function to start the first level - that being the the Tutorial.
+Once the application is launched, the user is taken to the \textit{Main Menu} screen (depicted below) where clicking the text \textit{Play} triggers a function to start the first level - that being the Tutorial.
 Each group member was responsible for the design of an individual level where the Tutorial/First level being the level undertaken in this project.
@@
 
-\noindent One the tutorial level has started, the user is shown the basic character movement controls on the right side of the screen and can continue forward.
-Text based signs were used throughout the level to explain various mechanics or tasks to be completed - an example of this is shown in Figure 4.2 below.
+\noindent Once the tutorial level has started, the user is shown the basic character movement controls on the right side of the screen and can continue forward.
+Text-based signs were used throughout the level to explain various mechanics or tasks to be completed - an example of this is shown in Figure 4.2 below.
 
@@
 
-\noindent The user must then make there way to a central area, referred to as the Hub Room, where they are given the choice in what order they would like to complete the five main tutorials.
+\noindent The user must then make their way to a central area referred to as the Hub Room, where they are given the choice in what order they would like to complete the five main tutorials.
 These will be discussed and shown below.
@@
   \centering
-  \includegraphics[width=1\linewidth]{Figures/barrier5.png}
+  \includegraphics[width=0.9\linewidth]{Figures/barrier5.png}
   \caption{No Tutorials Completed}
@@
   \centering
-  \includegraphics[width=1\linewidth]{Figures/barrier3.png}
+  \includegraphics[width=0.9\linewidth]{Figures/barrier3.png}
   \caption{Two Tutorials Completed}
@@
   \centering
-  \includegraphics[width=1\linewidth]{Figures/barrier0.png}
+  \includegraphics[width=0.9\linewidth]{Figures/barrier0.png}
   \caption{All Tutorials Completed}
@@
 
-\noindent Once the ball object collides with the end goal object, the user is taken to the next level where the main aim to to traverse the level and throw the ball object into the next end goal.
+\noindent Once the ball object collides with the end goal object, the user is taken to the next level where the main aim is to traverse the level and throw the ball object into the next end goal.
 This process is followed for two additional levels for three in total after which the user is taken to a scene where the group members and their contributions are listed with a prompt to close the application.
@@
 \section{Article}
-The individual research aspect of this project yielded a academic article titled \textit{"Linking Gamification, Ludology and Pedagogy: How to Use Serious Games for Various Knowledge Domains"}.
+The individual research aspect of this project yielded an academic article titled \textit{"Linking Gamification, Ludology and Pedagogy: How to Use Serious Games for Various Knowledge Domains"}.
 \\\\
@@
 \\\\
-The results of the research aspect of this project is the answer to these questions which were synthesised from various case studies and the literature analysis conducted.
+The results of the research aspect of this project are the answer to these questions which were synthesised from various case studies and the literature analysis conducted.
 The literature study of the article is similar to the one conducted in this document with the addition to an analysis of three case studies in detail, one of which was mentioned in the literature study above in Chapter \ref{Chapter2}.
@@
 \\\\
-The results of this encompass four archetypal qualities needed as well as a few qualities recommendations needed to be taken into account depending on the knowledge domain a topic falls under.
+The results of this encompass four archetypal qualities needed as well as a few qualities recommendations that needed to be taken into account depending on the knowledge domain a topic falls under.
 The reasoning for choosing these specific qualities and recommendations is elaborated in detail in the article itself which can be found in Appendix \ref{AppendixC}.
-In short these qualities are named:
+In short, these qualities are named:
 \begin{enumerate}
@@
 Feedback should also be scaled up or down depending on how a user is progressing - that is, if a user is doing well they require less feedback on where to improve as compared to another user who may be struggling and should require more feedback on how to improve.
-Further than this, the means of presenting feedback is heavily dependant on the topic being taught, how tasks are handles and the general loop of the game.
+Further than this, the means of presenting feedback is heavily dependant on the topic being taught, how tasks are handled and the general loop of the game.
 In addition to this.
@@
 \\\\
-Story-telling is also an important quality which centres around keeping engagement with the game high.
-It entails making use a story or role-play within the game or the use of a story-based agent such as a character that would guide users through the material and tasks.
+Story-telling is also an important quality that centres around keeping engagement with the game at a high level.
+It entails making use of a story or role-play within the game or the use of a story-based agent such as a character that would guide users through the material and tasks.
 This can be done through contextual story-telling by having the tasks form part of a story's progression or as the main means of relaying information on a topic.
@@
 Both Hi-fidelity and low fidelity simulation games, these being a subset of serious games, are the most useful for teaching content found in the Affective, Soft Skills and Psychomotor domains since the best means to teach these is through immersing the user in the phenomena, repeated application of skills and observation respectively.
-Simulation-type serious games can also be used in the other domains such as with the game used to aid in teaching physics.
+Simulation-type serious games can also be used in other domains such as with the game used to aid in teaching physics.
 These types of games are also the most effective means for the Psychomotor domain.
@@
 To reiterate, it simply states that a topic cannot be fully understood from only the procedures or context - both are needed for a deeper understanding.
-As such if a topic where to fall under these domains it is vital to present information in a manner that all aspects are clear to a user.
+As such if a topic were to fall under these domains it is vital to present information in a manner that all aspects are clear to a user.
 
@@
 This included a digital computer game as well as various qualities needed in order for a serious game to be effectively used in an educational environment.
-In brief, these qualities were, Reflection, Feedback, Structuring and Story-telling.
+In brief, these qualities were Reflection, Feedback, Structuring and Story-telling.

### 2021-11-09 Final Doc/Chapters/Chapter5.tex
Final Push

@@
 This was the language that most of the group, excluding myself, was familiar with and most experienced with when compared to the alternatives.
-Following this, C\# was also a new language learnt for this project and while the initial usage of it was difficult, with the experience  Java, another object-oriented language, it became easy to write and implement the scripts needed.
+Following this, C\# was also a new language learnt for this project and while the initial usage of it was difficult, with experience in Java, another object-oriented language, it became easy to write and implement the scripts needed.
 \\\\
@@
 \\\\
-\LaTeX was another technology used in the latter half the project.
+\LaTeX was another technology used in the latter half of the project.
 It is a software tool that allows for the creation of PDF's and was used for the Article as well as the final documentation.
@@
 \\
-A fair amount of information concerning game design was also learnt form how psychology plays a factor in the choices game designers take when developing a game or user interface.
+A fair amount of information concerning game design was also learnt from how psychology plays a factor in the choices game designers take when developing a game or user interface.
 While a fair amount of this knowledge was used when designing the artefact, there is still much more that could have been incorporated - such as the aforementioned use of psychology to style the game better.
@@
 Additionally, various knowledge in the fields used for the research article was learnt.
-These were fields concerning educational and instructional theories, the study of games as well as turning tasks into some form of game be it digital or not.
+These were fields concerning educational and instructional theories, the study of games as well as turning tasks into some form of a game be it digital or not.
 These topics were interesting to examine and read about and were a tremendous help on how to approach any future educational endeavours such as tutoring.
@@
 This process was heavily aided by Prof.
-Günther Drevin where we were tasked with various presentations on the field of ludology itself and on the analysis of a game - Myst.
+Günther Drevin where we were tasked with various presentations on the field of ludology itself and the analysis of a game - Myst.
 
 \section{Development of Artefact}
-The primary aim of this study was stated as, \textit{to identify what qualities and principles can be applied to a video game to allow it to be used in a learning environment as a means to provide better engagement among certain students by providing an enjoyable delivery of information.}
+The primary aim of this study was stated as \textit{to identify what qualities and principles can be applied to a video game to allow it to be used in a learning environment as a means to provide better engagement among certain students by providing an enjoyable delivery of information.}
 
@@
 The artefact and research aspects of this project are distinct with no correlation between each other bar the main topic at hand being \textit{Entertainment Computing} and this aim sought to combine them.
-The research was focused on educational games and the level designed was the tutorial level which intends to teach players and as such there is a correlation.
+The research was focused on educational games and the level designed was the tutorial level which intends to teach players and as such, there is a correlation.
 The qualities identified by the research study were implemented, such as with Reflection being done by giving the user time after each section before continuing to the next.
-However, the objective stated the use of both audio and visual stimuli where the final implementation of the artefact makes use of only visual.
+However, the objective stated the use of both audio and visual stimuli where the final implementation of the artefact makes use of only visuals.
 While this is a small distinction to make on a self-imposed objective, it would have been a fine inclusion to make which would have also aided users who struggle with reading.
@@
 Another aspect of the artefact and article development to discuss is the tame management of it all.
-While all milestone submissions were delivered on time, the time management of the individual aspects of the project were lacking.
+While all milestone submissions were delivered on time, the time management of the individual aspects of the project was lacking.
 The group aspect of this project was completed roughly three weeks before final submissions while the individual research project elements, the article and documentation, were only finalised a few days prior to the deadlines with final checks typically happing on the day of submission.
@@
 \noindent As indicated in the lists above, there was a roughly equal contribution from each group member.
-There was also no major problems with group dynamics throughout the duration of this project as each member was respectful and eager to learn about the aspects which the others were responsible for.
+There was also no major problems with group dynamics throughout the duration of this project as each member was respectful and eager to learn about the aspects for which the others were responsible.
 \\\\
@@
 \section{Future Work Possibilities}
-While the project is considered to completed as it stands, there are still aspects that can be improved or others added.
-In terms of the artefact, there are numerous game design techniques that could still be taken advantage of.
+While the project is considered to be completed as it stands, there are still aspects that can be improved or others added.
+In terms of the artefact, numerous game design techniques could still be taken advantage of.
 One example of this is Culling.
@@
 With respect to the research study and article, there are two possibilities for future work.
-One is to simply continue the research and expand on what was already found and including additional fields to perhaps describe new qualities.
+One is to simply continue the research and expand on what was already found and include additional fields to perhaps describe new qualities.
 For a more practical approach, an actual serious game could be designed and developed once a suitable topic is found to present in this format.
@@
 The process of working through a project in this capacity was an exciting learning experience.
-Being able to work on a topic that has always been a personal interest was an immense help to keep the motivation of working on both an individual research assignment and a group artefact at an all time high.
+Being able to work on a topic that has always been a personal interest was an immense help to keep the motivation of working on both an individual research assignment and a group artefact at an all-time high.
 The process of creating a provisional plan, performing literary research and documenting the entire development process was certainly a new way of approaching a project for myself.
 This way of completing a project is certainly a major help to finishing the project while maintaining the original aim and scope at all times.
-It was certainly a valuable educational and personal experience which will be useful in all future projects I take part in.
+It was certainly a valuable educational and personal experience that will be useful in all future projects I take part in.
